\documentclass[extrafontsizes,a5paper]{memoir}
\usepackage[hyphenate, printer]{system/ocmc-liturgical-text-durham}%
\input{system/control} %
\usepackage[defaultlines=3,all]{nowidow}%
\begin{document}%
\input{\ltClientPath/copyright}%
\ltCover%
%\frontmatter%
%\ltCopyRight{}%
%\ltBlessing%
\mainmatter%
\ltColumnsOn%
\ltSetPrimaryDomain{en}{uk}{durlash}%
\ltSetRightDomain{ro}{uk}{dur}%
\itId{en}{uk}{durlash}{actors}{Deacon}{
\textsc{deacon}
}%
\itId{en}{uk}{durlash}{actors}{Deacon.colon}{
\itRid{actors}{Deacon}:
}%
\itId{en}{uk}{durlash}{actors}{People}{
\textsc{people}
}%
\itId{en}{uk}{durlash}{actors}{People.colon}{
\itRid{actors}{People}:
}%
\itId{en}{uk}{durlash}{actors}{Priest}{
\textsc{priest}
}%
\itId{en}{uk}{durlash}{actors}{Priest.colon}{
\itRid{actors}{Priest}:
}%
\itId{en}{uk}{durlash}{actors}{Reader}{
\textsc{reader}
}%
\itId{en}{uk}{durlash}{actors}{Reader.colon}{
\itRid{actors}{Reader}:
}%
\itId{en}{uk}{durlash}{client}{cl.bishop1.name.c}{
N
}%
\itId{en}{uk}{durlash}{client}{cl.bishop1.name.p}{
N
}%
\itId{en}{uk}{durlash}{client}{cl.bishop1.rank}{
our Archbishop (and Metropolitan)
}%
\itId{en}{uk}{durlash}{dismissals}{dis01}{
Christ, our true God,
}%
\itId{en}{uk}{durlash}{dismissals}{dis02}{
through the prayers of his all pure and holy Mother,
}%
\itId{en}{uk}{durlash}{dismissals}{dis03}{
by the power of the precious and life-giving Cross,
}%
\itId{en}{uk}{durlash}{dismissals}{dis04}{
through the protection of the honoured, Bodiless Powers of heaven,
}%
\itId{en}{uk}{durlash}{dismissals}{dis05}{
through the intercessions of the honoured, glorious Prophet, Forerunner and Baptist, John,
}%
\itId{en}{uk}{durlash}{dismissals}{dis06}{
of the holy, glorious and all-praised Apostles,
}%
\itId{en}{uk}{durlash}{dismissals}{dis07}{
of the holy, glorious and triumphant Martyrs,
}%
\itId{en}{uk}{durlash}{dismissals}{dis08}{
of our venerable and God-bearing Fathers and Mothers who have shone forth in the ascetic life,
}%
\itId{en}{uk}{durlash}{dismissals}{dis09}{
of the holy and righteous forebears of God, Joachim and Anna,
}%
\itId{en}{uk}{durlash}{dismissals}{dis10}{
of Saint N. (to whom the Church is dedicated), of Saint N., whose memory we keep today, and of all the Saints,
}%
\itId{en}{uk}{durlash}{dismissals}{dis89}{
have mercy on us and save us, for he is good and loves mankind.
}%
\itId{en}{uk}{durlash}{dismissals}{li.dis.chrysostom}{
of our Father among the Saints John Chrysostom, Archbishop of Constantinople,
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key0200.text}{
LITANY OF PEACE
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key0201.text}{
Lord, our God, whose might is beyond compare and whose glory is beyond understanding, whose mercy is without measure and whose love for mankind beyond all telling, look upon us and upon this holy house, Master, according to your loving kindness, and bestow on us and on those who pray with us your acts of rich mercy and compassion.
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key0201.title}{
PRAYER OF THE FIRST ANTIPHON
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key0202.title}{
SHORT LITANY
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key0301.text}{
Lord, our God, save Your people and bless Your inheritance. Protect the fullness of Your Church. Sanctify those who love the beauty of Your house. Glorify them in return by Your divine power, and forsake us not who have set our hope in You.
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key0301.title}{
PRAYER OF THE SECOND ANTIPHON
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key0401.text}{
You have given us grace to make these common and united prayers, and have promised that when two or three agree in your name you will grant their requests; fulfil now the petitions of your servants as is expedient, granting us in this present age the knowledge of your truth and in the age to come eternal life.
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key0401.title}{
PRAYER OF THE THIRD ANTIPHON
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key0500.title}{
THIRD ANTIPHON AND ENTRANCE WITH THE HOLY GOSPEL
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key0501.text}{
Master, Lord our God, you have set orders and armies of Angels and Archangels in heaven to minister to your glory; grant that, with our entrance, holy Angels may enter, concelebrating with us, and with us glorifying your goodness.
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key0501.title}{
PRAYER OF THE ENTRANCE
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key0502.text}{
Master, bless the holy entrance.
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key0503.text}{
Blessed is the entrance of your holy place, now and for ever, and to the ages of ages.
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key0601.text}{
Holy God, at rest in the holy place, hymned by the Seraphim with the thrice-holy song, glorified by the Cherubim and worshipped by every heavenly Power, out of non-existence you brought the universe into being and created male and female according to your image and likeness, adorning them with every gift of your grace. You give wisdom and understanding to those who ask, and you do not reject the sinner, but for our salvation you have established repentance. You have counted us, your humble and unworthy servants, worthy to stand at this time before the glory of your holy altar, and to offer you due worship and praise. Accept, Master, the Thrice-holy Hymn even from the mouth of us sinners, and visit us in your goodness. Pardon us every offence, voluntary and involuntary; sanctify our souls and bodies, and grant that we may worship you in holiness all the days of our life; at the prayers of the holy Mother of God and of all the Saints who have been well-pleasing to you in every age.
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key0601.title}{
PRAYER OF THE TRISAGION
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key0602.text}{
Dynamis.
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key0704.text}{
Master, Lover of mankind, make the pure light of your divine knowledge shine in our hearts and open the eyes of our mind to understand the message of your Gospel. Implant in us the fear of your blessed commandments, so that, having trampled down all carnal desires, we may change to a spiritual way of life, thinking and doing all things that are pleasing to you. For you are the illumination of our souls and bodies, Christ God, and to you we give glory, together with your Father who is without beginning, and your all-holy, good and life-giving Spirit, now and for ever, and to the ages of ages. Amen.
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key0704.title}{
PRAYER OF THE GOSPEL
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key0706.title}{
THE SERMON
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key0708}{
[
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key0709}{
]
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key0800.title}{
LITANY OF FERVENT SUPPLICATION
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key0801.text}{
Lord, our God, accept this fervent supplication from your servants, and have mercy on us according to the multitude of your mercy; and send down your pity on us and on all your people, who await your rich mercy.
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key0801.title}{
PRAYER OF SUPPLICATION
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key0900.title}{
LITANY FOR THE CATECHUMENS
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key0901.text}{
Catechumens, pray to the Lord.
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key0902.text}{
Believers, let us pray for the catechumens;
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key0903.text}{
That the Lord will have mercy on them;
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key0904.text}{
Instruct them in the word of truth;
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key0905.text}{
Reveal to them the Gospel of righteousness;
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key0906.text}{
Unite them to his Holy, Catholic and Apostolic Church.
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key0907.text}{
Save them, have mercy on them, help them and keep them, O God, by your grace.
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key0908.text}{
Catechumens, bow your heads to the Lord.
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key0909.text}{
Lord, our God, dwelling on high and beholding things below, who for the salvation of mankind sent forth your only-begotten Son, our Lord and God, Jesus Christ, look upon your servants the catechumens, who have bowed their necks to you; and count them worthy in due time of the washing of rebirth, the forgiveness of sins and the garment of incorruption; unite them to your holy, Catholic and Apostolic Church, and number them with your chosen flock.
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key0909.title}{
THE PRAYER FOR THE CATECHUMENS
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key0910.text}{
That with us they too may glorify your all-honoured and majestic name, of the Father, the Son and the Holy Spirit, now and for ever, and to the ages of ages.
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key0911.text}{
As many as are Catechumens, depart; Catechumens, depart; as many as are Catechumens, depart. None of the Catechumens!
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key0912.text}{
As many as are believers: again and again in peace, let us pray to the Lord.
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key1000.title}{
THE LITURGY OF THE FAITHFUL
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key1001.text}{
We thank you, Lord, God of the powers of heaven, for counting us worthy to stand even now before your holy altar and humbly to seek your compassion for our sins and for those committed in ignorance by the people. Receive our supplication, O God; make us worthy to offer you prayers and entreaties and unbloody sacrifices for all your people. And enable us, whom you have appointed to this your ministry by the power of your Holy Spirit, to invoke you at every time and place without blame and without condemnation, with the witness of a pure conscience, so that you may hear us and be merciful to us in the abundance of your goodness.
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key1001.title}{
FIRST PRAYER OF THE FAITHFUL
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key1002.text}{
Again and many times we fall down before you and beseech you, who are good and the lover of mankind, that heeding our prayer you will cleanse our souls and bodies from every defilement of flesh and spirit, and will grant us to stand without guilt or condemnation before your holy altar. Give also to those who pray with us the grace of progress in right living, in faith and spiritual understanding. Grant that always worshipping you with fear and love, they may partake of your holy Mysteries without guilt or condemnation, and be counted worthy of your heavenly kingdom.
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key1002.title}{
SECOND PRAYER OF THE FAITHFUL
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key1003.text}{
That being always guarded by your might, we may give glory to you, the Father, the Son and the Holy Spirit, now and for ever, and to the ages of ages.
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key1100.title}{
CHERUBIC HYMN AND GREAT ENTRANCE WITH THE GIFTS OF BREAD AND WINE
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key1101.text}{
None of those who are entangled in carnal desires and pleasures is worthy to approach or draw near or minister to you, King of glory; for to serve you is great and awesome even for the heavenly Powers. Yet on account of your inexpressible and boundless love for mankind you became man without change or alteration and were named our High Priest; and as Master of all you have committed to us the sacred ministry of this liturgical sacrifice without shedding of blood. 
For you alone, Lord our God, are Ruler over all things in heaven and on earth, mounted on the throne of the Cherubim, Lord of the Seraphim and King of Israel, the only Holy One, resting in the holy place. Therefore I entreat you, who alone are good and ready to hear: Look upon me, your sinful and unprofitable servant, and purify my soul and heart from an evil conscience. By the power of your Holy Spirit enable me, clothed with the grace of the priesthood, to stand at this your Holy Table and celebrate the mystery of your holy and most pure Body and your precious Blood. 
For to you I come, bending my neck and praying: Do not turn away your face from me, nor reject me from among your children, but count me, your sinful and unworthy servant, worthy to offer these gifts to you. For you are the one who offers and is offered, who receives and is distributed, Christ our God, and to you we give glory, together with your Father, who is without beginning, and your all-holy, good and life-giving Spirit, now and for ever, and to the ages of ages. Amen.
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key1101.title}{
PRAYER OF THE CHERUBIC HYMN
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key1102.text}{
We, who in a mystery represent the Cherubim and sing the thrice-holy hymn to the life-giving Trinity, let us now lay aside every care of this life.
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key1102.title}{
THE CHERUBIC HYMN
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key1103.text}{
For we are about to receive the King of all, invisibly escorted by the angelic hosts. Alleluia, alleluia, alleluia.
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key1110.text}{
May the Lord God remember you all in his Kingdom always, now and for ever, and to the ages of ages.
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key1200.title}{
LITANY OF THE PRECIOUS GIFTS
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key1201.text}{
For the precious gifts here set forth, let us pray to the Lord.
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key1202.text}{
Lord, God almighty, who alone are holy and who accept a sacrifice of praise from those who call on you with all their heart, accept also the supplication of us sinners, bring us to your holy altar, and enable us to offer you gifts and spiritual sacrifices for our sins and those committed in ignorance by the people. Count us worthy to find grace in your sight, that our sacrifice may be well pleasing to you and that the good Spirit of your grace may rest on us and on these gifts here set forth, and on all your people.
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key1202.title}{
PRAYER OF OFFERING
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key1203.text}{
Through the compassion of Your only begotten Son, with whom You are blessed, together with your all-holy, good, and life-giving Spirit, now and forever and to the ages of ages.
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key1204.text}{
Let us love one another, that with one mind we may confess:
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key1205.text}{
Father, Son and Holy Spirit, Trinity consubstantial and undivided.
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key1208.text}{
The doors, the doors. With wisdom let us attend.
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key1209.title}{
THE CREED (The Symbol of Our Faith)
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key1300.title}{
THE HOLY OBLATION
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key1301.text}{
Let us stand with awe; let us stand with fear; let us attend, that we may offer the holy oblation in peace.
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key1302.text}{
Mercy and peace: a sacrifice of praise.
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key1303.text}{
The grace of our Lord Jesus Christ, and the love of God the Father, and the communion of the Holy Spirit be with you all.
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key1304.text}{
And with your spirit.
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key1305.text}{
Let our hearts be on high.
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key1306.text}{
We have them with the Lord.
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key1307.text}{
Let us give thanks to the Lord.
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key1308.text}{
It is right and fitting [to worship Father, Son and Holy Spirit, Trinity consubstantial and undivided].
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key1309.text}{
It is right and fitting to hymn you, to bless you, to praise you, to give you thanks, to worship you in every place of your dominion; for you are God, ineffable, incomprehensible, invisible, inconceivable, ever existing, eternally the same; you and your only-begotten Son and your Holy Spirit. You brought us out of non-existence into being, and when we had fallen you raised us up again, and left nothing undone until you had brought us up to heaven and had granted us your Kingdom that is to come. For all these things we give thanks to you, and to your only-begotten Son and your Holy Spirit; for all the benefits that we have received, known and unknown, manifest and hidden. We thank you also for this liturgy which you have been pleased to accept from our hands, though there stand around you thousands of Archangels and tens of thousands of Angels, the Cherubim and the Seraphim, six-winged and many-eyed, soaring aloft upon their wings,
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key1310.text}{
singing, crying, shouting the triumphal hymn, and saying:
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key1311.text}{
Holy, holy, holy, Lord Sabaoth; heaven and earth are full of your glory. Hosanna in the highest. Blessed is he who comes in the name of the Lord. Hosanna in the highest.
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key1312.text}{
With these blessed Powers, Master, Lover of mankind, we also cry aloud and say: Holy are you and all-holy, you and your only-begotten Son and your Holy Spirit; holy are you and all-holy, and magnificent is your glory. This is how you loved your world: you gave your only-begotten Son, so that whoever believes in him might not perish, but have eternal life. And, when he had come and had fulfilled the whole dispensation for us, in the night in which he was given up, or rather gave himself up, for the life of the world, he took bread in his holy, most pure and unblemished hands and, when he had given thanks and had blessed, sanctified and broken it, gave it to his holy Disciples and Apostles, saying:
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key1313.text}{
Take, eat; this is my body, which is broken for you, for the forgiveness of sins.
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key1314.text}{
Likewise after supper he also took the cup, saying:
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key1315.text}{
Drink from this, all of you; this is my blood of the New Covenant, which is shed for you and for many for the forgiveness of sins.
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key1316.text}{
Remembering therefore this our Saviour’s command and all that has been done for us: the Cross, the Tomb, the Resurrection on the third day, the Ascension into heaven, the Sitting at the right hand, the second and glorious Coming again;
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key1317.text}{
Offering you your own of your own — in all things and for all things —
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key1318.text}{
We praise you, we bless you, we give thanks to you, O Lord, and we pray to you, our God.
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key1319.text}{
Also we offer you this spiritual worship without shedding of blood, and we ask, pray and implore you: send down your Holy Spirit upon us and upon these gifts here set forth,
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key1321.text}{
and make this bread the precious Body of your Christ,
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key1323.text}{
and what is in this Cup the precious Blood of your Christ,
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key1325.text}{
changing them by your Holy Spirit,
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key1326.text}{
so that those who partake of them may obtain vigilance of soul, forgiveness of sins, communion of your Holy Spirit, fulness of the Kingdom of heaven, freedom to speak in your presence, not judgement or condemnation. Also we offer you this spiritual worship for those who have gone to their rest in faith, Forefathers, Fathers, Patriarchs, Prophets, Apostles, Preachers, Evangelists, Martyrs, Confessors, Ascetics and every righteous spirit made perfect in faith;
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key1327.text}{
Above all for our most holy, pure, most blessed and glorious Lady, the Mother of God and Ever-Virgin, Mary.
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key1329.text}{
For the holy Prophet, Forerunner and Baptist John, the holy, glorious and all-praised Apostles, for Saint N, whose memory we keep today, and for all your Saints, at whose prayers visit us, O God. Remember too all those who have fallen asleep in hope of resurrection to eternal life (N and N), and give them rest where the light of your countenance watches. Also we beseech you: Remember, Lord, all Orthodox bishops, who rightly proclaim the word of your truth, the whole order of presbyters, the diaconate in Christ, and every order of clergy. Also we offer you this spiritual worship for the whole world, for the holy, Catholic and Apostolic Church, for those who live in chastity and holiness of life; for our faithful Christian rulers (here he may remember the Sovereign and the Royal Family) and all their household. Grant them, Lord, a peaceful reign, so that in their tranquillity we too may live calm and peaceful lives in godliness and holiness.
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key1330a.text}{
First of all, remember, Lord,
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key1330b.text}{
and grant that he may serve your holy churches in peace, safety, honour, health, and length of days, rightly proclaiming the word of your truth.
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key1331.text}{
Remember too, Lord, those whom each one has in mind, and each and all.
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key1332.text}{
And each and all.
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key1333.text}{
Remember, Lord, the city in which we dwell, and every city, town and village, and the faithful who dwell in them. Remember, Lord, those who travel by land, air, or water, the sick, the suffering, those in captivity, and their safety and salvation. Remember, Lord, those who bring offerings, those who care for the beauty of your holy churches, and those who remember the poor, and send down upon us all your rich mercies.
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key1334.text}{
And grant that with one voice and one heart we may glorify and praise your all-honoured and majestic name, of the Father, the Son and the Holy Spirit, now and for ever, and to the ages of ages.
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key1335.text}{
And the mercies of our great God and Saviour, Jesus Christ, shall be with all of you.
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key1336.text}{
And with your spirit.
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key1401.text}{
Having commemorated all the saints, again and again in peace let us pray to the Lord.
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key1402.text}{
For the precious gifts here set forth and sanctified, let us pray to the Lord.
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key1403.text}{
That our God, who loves mankind, having accepted them on his holy and immaterial Altar above the heavens, as a savour of spiritual fragrance, may send down upon us in return his divine grace and the gift of the Holy Spirit, let us pray.
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key1404.text}{
Having asked for the unity of the faith and the communion of the Holy Spirit, let us entrust ourselves and one another and our whole life to Christ, our God.
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key1405.text}{
To you, Master, Lover of mankind, we entrust our whole life and our hope, and we entreat, pray and implore you: count us worthy to partake of your heavenly and awesome Mysteries at this sacred and spiritual Table with a pure conscience, for forgiveness of sins and pardon of offences, for communion of the Holy Spirit, for inheritance of the Kingdom of heaven and for boldness before you; not for judgement or condemnation.
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key1406.text}{
And count us worthy, Master, with boldness and without condemnation to dare to call upon you, the God of heaven, as Father, and to say:
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key1407.text}{
We thank you, King invisible, who by your boundless power created all things, in the abundance of your mercy bringing them into being out of nothing. Do you yourself, Master, look down from heaven on those who have bowed their heads to you; for they have bowed not to flesh and blood, but to you, the God before whom we stand in awe. Make smooth, then, our path for our good, Master, through what lies before us, according to the need of each: sail with those sail, journey with those who journey, heal the sick, for you are the physician of our souls and bodies.
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key1409.text}{
Give heed, Lord Jesus Christ our God, from your holy dwelling-place and from the glorious throne of your kingdom; and come to sanctify us, you who are enthroned on high with the Father and invisibly present here with us. And with your mighty hand grant communion in your most pure Body and precious Blood to us, and through us to all the people.
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key1409.title}{
COMMUNION OF THE CLERGY AND PEOPLE
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key1410.text}{
The Holy Things for the Holy.
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key1411.text}{
One is Holy, one is Lord: Jesus Christ, to the glory of God the Father. Amen.
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key1526.text}{
With fear of God, with faith and love, draw near.
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key1527.text}{
The servant of God (Name), is granted communion of the precious and all-holy Body and Blood of our Lord and God and Saviour, Jesus Christ, for the forgiveness of sins and for eternal life.
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key1528.rubric}{
The Deacon hands the chalice to the Priest, who gives Communion to the People, saying to each communicant:
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key1529.text}{
O God, save your people, and bless your inheritance.
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key1530.text}{
We have seen the true light; we have received the heavenly Spirit; we have found the true faith, as we worship the undivided Trinity; for the Trinity has saved us.
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key1603.text}{
Let our mouth be filled with your praise, O Lord, that we may sing of your glory, for you have counted us worthy to partake of your holy Mysteries; keep us in your holiness, as we may meditate on your righteousness all the day long. Alleluia, alleluia, alleluia.
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key1604.text}{
Stand upright. Having received the divine, holy, pure, immortal, heavenly, life-giving and dread Mysteries of Christ, let us give worthy thanks to the Lord.
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key1605.text}{
Having asked that the whole day may be perfect, holy, peaceful and sinless, let us entrust ourselves and one another and our whole life to Christ our God.
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key1606.text}{
We thank you, Lord, lover of mankind, benefactor of our souls, that you have counted us worthy today of your heavenly and immortal Mysteries. Make straight our way, establish us all in the fear of you, watch over our life, and make firm our steps, through the prayers and intercessions of the glorious Mother of God and Ever-Virgin Mary, and of all your Saints.
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key1606.title}{
PRAYER OF THANKSGIVING
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key1700.title}{
DISMISSAL
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key1701.text}{
Let us go forth in peace.
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key1702.text}{
O Lord, you bless those who bless you, and sanctify those who have put their trust in you: save your people and bless your inheritance; protect the fullness of your Church; sanctify those who love the beauty of your house; glorify them in return by your divine power, and do not forsake us who hope in you. Give peace to your world, to your churches, to the priests, to our rulers, and to all your people. For every good gift and every perfect gift is from on high, coming down from you, the Father of lights; and to you we give glory, thanksgiving and worship, to the Father, the Son and the Holy Spirit, now and for ever, and to the ages of ages.
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key1702.title}{
PRAYER BEHIND THE AMBO
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.Key1704.text}{
Christ, our God, the fulfilment of the Law and the Prophets, you have fulfilled all the Father’s dispensation. Fill our hearts with joy and gladness, always, now and for ever, and to the ages of ages. Amen.
}%
\itId{en}{uk}{durlash}{eu.lichrysbasil}{euLI.MM.HymnsDuringCommunion.title}{
HYMNS DURING HOLY COMMUNION
}%
\itId{en}{uk}{durlash}{ho.s07}{hoLI.Antiphon1.text}{
At the prayers of the Mother of God, O Saviour, save us.
}%
\itId{en}{uk}{durlash}{ho.s07}{hoLI.Antiphon21.text}{
Son of God,
}%
\itId{en}{uk}{durlash}{ho.s07}{hoLI.Antiphon22.text}{
save us who sing to you: Alleluia!
}%
\itId{en}{uk}{durlash}{ho.s07}{hoLI.Antiphon2s.text}{
risen from the dead,
}%
\itId{en}{uk}{durlash}{ho.s07}{hoLI.EntranceHymn.text}{
Come, let us worship and fall down before Christ. Son of God, risen from the dead, save us who sing to you: Alleluia! [If it is not a Sunday or Eastertide, we sing: Son of God, wonderful in the Saints, save us who sing to you: Alleluia!]
}%
\itId{en}{uk}{durlash}{ho.s07}{hoLI.OnlyBegotten.text}{
Only-begotten Son and Word of God, who, being immortal, accepted for our salvation to take flesh from the holy Mother of God and Ever-Virgin Mary, and without change became man; you were crucified, Christ God, by death trampling on death, being one of the Holy Trinity, glorified with the Father and the Holy Spirit: save us!
}%
\itId{en}{uk}{durlash}{ho.s07}{hoLI.TrisagiosHymn.text}{
Holy God, Holy Strong, Holy Immortal, have mercy on us.
}%
\itId{en}{uk}{durlash}{ho.s07}{hoLI.TrisagiosHymn3.text}{
Holy Immortal,
}%
\itId{en}{uk}{durlash}{ho.s07}{hoLI.TrisagiosHymn4.text}{
have mercy on us.
}%
\itId{en}{uk}{durlash}{ho.s21}{hoPrayer.Key101.text}{
I believe, Lord, and I confess that you are truly the Christ, the Son of the living God, who came into the world to save sinners, of whom I am the first. Also I believe that this is indeed Your most pure Body, and this indeed your precious Blood. Therefore, I beseech you, have mercy upon me, and forgive me my offences, voluntary and involuntary, in word and in deed, in knowledge and in ignorance, and count me worthy, to partake uncondemned of your pure Mysteries for forgiveness of sins and for eternal life. Amen.
}%
\itId{en}{uk}{durlash}{ho.s21}{hoPrayer.Key110.text}{
See, to divine Communion I draw near; My Maker, burn me not as I partake, for you are fire consuming the unworthy. But therefore make me clean from every stain.
}%
\itId{en}{uk}{durlash}{ho.s21}{hoPrayer.Key121.text}{
Of your mystical Supper, Son of God, receive me today as a communicant; for I will not tell of the Mystery to your enemies; I will not give you a kiss, like Judas; but like the Thief I confess you; Remember me, Lord, in your Kingdom.
}%
\itId{en}{uk}{durlash}{ho.s21}{hoPrayer.Key161.text}{
Master, lover of mankind, Lord Jesus Christ, my God, let not these holy Mysteries be for my condemnation because of my unworthiness, but rather for the cleansing and sanctification of both soul and body, and as a pledge of the life and kingdom to come. It is good for me to cleave to God, to place in the Lord the hope of my salvation.
}%
\itId{en}{uk}{durlash}{ho.s21}{hoPrayer.title}{
PRAYERS OF HOLY COMMUNION
}%
\itId{en}{uk}{durlash}{ho.s99}{bede.text}{
Orthodoxy's guide, teacher of piety and reverence, beacon of the world, fair ornament of monks. Inspired by God, o, wise Bede, by your teaching you have enlightened all; o, harp of the Spirit, intercede with Christ God, that our souls may be saved.
}%
\itId{en}{uk}{durlash}{ho.s99}{cuthbert.text}{
Faithful guide of Northumbria's Church an example of meekness and humility in fasting, vigils and in prayer an adornment of bishops and the glory of monks. O Holy Cuthbert, you dwell now in the light which knows no evening standing at the throne of God. Remember those that honour you and ask of Christ to have mercy on us.
}%
\itId{en}{uk}{durlash}{ho.s99}{silouan.text}{
You received and knew the Holy Spirit and acquired fully Adam’s tears. With unquenchable thirst and desire for Christ you kept your mind in hell by repentance and thus obtained the great love for all nations. Father Silouan, ever pray before God to grant to us His Holy Sprit and His great mercy.
}%
\itId{en}{uk}{durlash}{liturgical.verses}{psLI.aftercommunion.v1.text}{
Blessed be the name of the Lord, from this time forth and for evermore.
}%
\itId{en}{uk}{durlash}{me.m10.d28}{alt1.meLI.Antiphon2.text}{
Son of God, wonderful in the Saints, save us who sing to you: Alleluia!
}%
\itId{en}{uk}{durlash}{misc}{vVerse1}{
1st Verse
}%
\itId{en}{uk}{durlash}{misc}{vVerse2}{
2nd Verse
}%
\itId{en}{uk}{durlash}{misc}{vVerse3}{
3rd Verse
}%
\itId{en}{uk}{durlash}{prayers}{Allilouia3.text}{
Alleluia. Alleluia. Alleluia.
}%
\itId{en}{uk}{durlash}{prayers}{AxionEstinComplete.text}{
It is truly right to call you blessed, who gave birth to God, ever-blessed and most pure, and Mother of our God. Greater in honour than the Cherubim and beyond compare more glorious than the Seraphim, without corruption you gave birth to God the Word; truly the Mother of God, we magnify you.
}%
\itId{en}{uk}{durlash}{prayers}{DiEfchonPateron.text}{
Through the prayers of our holy fathers Lord Jesus Christ, our God have mercy upon us.
}%
\itId{en}{uk}{durlash}{prayers}{DoxaPatri}{
Glory to the Father, and to the Son, and to the Holy Spirit.
}%
\itId{en}{uk}{durlash}{prayers}{DoxaSoiKyrie}{
Glory to You, O Lord, glory to You.
}%
\itId{en}{uk}{durlash}{prayers}{DoxaSoiOTheosImon.text}{
Glory to you, Christ God, our hope, glory to you.
}%
\itId{en}{uk}{durlash}{prayers}{KaiNynKaiAei.text}{
Both now and for ever, and to the ages of ages. Amen.
}%
\itId{en}{uk}{durlash}{prayers}{PantoteNyn.text}{
Always, now and for ever, and to the ages of ages. Amen.
}%
\itId{en}{uk}{durlash}{prayers}{PaterImon.text}{
Our Father, in heaven, may your name be hallowed; your kingdom come; your will be done on earth as in heaven. Give us today our daily bread, and forgive us our debts, as we forgive our debtors; and do not lead us into temptation, but deliver us from the evil one.
}%
\itId{en}{uk}{durlash}{prayers}{Pistevo.text}{
I believe in one God, Father almighty, Maker of heaven and earth, and of all things visible and invisible. And in one Lord, Jesus Christ, the only-begotten Son of God, begotten from the Father before all ages. Light from Light, true God from true God, begotten not made, consubstantial with the Father; through him all things were made. For our sake and for our salvation he came down from heaven, and was incarnate from the Holy Spirit and the Virgin Mary and became man. He was crucified also for us under Pontius Pilate, and suffered and was buried; he rose again on the third day, in accordance with the Scriptures, and ascended into heaven, and is seated at the right hand of the Father. He is coming again in glory to judge the living and the dead, and his kingdom will have no end. And in the Holy Spirit, the Lord, the Giver of life, who proceeds from the Father, who together with Father and Son is worshipped and together glorified; who spoke through the Prophets. In one Holy, Catholic and Apostolic Church. I confess one Baptism for the forgiveness of sins. I await the resurrection of the dead and the life of the age to come. Amen.
}%
\itId{en}{uk}{durlash}{prayers}{enarxis02}{
Blessed is the Kingdom of the Father, and of the Son, and of the Holy Spirit, now and for ever and to the ages of ages.
}%
\itId{en}{uk}{durlash}{prayers}{epi02}{
Peace to you.
}%
\itId{en}{uk}{durlash}{prayers}{exc01}{
For to you belong all glory, honour and worship, to the Father, the Son and the Holy Spirit, now and for ever, and to the ages of ages.
}%
\itId{en}{uk}{durlash}{prayers}{exc02}{
For yours is the might, and yours is the kingdom, the power and the glory, of the Father, the Son and the Holy Spirit, now and for ever, and to the ages of ages.
}%
\itId{en}{uk}{durlash}{prayers}{exc03}{
For you, O God, are good and love mankind, and to you we give glory, to the Father, the Son, and the Holy Spirit, now and for ever, and to the ages of ages.
}%
\itId{en}{uk}{durlash}{prayers}{exc05a}{
For you, our God, are holy, and to you we give glory, to the Father, the Son, and the Holy Spirit, now and for ever,
}%
\itId{en}{uk}{durlash}{prayers}{exc05b}{
And to the ages of ages.
}%
\itId{en}{uk}{durlash}{prayers}{exc07a}{
Through the grace and compassion and love towards mankind of your only-begotten Son, with whom you are blessed, together with your all-holy, good and life-giving Spirit, now and for ever, and to the ages of ages.
}%
\itId{en}{uk}{durlash}{prayers}{exc11}{
For you, O God, are merciful, and love mankind, and to you we give glory, to the Father, the Son, and the Holy Spirit, now and for ever, and to the ages of ages.
}%
\itId{en}{uk}{durlash}{prayers}{exc17}{
Wisdom.
}%
\itId{en}{uk}{durlash}{prayers}{exc18}{
Stand upright.
}%
\itId{en}{uk}{durlash}{prayers}{exc19}{
Let us attend.
}%
\itId{en}{uk}{durlash}{prayers}{exc20}{
For yours is the kingdom, the power and the glory, of the Father, the Son and the Holy Spirit, now and for ever, and to the ages of ages.
}%
\itId{en}{uk}{durlash}{prayers}{exc24}{
For you are our sanctification, and to you we give glory, to the Father, the Son and the Holy Spirit, now and for ever, and to the ages of ages.
}%
\itId{en}{uk}{durlash}{prayers}{gos02}{
Let us listen to the Holy Gospel.
}%
\itId{en}{uk}{durlash}{prayers}{gos03a}{
The reading is from the Holy Gospel according to
}%
\itId{en}{uk}{durlash}{prayers}{gos03b}{
N
}%
\itId{en}{uk}{durlash}{prayers}{gos04}{
Peace to you.
}%
\itId{en}{uk}{durlash}{prayers}{pet00}{
Let us pray to the Lord.
}%
\itId{en}{uk}{durlash}{prayers}{pet01}{
In peace, let us pray to the Lord.
}%
\itId{en}{uk}{durlash}{prayers}{pet02}{
For the peace from on high and for the salvation of our souls, let us pray to the Lord.
}%
\itId{en}{uk}{durlash}{prayers}{pet03}{
For the peace of the whole world, for the welfare of the holy Churches of God, and for the union of all, let us pray to the Lord.
}%
\itId{en}{uk}{durlash}{prayers}{pet04}{
For this holy house, and for those who enter it with faith, reverence and the fear of God, let us pray to the Lord.
}%
\itId{en}{uk}{durlash}{prayers}{pet05}{
For all devout and Orthodox Christians, let us pray to the Lord.
}%
\itId{en}{uk}{durlash}{prayers}{pet06a}{
For
}%
\itId{en}{uk}{durlash}{prayers}{pet06b}{
for the honoured order of presbyters, for the diaconate in Christ, for all the clergy and the people, let us pray to the Lord.
}%
\itId{en}{uk}{durlash}{prayers}{pet07S}{
For our Sovereign Lord, King Charles, the Royal Family, his Government, and all in authority, let us pray to the Lord.
}%
\itId{en}{uk}{durlash}{prayers}{pet08}{
For this city, for every city, town and village, and for the faithful who dwell in them, let us pray to the Lord.
}%
\itId{en}{uk}{durlash}{prayers}{pet09}{
For favourable weather, an abundance of the fruits of the earth, and temperate seasons, let us pray to the Lord.
}%
\itId{en}{uk}{durlash}{prayers}{pet10}{
For those who travel by land, air or water, for the sick, the suffering, for those in captivity, and for their safety and salvation, let us pray to the Lord.
}%
\itId{en}{uk}{durlash}{prayers}{pet11}{
For our deliverance from all affliction, wrath, danger and constraint, let us pray to the Lord.
}%
\itId{en}{uk}{durlash}{prayers}{pet12}{
Help us, save us, have mercy on us and keep us, O God, by your grace.
}%
\itId{en}{uk}{durlash}{prayers}{pet13}{
Commemorating our all-holy, pure, most blessed and glorious Lady, Mother of God and Ever-Virgin Mary, with all the Saints, let us entrust ourselves and one another and our whole life to Christ our God.
}%
\itId{en}{uk}{durlash}{prayers}{pet14}{
Again and again, in peace, let us pray to the Lord.
}%
\itId{en}{uk}{durlash}{prayers}{pet15}{
Let us all say, with all our soul and with all our mind, let us say.
}%
\itId{en}{uk}{durlash}{prayers}{pet16}{
Lord Almighty, the God of our fathers, we pray you, hear and have mercy.
}%
\itId{en}{uk}{durlash}{prayers}{pet17}{
Have mercy on us, O God, according to your great mercy, we pray you, hear and have mercy.
}%
\itId{en}{uk}{durlash}{prayers}{pet19Sa}{
Also we pray for
}%
\itId{en}{uk}{durlash}{prayers}{pet20}{
Also we pray for our Sovereign Lord, King Charles, the Royal Family, his Government, and all in authority.
}%
\itId{en}{uk}{durlash}{prayers}{pet21}{
Also we pray for mercy, life, peace, health, salvation, visitation, pardon and forgiveness of sins for the servants of God, all devout and Orthodox Christians, those who dwell in or visit this city and parish, the wardens and members of this church and their families, and all who have asked for our prayers, unworthy though we are.
}%
\itId{en}{uk}{durlash}{prayers}{pet22}{
Also we pray for the blessed and ever-remembered founders of this holy church, and for all our brothers and sisters who have gone to their rest before us, and who lie here asleep in the true faith; and for the Orthodox everywhere and that they may be pardoned all their offences, both voluntary and involuntary.
}%
\itId{en}{uk}{durlash}{prayers}{pet23}{
Also we pray for those who bring offerings, those who care for the beauty of this holy and venerable house, for those who labour in its service, for those who sing, and for the people here present, who await your great and rich mercy.
}%
\itId{en}{uk}{durlash}{prayers}{pet24}{
Let us complete our prayer to the Lord.
}%
\itId{en}{uk}{durlash}{prayers}{pet25m}{
That the whole day may be perfect, holy, peaceful, and sinless let us ask of the Lord.
}%
\itId{en}{uk}{durlash}{prayers}{pet26}{
An angel of peace, a faithful guide, a guardian of our souls and bodies, let us ask of the Lord.
}%
\itId{en}{uk}{durlash}{prayers}{pet27}{
Pardon and forgiveness of our sins and offences, let us ask of the Lord.
}%
\itId{en}{uk}{durlash}{prayers}{pet28}{
Things good and profitable for our souls, and peace for the world, let us ask of the Lord.
}%
\itId{en}{uk}{durlash}{prayers}{pet29}{
That we may live out the rest of our days in peace and repentance, let us ask of the Lord.
}%
\itId{en}{uk}{durlash}{prayers}{pet30}{
A Christian end to our life, painless, unashamed and peaceful, and a good defence before the dread judgement seat of Christ, let us ask.
}%
\itId{en}{uk}{durlash}{prayers}{pet31}{
Peace to all.
}%
\itId{en}{uk}{durlash}{prayers}{pet32}{
Let us bow our heads to the Lord.
}%
\itId{en}{uk}{durlash}{prayers}{pet37}{
May the blessing of the Lord and his mercy come upon you, by his grace and love for mankind, always, now and for ever, and to the ages of ages.
}%
\itId{en}{uk}{durlash}{prayers}{res01}{
Lord, have mercy.
}%
\itId{en}{uk}{durlash}{prayers}{res02}{
Grant this, O Lord.
}%
\itId{en}{uk}{durlash}{prayers}{res03}{
To you, O Lord.
}%
\itId{en}{uk}{durlash}{prayers}{res04}{
Amen.
}%
\itId{en}{uk}{durlash}{prayers}{res05}{
And to your spirit.
}%
\itId{en}{uk}{durlash}{prayers}{res06}{
Lord, have mercy. Lord, have mercy. Lord, have mercy.
}%
\itId{en}{uk}{durlash}{prayers}{res08}{
Master, give the blessing.
}%
\itId{en}{uk}{durlash}{prayers}{res10}{
Amen. Amen. Amen.
}%
\itId{en}{uk}{durlash}{prayers}{res13}{
Holy Master, give the blessing.
}%
\itId{en}{uk}{durlash}{ps}{psa102.v1.text}{
Bless the Lord, O my soul, and all that is within me, bless his holy name.
}%
\itId{en}{uk}{durlash}{ps}{psa102.v19.text}{
The Lord has prepared his throne in heaven, and his kingdom rules over all.
}%
\itId{en}{uk}{durlash}{ps}{psa102.v2.text}{
Bless the Lord, O my soul, and forget none of his benefits.
}%
\itId{en}{uk}{durlash}{ps}{psa117.v1.text}{
Give thanks to the Lord, for he is good, for his mercy endures for ever.
}%
\itId{en}{uk}{durlash}{ps}{psa145.v1.text}{
Praise the Lord, O my soul:
}%
\itId{en}{uk}{durlash}{ps}{psa145.v10.text}{
The Lord will be king for ever: your God, O Sion, will reign throughout all generations.
}%
\itId{en}{uk}{durlash}{ps}{psa145.v2.text}{
while I live, I will praise the Lord; while I exist, I will praise my God.
}%
\itId{en}{uk}{durlash}{ps}{psa145.v5.text}{
Blessed are those whose helper is the God of Jacob; whose hope is in the Lord their God.
}%
\itId{en}{uk}{durlash}{ps}{psa68.v35.text}{
Let the heavens and the earth sing his praise.
}%
\itId{en}{uk}{durlash}{pub.priest.servicebook}{doxapatrikainyn}{
Glory to the Father, and to the Son, and to the Holy Spirit, both now and for ever, and to the ages of ages. Amen.
}%
\itId{en}{uk}{durlash}{pub.priest.servicebook}{li.blessboth}{
Master, bless them both.
}%
\itId{en}{uk}{durlash}{pub.priest.servicebook}{li.blessingmercy}{
May the blessing and mercy of the Lord come upon you.
}%
\itId{en}{uk}{durlash}{pub.priest.servicebook}{li.blessreader}{
Master, bless the herald of the Good Tidings of the Holy Apostle and Evangelist N.
}%
\itId{en}{uk}{durlash}{pub.priest.servicebook}{li.blessreader2}{
May God, through the prayers of the holy, glorious Apostle and Evangelist N., grant you to proclaim the word with much power, for the fulfilling of the Gospel of his Beloved Son, our Lord Jesus Christ.
}%
\itId{en}{uk}{durlash}{pub.priest.servicebook}{li.changebread}{
Master, bless the holy Bread.
}%
\itId{en}{uk}{durlash}{pub.priest.servicebook}{li.changewine}{
Master, bless the holy Cup.
}%
\itId{en}{uk}{durlash}{pub.priest.servicebook}{li.dis.oanastas}{
May
}%
\itId{en}{uk}{durlash}{pub.priest.servicebook}{li.end.title.doc}{
THE END OF THE DIVINE LITURGY OF JOHN CHRYSOSTOM
}%
\itId{en}{uk}{durlash}{pub.priest.servicebook}{li.godisthelord}{
Blessed is he who comes in the name of the Lord. The Lord is God and has appeared to us.
}%
\itId{en}{uk}{durlash}{pub.priest.servicebook}{li.litanylordsprayer.title.doc}{
LITANY OF THE LORD'S PRAYER
}%
\itId{en}{uk}{durlash}{pub.priest.servicebook}{li.lordsname}{
In the name of the Lord.
}%
\itId{en}{uk}{durlash}{pub.priest.servicebook}{li.preparation.mercy}{
God, cleanse me a sinner.
}%
\itId{en}{uk}{durlash}{pub.priest.servicebook}{li.prokeimenonmode}{
Prokeimenon of the Apostle. Tone... A Psalm of David.
}%
\itId{en}{uk}{durlash}{pub.priest.servicebook}{li.readings.title.doc}{
THE READINGS FROM THE NEW TESTAMENT
}%
\itId{en}{uk}{durlash}{pub.priest.servicebook}{li.rubric.alldays}{
Then, on all days:
}%
\itId{en}{uk}{durlash}{pub.priest.servicebook}{li.rubric.bede}{
Tone 8. Troparion of St Bede
}%
\itId{en}{uk}{durlash}{pub.priest.servicebook}{li.rubric.blesswithgospel}{
The Priest takes the Gospel from the Deacon, kisses it and blesses the people with it. He then replaces it on the Holy Table.
}%
\itId{en}{uk}{durlash}{pub.priest.servicebook}{li.rubric.bowcommunion}{
Then the Priest, and the Deacon, in his usual place, bow three times, saying
}%
\itId{en}{uk}{durlash}{pub.priest.servicebook}{li.rubric.catechumens}{
Here may follow the Litany for the Catechumens, this is, those preparing for baptism.
}%
\itId{en}{uk}{durlash}{pub.priest.servicebook}{li.rubric.catechumens2}{
To each petition the People answer:
}%
\itId{en}{uk}{durlash}{pub.priest.servicebook}{li.rubric.cuthbert}{
Tone 8. Troparion of St Cuthbert
}%
\itId{en}{uk}{durlash}{pub.priest.servicebook}{li.rubric.deaconquietly}{
The Deacon, in a low voice, says:
}%
\itId{en}{uk}{durlash}{pub.priest.servicebook}{li.rubric.eachpetition}{
And so after each petition
}%
\itId{en}{uk}{durlash}{pub.priest.servicebook}{li.rubric.eachpetition2}{
And so after each of the following petitions.
}%
\itId{en}{uk}{durlash}{pub.priest.servicebook}{li.rubric.giveantidoron}{
The Priest distributes the Antidoron, saying to each recipient:
}%
\itId{en}{uk}{durlash}{pub.priest.servicebook}{li.rubric.kontakion1}{
The Apolytikia for the day and for the dedication of the Church are sung:
}%
\itId{en}{uk}{durlash}{pub.priest.servicebook}{li.rubric.notsunday}{
On weekdays, outside Eastertide, or a feast of the Lord, we sing after each verse:
}%
\itId{en}{uk}{durlash}{pub.priest.servicebook}{li.rubric.preach}{
Then the Preacher instructs the people in the word of God.
}%
\itId{en}{uk}{durlash}{pub.priest.servicebook}{li.rubric.readgospel}{
The Deacon reads the Gospel for the day. When it is finished the Priest blesses the Deacon saying:
}%
\itId{en}{uk}{durlash}{pub.priest.servicebook}{li.rubric.resurrectionmode}{
Then the Resurrection Apolytikion of the current Tone.
}%
\itId{en}{uk}{durlash}{pub.priest.servicebook}{li.rubric.silouan}{
Tone 3. Troparion of St Silouan
}%
\itId{en}{uk}{durlash}{pub.priest.servicebook}{li.rubric.smallentrance}{
While the Doxastikon of the Beatitudes, or the Third Antiphon, is being sung, the Priest and Deacon, standing in front of the Holy Table, make three bows; then the Priest takes the holy Gospel and gives it to the Deacon, who kisses the Priest’s hand. And so they come out through the north door, preceded by lights, and make the Little Entrance. Standing in the middle of the Church they bow their heads.
}%
\itId{en}{uk}{durlash}{pub.priest.servicebook}{li.rubric.sundayantifon3}{
Then the Beatitudes, or the Third Antiphon, are sung. On Sundays the following Antiphon may be used:
}%
\itId{en}{uk}{durlash}{pub.priest.servicebook}{li.rubric.sundaydismissal}{
(on Sundays: he who rose from the dead,)
}%
\itId{en}{uk}{durlash}{pub.priest.servicebook}{li.rubric.thriceeach}{
Three times. And so after the remaining petitions.
}%
\itId{en}{uk}{durlash}{pub.priest.servicebook}{li.thanksdismissal.title.doc}{
THANKSGIVING AND DISMISSAL
}%
\itId{en}{uk}{durlash}{rubrical}{BeginLiturgy}{
The Priest, lifting up the book of the Gospel, and making the sign of the Cross with it over the Antimension, says in a clear voice:
}%
\itId{en}{uk}{durlash}{rubrical}{DeaconStart}{
The Deacon, having received a blessing from the Priest, comes out of the Sanctuary by the North Door and, standing in his usual place in front of the Holy Doors, makes three bows and begins:
}%
\itId{en}{uk}{durlash}{rubrical}{InALowVoice}{
(in a low voice)
}%
\itId{en}{uk}{durlash}{rubrical}{Or}{
\emph{or:}
}%
\itId{en}{uk}{durlash}{rubrical}{Thrice}{
(three times)
}%
\itId{en}{uk}{durlash}{rubrical}{cl.eu.lichrysbasil.R009}{
The Reader reads the title of the Apostle.
}%
\itId{en}{uk}{durlash}{rubrical}{cl.eu.lichrysbasil.R010}{
The Reader reads the Apostle, and when he has finished the priest says:
}%
\itId{en}{uk}{durlash}{template.titles}{li2.html.tab}{
THE DIVINE LITURGY OF OUR FATHER AMONG THE SAINTS JOHN CHRYSOSTOM
}%
\itId{en}{uk}{durlash}{template.titles}{li2.html.tab.doc}{
THE DIVINE LITURGY OF OUR FATHER AMONG THE SAINTS JOHN CHRYSOSTOM
}%
\itId{en}{uk}{durlash}{template.titles}{li2.html.tab.header}{
THE DIVINE LITURGY OF OUR FATHER AMONG THE SAINTS JOHN CHRYSOSTOM
}%
\itId{en}{uk}{durlash}{template.titles}{li2.html.tab.toc}{
THE DIVINE LITURGY OF OUR FATHER AMONG THE SAINTS JOHN CHRYSOSTOM
}%
\itId{en}{uk}{durlash}{titles}{Eisodikon}{
ENTRANCE HYMN
}%
\itId{en}{uk}{durlash}{titles}{KyriakiProsefchi}{
THE LORD'S PRAYER
}%
\itId{en}{uk}{durlash}{titles}{LitCatechumens}{
THE LITURGY OF THE CATECHUMENS
}%
\itId{en}{uk}{durlash}{variables.info}{Antiphon1.title}{
FIRST ANTIPHON
}%
\itId{en}{uk}{durlash}{variables.info}{Antiphon2.title}{
SECOND ANTIPHON
}%
\itId{en}{uk}{durlash}{variables.info}{TheotokosHymn.title}{
HYMN TO THE THEOTOKOS
}%
\itId{en}{uk}{durlash}{variables.info}{Trisagion.title}{
TRISAGION HYMN
}%
\itId{en}{us}{ages}{actors}{Deacon}{
\textsc{deacon}
}%
\itId{en}{us}{ages}{actors}{Deacon.colon}{
\itRid{actors}{Deacon}:
}%
\itId{en}{us}{ages}{actors}{People}{
\textsc{people}
}%
\itId{en}{us}{ages}{actors}{People.colon}{
\itRid{actors}{People}:
}%
\itId{en}{us}{ages}{actors}{Priest}{
\textsc{priest}
}%
\itId{en}{us}{ages}{actors}{Priest.colon}{
\itRid{actors}{Priest}:
}%
\itId{en}{us}{ages}{actors}{Reader}{
\textsc{reader}
}%
\itId{en}{us}{ages}{actors}{Reader.colon}{
\itRid{actors}{Reader}:
}%
\itId{en}{us}{ages}{client}{cl.bishop1.name.c}{
(name),
}%
\itId{en}{us}{ages}{client}{cl.bishop1.name.p}{
N.
}%
\itId{en}{us}{ages}{client}{cl.bishop1.rank}{
(episcopal rank)
}%
\itId{en}{us}{ages}{dismissals}{dis01}{
Christ, our true God,
}%
\itId{en}{us}{ages}{dismissals}{dis02}{
through the prayers of his all pure and holy Mother,
}%
\itId{en}{us}{ages}{dismissals}{dis03}{
by the power of the precious and life-giving Cross,
}%
\itId{en}{us}{ages}{dismissals}{dis04}{
through the protection of the honoured, Bodiless Powers of heaven,
}%
\itId{en}{us}{ages}{dismissals}{dis05}{
through the intercessions of the honoured, glorious Prophet, Forerunner and Baptist, John,
}%
\itId{en}{us}{ages}{dismissals}{dis06}{
of the holy, glorious and all-praised Apostles,
}%
\itId{en}{us}{ages}{dismissals}{dis07}{
of the holy, glorious and triumphant Martyrs,
}%
\itId{en}{us}{ages}{dismissals}{dis08}{
of our venerable and God-bearing Fathers and Mothers who have shone forth in the ascetic life,
}%
\itId{en}{us}{ages}{dismissals}{dis09}{
of the holy and righteous forebears of God, Joachim and Anna,
}%
\itId{en}{us}{ages}{dismissals}{dis10}{
of Saint N. (to whom the Church is dedicated), of Saint N., whose memory we keep today, and of all the Saints,
}%
\itId{en}{us}{ages}{dismissals}{dis89}{
have mercy on us and save us, for he is good and loves mankind.
}%
\itId{en}{us}{ages}{dismissals}{li.dis.chrysostom}{
of our Father among the Saints John Chrysostom, Archbishop of Constantinople,
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key0200.text}{
THE LITANY OF PEACE OR GREAT LITANY
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key0201.text}{
Lord, our God, Whose dominion is incomparable and glory incomprehensible; Whose mercy is immeasurable, and love for mankind ineffable: Look upon us and upon this holy house in Your loving-kindness, and grant to us and to those who pray with us Your abundant mercy and compassion.
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key0201.title}{
THE PRAYER OF THE FIRST ANTIPHON
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key0202.title}{
THE SMALL LITANY
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key0301.text}{
Lord, our God, save Your people and bless Your inheritance. Protect the fullness of Your Church. Sanctify those who love the beauty of Your house. Glorify them in return by Your divine power, and forsake us not who have set our hope in You.
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key0301.title}{
THE PRAYER OF THE SECOND ANTIPHON
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key0401.text}{
Lord, You have granted us to offer these common prayers in unison and have promised that when two or three agree in Your name, You will grant their requests. Fulfill now, O Lord, the petitions of Your servants as may be of benefit to them, granting us in the present age the knowledge of Your truth, and in the age to come eternal life.
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key0401.title}{
THE PRAYER OF THE THIRD ANTIPHON
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key0500.title}{
THE SMALL ENTRANCE
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key0501.text}{
Master, Lord our God, Who has established the orders and hosts of angels and archangels in heaven to minister to Your glory, grant that holy angels may enter with us, that together we may celebrate and glorify Your goodness.
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key0501.title}{
THE ENTRANCE PRAYER
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key0502.text}{
Master, bless the holy entrance.
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key0503.text}{
Blessed be the entrance of Your holy ones always, now and forever and to the ages of ages.
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key0601.text}{
O Holy God, Who is resting among the holy ones, praised by the Seraphim with the thrice-holy voice, glorified by the Cherubim, and worshiped by every celestial power, You have brought all things into being out of nothing. You have created man according to Your image and likeness and adorned him with all the gifts of Your grace. You give wisdom and understanding to the one who asks, and You overlook not the sinner, but have set repentance as the way of salvation. You have granted us, Your humble and unworthy servants, to stand even at this hour before the glory of Your holy Altar of sacrifice and to offer to You due worship and praise. Master, accept the Trisagion Hymn also from the lips of us sinners, and visit us in Your goodness. Forgive all our voluntary and involuntary transgressions, sanctify our souls and bodies, and grant that we may worship You in holiness all the days of our lives, through the intercessions of the holy Theotokos and of all the saints who have pleased You throughout the ages.
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key0601.title}{
THE PRAYER OF THE TRISAGION HYMN
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key0602.text}{
Dynamis.
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key0704.text}{
Shine in our hearts, O Master Who loves mankind, the pure light of Your divine knowledge, and open the eyes of our mind that we may comprehend the proclamations of Your Gospels. Instill in us also reverence for Your blessed commandments so that, having trampled down all carnal desires, we may lead a spiritual life, both thinking and doing all those things that are pleasing to You. For You, Christ our God, are the illumination of our souls and bodies, and to You we offer up glory, together with Your Father, Who is without beginning, and Your all-holy, good, and life-creating Spirit, now and forever and to the ages of ages. Amen.
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key0704.title}{
THE PRAYER OF THE HOLY GOSPEL
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key0706.title}{
THE SERMON
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key0708}{
[
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key0709}{
]
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key0800.title}{
THE LITANY OF FERVENT SUPPLICATION
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key0801.text}{
Lord our God, accept this fervent supplication from Your servants, and have mercy on us in accordance with the abundance of Your mercy, and send down Your compassion upon us and upon all Your people who await Your great and rich mercy.
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key0801.title}{
THE PRAYER OF FERVENT SUPPLICATION
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key0900.title}{
THE PRAYERS FOR THE CATECHUMENS
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key0901.text}{
Catechumens, pray to the Lord.
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key0902.text}{
Let us, the faithful, pray for the catechumens.
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key0903.text}{
That the Lord will have mercy on them.
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key0904.text}{
That He will teach them the word of truth.
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key0905.text}{
That He will reveal to them the gospel of righteousness.
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key0906.text}{
That He will unite them to His holy, catholic, and apostolic Church.
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key0907.text}{
Save them, have mercy on them, help them, and protect them, O God, by Your grace.
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key0908.text}{
Catechumens, bow your heads to the Lord.
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key0909.text}{
Lord our God, Who dwells on high and watches over the humble, You sent forth Your only-begotten Son and God, our Lord Jesus Christ, for the salvation of the human race. Look down upon Your servants, the catechumens, who have inclined their necks to You, and grant them at a proper time the baptism of rebirth, the remission of sins, and the garment of incorruption. Unite them to Your holy, catholic, and apostolic Church, and number them among Your chosen flock.
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key0909.title}{
THE PRAYER FOR THE CATECHUMENS
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key0910.text}{
So that with us they also may glorify Your most honorable and majestic name, of the Father and of the Son and of the Holy Spirit, now and forever and to the ages of ages.
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key0911.text}{
Those who are catechumens, depart, catechumens depart, all those who are catechumens, depart. Let none of the catechumens remain.
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key0912.text}{
Again and again, in peace, let all of us, the faithful, pray to the Lord.
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key1000.title}{
THE SUPPLICATION OF THE FAITHFUL
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key1001.text}{
We give thanks to You, O Lord God of Hosts, Who has made us worthy to stand even now before Your holy Altar of sacrifice and to fall down before You seeking Your compassion for our sins and those committed in ignorance by the people. Accept, O God, our supplication. Make us worthy to offer You prayers, supplications, and bloodless sacrifices for all Your people. By the power of Your Holy Spirit, make us, whom You have appointed to this, Your ministry, free of blame or stumbling and, with the witness of a clear conscience, able to call upon You at every time and in every place, so that, hearing us, You may be merciful to us in the abundance of Your goodness.
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key1001.title}{
THE FIRST PRAYER OF THE FAITHFUL
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key1002.text}{
Again and countless times we fall down before You, and we implore You, O Good One, Who loves mankind: That You, having regarded our prayer, may cleanse our souls and bodies from every defilement of flesh and spirit, and grant to us to stand before Your holy Altar of sacrifice, free of guilt and condemnation. Grant also, O God, to those who pray with us, progress in life, faith, and spiritual understanding. Grant that they always worship You with awe and love, partake of Your Holy Mysteries without guilt or condemnation, and be deemed worthy of Your celestial Kingdom.
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key1002.title}{
THE SECOND PRAYER OF THE FAITHFUL
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key1003.text}{
That, ever guarded by Your might, we may ascribe glory to You, to the Father and to the Son and to the Holy Spirit, now and forever and to the ages of ages.
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key1100.title}{
THE GREAT ENTRANCE
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key1101.text}{
No one bound by carnal desires and pleasures is worthy to approach, draw near, or minister to You, the King of Glory. For to serve You is great and awesome even for the heavenly powers. Yet, because of Your ineffable and immeasurable love for mankind, You impassibly and immutably became man. You, as the Master of all, became our high priest and delivered unto us the sacred service of this liturgical sacrifice without the shedding of blood. Indeed, Lord our God, You alone reign over the celestial and the terrestrial; borne aloft on the cherubic throne, Lord of the Seraphim and King of Israel, the only holy and resting among the holy ones. I now beseech You, Who alone are good and inclined to hear: Look down upon me, Your sinful and unprofitable servant, and cleanse my soul and heart of a wicked conscience; and enable me, by the power of Your Holy Spirit, clothed with the grace of the priesthood, to stand before Your holy Table and celebrate the Mystery of Your holy and pure Body and Your precious Blood. I come before You with my head bowed, and I implore You: Turn not Your face away from me, nor reject me from among Your children, but make me, Your sinful and unworthy servant, worthy to offer these gifts to You. For You are the One Who both offers and is offered, the One Who is received and is distributed, O Christ our God, and to You we offer up glory, with Your Father, Who is without beginning, and Your all-holy and good and life-creating Spirit, now and forever and to the ages of ages. Amen.
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key1101.title}{
THE PRAYER OF THE CHERUBIC HYMN
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key1102.text}{
Let us, who mystically represent the Cherubim and who sing the thrice-holy hymn to the life-creating Trinity, now lay aside every worldly care.
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key1102.title}{
The Cherubic Hymn.
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key1103.text}{
So that we may receive the King of all.
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key1110.text}{
May the Lord God remember all of us in His Kingdom always, now and forever and to the ages of ages.
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key1200.title}{
THE LITANY OF COMPLETION
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key1201.text}{
For the precious Gifts here presented, let us pray to the Lord.
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key1202.text}{
Lord God Almighty, You alone are holy. You accept the sacrifice of praise from those who call upon You with their whole heart, even so, accept from us sinners our supplication, and bring it to Your holy Altar of sacrifice. Enable us to offer You gifts and spiritual sacrifices for our own sins and the failings of Your people. Deem us worthy to find grace in Your sight, that our sacrifice may be well pleasing to You, and that the good Spirit of Your grace may rest upon us and upon these gifts presented and upon all Your people.
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key1202.title}{
THE OFFERTORY PRAYER
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key1203.text}{
Through the mercies of Your only begotten Son, with Whom You are blessed, together with Your all-holy, good, and life-creating Spirit, now and forever and to the ages of ages.
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key1204.text}{
Let us love one another, that with oneness of mind we may confess:
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key1205.text}{
Father, Son, and Holy Spirit: Trinity, one in essence and undivided.
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key1208.text}{
The doors! The doors! In wisdom, let us be attentive!
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key1209.title}{
THE SYMBOL OF OUR FAITH
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key1300.title}{
THE HOLY ANAPHORA
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key1301.text}{
Let us stand aright! Let us stand in awe! Let us be attentive, that we may present the Holy Offering in peace.
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key1302.text}{
A mercy of peace, a sacrifice of praise.
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key1303.text}{
The grace of our Lord Jesus Christ, and the love of God and Father, and the communion of the Holy Spirit, be with you all.
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key1304.text}{
And with your spirit.
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key1305.text}{
Let us lift up our hearts.
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key1306.text}{
We lift them up to the Lord.
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key1307.text}{
Let us give thanks to the Lord.
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key1308.text}{
It is proper and right.
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key1309.text}{
It is proper and right to hymn You, to bless You, to praise You, to give thanks to You, and to worship You in every place of Your dominion. For You, O God, are ineffable, inconceivable, invisible, incomprehensible, existing forever, forever the same, You and Your only begotten Son and Your Holy Spirit. You brought us out of nothing into being, and when we had fallen away, You raised us up again. You left nothing undone until you had led us up to heaven and granted us Your Kingdom, which is to come. For all these things, we thank You and Your only begotten Son and Your Holy Spirit: for all things we know and do not know, for blessings manifest and hidden that have been bestowed on us. We thank You also for this Liturgy, which You have deigned to receive from our hands, even though thousands of archangels and tens of thousands of angels stand around You, the Cherubim and Seraphim, six-winged, many­ eyed, soaring aloft upon their wings,
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key1310.text}{
Singing the triumphal hymn, exclaiming, proclaiming, and saying...
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key1311.text}{
Holy, holy, holy, Lord Sabaoth, heaven and earth are filled with Your glory. Hosanna in the highest. Blessed is He Who comes in the name of the Lord. Hosanna in the highest.
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key1312.text}{
Together with these blessed powers, Master, Who loves mankind, we also exclaim and say: Holy are You and most holy, You and Your only­begotten Son and Your Holy Spirit. Holy are You and most holy, and sublime is Your glory. You so loved Your world that You gave Your only begotten Son so that everyone who believes in Him should not perish, but have eternal life. When He had come and fulfilled for our sake the entire plan of salvation, on the night in which He was delivered up, or rather when He delivered Himself up for the life of the world, He took bread in His holy, pure, and blameless hands, and, giving thanks and blessing, He hallowed and broke it, and gave it to His holy disciples and apostles, saying:
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key1313.text}{
Take, eat, this is My Body, which is broken for you for the remission of sins.
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key1314.text}{
Likewise, after partaking of the supper, He took the cup, saying,
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key1315.text}{
Drink of this, all of you; this is My Blood of the new covenant, which is shed for you and for many for the remission of sins.
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key1316.text}{
Remembering, therefore, this saving commandment and all that has been done for our sake: the Cross, the tomb, the Resurrection on the third day, the Ascension into heaven, the enthronement at the right hand, and the second and glorious coming again.
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key1317.text}{
Your own of Your own we offer to You, in all and for all.
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key1318.text}{
We praise You, we bless You, we give thanks to You, and we pray to You, Lord our God.
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key1319.text}{
Once again we offer to You this spiritual worship without the shedding of blood, and we beseech and pray and entreat You: Send down Your Holy Spirit upon us and upon the gifts here presented,
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key1321.text}{
And make this Bread the precious Body of Your Christ.
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key1323.text}{
And that which is in this Cup, the precious Blood of Your Christ.
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key1325.text}{
Changing them by Your Holy Spirit.
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key1326.text}{
So that they may be for those who partake of them for vigilance of soul, remission of sins, communion of Your Holy Spirit, fullness of the Kingdom of Heaven, boldness before You, not for judgment or condemnation. Again, we offer You this spiritual worship for those who have reposed in the faith: forefathers, fathers, patriarchs, prophets, apostles, preachers, evangelists, martyrs, confessors, ascetics, and for every righteous spirit made perfect in faith,
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key1327.text}{
Especially for our most holy, pure, blessed, and glorious Lady, the Theotokos and ever-virgin Mary.
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key1329.text}{
For Saint John the prophet, forerunner, and Baptist; for the holy, glorious, and most praiseworthy apostles; for Saint(s) (Name), whose memory we celebrate; and for all Your saints, through whose supplications, visit us, O God. And remember all who have fallen asleep in the hope of the resurrection to life eternal (here the Priest commemorates by name those departed whom he wishes). Grant them rest, O our God, where the light of Your countenance keeps watch. Again we beseech You, Lord, remember all Orthodox bishops who rightly teach the word of Your truth, the presbyterate, the diaconate in Christ, and every priestly and monastic order. Again we offer You this spiritual worship for the whole world, for the holy, catholic, and apostolic Church, and for those living pure and reverent lives. For civil authorities and our armed forces, grant that they may govern in peace, Lord, so that in their tranquility we, too, may live calm and serene lives, in all piety and virtue.
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key1330a.text}{
Among the first remember, Lord,
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key1330b.text}{
grant him to Your holy churches in peace, safety, honor, and health, unto length of days, rightly teaching the word of Your truth.
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key1331.text}{
And remember those whom each one of us has in mind, and all the people.
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key1332.text}{
And all the people.
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key1333.text}{
Remember, Lord, this city in which we live, and every city and land, and the faithful who live in them. Remember, Lord, those who travel by land, sea, and air; the sick; the suffering; the captives; and their salvation. Remember those who bear fruit and do good works in Your holy churches and those who are mindful of the poor, and upon us all send forth Your mercies.
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key1334.text}{
And grant that with one voice and one heart we may glorify and praise Your most honorable and majestic name, of the Father and of the Son and of the Holy Spirit, now and forever and to the ages of ages.
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key1335.text}{
And the mercies of our great God and Savior, Jesus Christ, be with you all.
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key1336.text}{
And with your spirit.
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key1401.text}{
Having commemorated all the saints, again and again, in peace, let us pray to the Lord.
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key1402.text}{
For the precious Gifts here presented and consecrated, let us pray to the Lord.
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key1403.text}{
That our God Who loves mankind, having accepted them at His holy and celestial and mystical altar as an offering of spiritual fragrance, may in return send down upon us the divine grace and the gift of the Holy Spirit, let us pray.
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key1404.text}{
Having asked for the unity of the faith and for the communion of the Holy Spirit, let us commend ourselves and one another and our whole life to Christ our God.
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key1405.text}{
We entrust to You, loving Master, our whole life and hope, and we beseech, pray, and implore You: Grant us to partake of Your heavenly and awesome Mysteries from this sacred and spiritual table with a clear conscience for the remission of sins, the forgiveness of transgressions, the communion of the Holy Spirit, the inheritance of the Kingdom of Heaven, and boldness before You, not unto judgment or condemnation.
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key1406.text}{
And grant us, Master, with boldness and without condemnation, to dare call You, the heavenly God, Father, and to say:
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key1407.text}{
We give thanks to You, invisible King, Who by Your boundless power fashioned the universe, and in the multitude of Your mercy brought all things from nothing into being. Look down from heaven, O Master, upon those who have bowed their heads before You, for they have not bowed before flesh and blood, but before You, the awesome God. Therefore, O Master, make smooth and beneficial for us all, whatever lies ahead, according to the need of each: Sail with those who sail, travel with those who travel, heal the sick, Physician of our souls and bodies.
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key1409.text}{
Hearken, O Lord Jesus Christ our God, from Your holy dwelling place and from the throne of glory of Your Kingdom, and come to sanctify us, You Who are enthroned with the Father on high and are present among us invisibly here. And with Your mighty hand, grant Communion of Your most pure Body and precious Blood to us, and through us to all the people.
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key1409.title}{
THE HOLY COMMUNION
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key1410.text}{
The Holy Gifts for the holy people of God.
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key1411.text}{
One is Holy, one is Lord, Jesus Christ, to the glory of God the Father. Amen.
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key1526.text}{
With the fear of God, faith, and love, draw near.
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key1527.text}{
The servant of God (Name) partakes of the Body and Blood of Christ for the remission of sins and life eternal.
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key1528.rubric}{
And the people receive Holy Communion. The Priest receives the holy Chalice from the hands of the Deacon and begins communing the people, saying to each one:
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key1529.text}{
Save, O God, Your people, and bless Your inheritance.
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key1530.text}{
We have seen the true light; we have received the heavenly Spirit; we have found the true faith, as we worship the undivided Trinity; for the Trinity has saved us.
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key1603.text}{
Let our mouths be filled with Your praise, O Lord, that we may sing of Your glory, because You have made us worthy to partake of Your Holy Mysteries. Keep us in Your sanctification, that all day long we may meditate upon Your righteousness. Alleluia. Alleluia. Alleluia.
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key1604.text}{
Arise! Having partaken of the divine, holy, pure, immortal, heavenly, life-creating, and awesome Mysteries of Christ, let us worthily give thanks to the Lord.
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key1605.text}{
Having prayed for a perfect, holy, peaceful, and sinless day, let us commend ourselves and one another and our whole life to Christ our God.
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key1606.text}{
We give thanks to You, Master Who loves mankind, benefactor of our souls, that even on this very day You have made us worthy of Your heavenly and immortal Mysteries. Make straight our path, fortify us in Your fear, guard our life, make secure our steps, through the prayers and supplications of the glorious Theotokos and ever­ virgin Mary and of all Your saints.
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key1606.title}{
THE THANKSGIVING PRAYER
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key1700.title}{
DISMISSAL
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key1701.text}{
Let us go forth in peace.
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key1702.text}{
O Lord, Who blesses those who bless You and sanctifies those who put their trust in You, save Your people and bless Your inheritance. Protect the whole body of Your Church. Sanctify those who love the beauty of Your house. Glorify them in return by Your divine power, and forsake us not who have set our hope in You. Grant peace to Your world, to Your churches, to the clergy, to our civic leaders, to the armed forces, and to all Your people. For every good and perfect gift is from above, coming down from You, the Father of lights. To You we give glory, thanksgiving, and worship, to the Father and to the Son and to the Holy Spirit, now and forever and to the ages of ages.
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key1702.title}{
THE PRAYER BEHIND THE AMBON
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.Key1704.text}{
Christ our God, You are the fulfillment of the Law and the Prophets. You have fulfilled the Father's entire plan of salvation. Fill our hearts with joy and gladness always, now and forever and to the ages of ages. Amen.
}%
\itId{en}{us}{ages}{eu.lichrysbasil}{euLI.MM.HymnsDuringCommunion.title}{
Hymns During Holy Communion
}%
\itId{en}{us}{ages}{ho.s07}{hoLI.Antiphon1.text}{
At the prayers of the Mother of God, O Saviour, save us.
}%
\itId{en}{us}{ages}{ho.s07}{hoLI.Antiphon21.text}{
Son of God,
}%
\itId{en}{us}{ages}{ho.s07}{hoLI.Antiphon22.text}{
save us who sing to you: Alleluia!
}%
\itId{en}{us}{ages}{ho.s07}{hoLI.Antiphon2s.text}{
risen from the dead,
}%
\itId{en}{us}{ages}{ho.s07}{hoLI.EntranceHymn.text}{
Come, let us worship and fall down before Christ. Son of God, risen from the dead, save us who sing to you: Alleluia!
}%
\itId{en}{us}{ages}{ho.s07}{hoLI.OnlyBegotten.text}{
Only-begotten Son and Word of God, who, being immortal, accepted for our salvation to take flesh from the holy Mother of God and Ever-Virgin Mary, and without change became man; you were crucified, Christ God, by death trampling on death, being one of the Holy Trinity, glorified with the Father and the Holy Spirit: save us!
}%
\itId{en}{us}{ages}{ho.s07}{hoLI.TrisagiosHymn.text}{
Holy God, Holy Strong, Holy Immortal, have mercy on us.
}%
\itId{en}{us}{ages}{ho.s07}{hoLI.TrisagiosHymn3.text}{
Holy Immortal,
}%
\itId{en}{us}{ages}{ho.s07}{hoLI.TrisagiosHymn4.text}{
have mercy on us.
}%
\itId{en}{us}{ages}{ho.s21}{hoPrayer.Key101.text}{
I believe and confess, Lord, that You are truly the Christ, the Son of the living God, Who came into the world to save sinners, of whom I am the first. I also believe that this is truly Your pure Body and that this is truly Your precious Blood. Therefore, I pray to You, have mercy upon me, and forgive my transgressions, voluntary and involuntary, in word and deed, in knowledge or in ignorance. And make me worthy, without condemnation, to partake of Your pure Mysteries for the remission of sins and for eternal life. Amen.
}%
\itId{en}{us}{ages}{ho.s21}{hoPrayer.Key110.text}{
Behold, I approach for Divine Communion. * O Maker, burn me not as I partake, * for You are fire consuming the unworthy. * But cleanse me from every stain.
}%
\itId{en}{us}{ages}{ho.s21}{hoPrayer.Key121.text}{
O Son of God, receive me today as a partaker of Your mystical supper. For I will not speak of the mystery to Your enemies, nor will I give You a kiss, as did Judas. But like the thief, I confess to You: Remember me, Lord, in Your Kingdom.
}%
\itId{en}{us}{ages}{ho.s21}{hoPrayer.Key161.text}{
Master Who loves mankind, Lord Jesus Christ, my God, let not these Holy Gifts be to my judgment because I am unworthy, but rather for the purification and sanctification of both soul and body and the pledge of the life and Kingdom to come. It is good for me to cleave unto God and to place in Him the hope of my salvation.
}%
\itId{en}{us}{ages}{ho.s21}{hoPrayer.title}{
PRAYERS OF HOLY COMMUNION
}%
\itId{en}{us}{ages}{ho.s99}{bede.text}{
Orthodoxy's guide, teacher of piety and reverence, beacon of the world, fair ornament of monks. Inspired by God, o, wise Bede, by your teaching you have enlightened all; o, harp of the Spirit, intercede with Christ God, that our souls may be saved.
}%
\itId{en}{us}{ages}{ho.s99}{cuthbert.text}{
Faithful guide of Northumbria's Church an example of meekness and humility in fasting, vigils and in prayer an adornment of bishops and the glory of monks. O Holy Cuthbert, you dwell now in the light which knows no evening standing at the throne of God. Remember those that honour you and ask of Christ to have mercy on us.
}%
\itId{en}{us}{ages}{ho.s99}{silouan.text}{
You received and knew the Holy Spirit and acquired fully Adam’s tears. With unquenchable thirst and desire for Christ you kept your mind in hell by repentance and thus obtained the great love for all nations. Father Silouan, ever pray before God to grant to us His Holy Sprit and His great mercy.
}%
\itId{en}{us}{ages}{liturgical.verses}{psLI.aftercommunion.v1.text}{
Blessed be the name of the Lord, from this time forth and to the ages.
}%
\itId{en}{us}{ages}{me.m10.d28}{alt1.meLI.Antiphon2.text}{
Son of God, wonderful in the Saints, save us who sing to you: Alleluia!
}%
\itId{en}{us}{ages}{misc}{vVerse1}{
1st Verse
}%
\itId{en}{us}{ages}{misc}{vVerse2}{
2nd Verse
}%
\itId{en}{us}{ages}{misc}{vVerse3}{
3rd Verse
}%
\itId{en}{us}{ages}{prayers}{Allilouia3.text}{
Alleluia. Alleluia. Alleluia.
}%
\itId{en}{us}{ages}{prayers}{AxionEstinComplete.text}{
It is truly right to call you blessed, who gave birth to God, ever-blessed and most pure, and Mother of our God. Greater in honour than the Cherubim and beyond compare more glorious than the Seraphim, without corruption you gave birth to God the Word; truly the Mother of God, we magnify you.
}%
\itId{en}{us}{ages}{prayers}{DiEfchonPateron.text}{
Through the prayers of our holy fathers Lord Jesus Christ, our God have mercy upon us.
}%
\itId{en}{us}{ages}{prayers}{DoxaPatri}{
Glory to the Father, and to the Son, and to the Holy Spirit.
}%
\itId{en}{us}{ages}{prayers}{DoxaSoiKyrie}{
Glory to You, O Lord, glory to You.
}%
\itId{en}{us}{ages}{prayers}{DoxaSoiOTheosImon.text}{
Glory to You, our God. Glory to You.
}%
\itId{en}{us}{ages}{prayers}{KaiNynKaiAei.text}{
Both now and for ever, and to the ages of ages. Amen.
}%
\itId{en}{us}{ages}{prayers}{PantoteNyn.text}{
Always, now and forever and to the ages of ages.
}%
\itId{en}{us}{ages}{prayers}{PaterImon.text}{
Our Father, who art in heaven, hallowed be Thy name. Thy kingdom come, Thy will be done, on earth as it is in heaven. Give us this day our daily bread; and forgive us our trespasses, as we forgive those who trespass against us. And lead us not into temptation, but deliver us from evil.
}%
\itId{en}{us}{ages}{prayers}{Pistevo.text}{
I believe in one God, Father Almighty, Creator of heaven and earth, and of all things visible and invisible. And in one Lord Jesus Christ, the only-begotten Son of God, begotten of the Father before all ages; Light of Light, true God of true God, begotten, not created, of one essence with the Father through Whom all things were made. Who for us men and for our salvation came down from heaven and was incarnate of the Holy Spirit and the Virgin Mary and became man. He was crucified for us under Pontius Pilate, and suffered and was buried; And He rose on the third day, according to the Scriptures. He ascended into heaven and is seated at the right hand of the Father; And He will come again with glory to judge the living and dead. His kingdom shall have no end. And in the Holy Spirit, the Lord, the Creator of life, Who proceeds from the Father, Who together with the Father and the Son is worshipped and glorified, Who spoke through the prophets. In one, holy, catholic, and apostolic Church. I confess one baptism for the forgiveness of sins. I look for the resurrection of the dead, and the life of the age to come. Amen.
}%
\itId{en}{us}{ages}{prayers}{enarxis02}{
Blessed is the Kingdom of the Father, and of the Son, and of the Holy Spirit, now and for ever and to the ages of ages.
}%
\itId{en}{us}{ages}{prayers}{epi02}{
Peace be with you.
}%
\itId{en}{us}{ages}{prayers}{exc01}{
For to You belong all glory, honor, and worship, to the Father and to the Son and to the Holy Spirit, now and forever and to the ages of ages.
}%
\itId{en}{us}{ages}{prayers}{exc02}{
For Yours is the dominion, and Yours is the kingdom and the power and the glory, of the Father and of the Son and of the Holy Spirit, now and forever and to the ages of ages.
}%
\itId{en}{us}{ages}{prayers}{exc03}{
For You, O God, are good and love mankind, and to You we offer glory, to the Father and to the Son and to the Holy Spirit, now and forever, and to the ages of ages.
}%
\itId{en}{us}{ages}{prayers}{exc05a}{
For You, our God, are holy, and to You we offer up glory, to the Father and to the Son and to the Holy Spirit, now and forever,
}%
\itId{en}{us}{ages}{prayers}{exc05b}{
And to the ages of ages.
}%
\itId{en}{us}{ages}{prayers}{exc07a}{
Through the grace, compassion, and love for mankind of Your only begotten Son, with whom You are blessed, together with Your all-holy, good, and life-creating Spirit, now and forever and to the ages of ages.
}%
\itId{en}{us}{ages}{prayers}{exc11}{
For You are a merciful God Who loves mankind, and to You we offer up glory, to the Father and to the Son and to the Holy Spirit, now and forever and to the ages of ages.
}%
\itId{en}{us}{ages}{prayers}{exc17}{
Wisdom.
}%
\itId{en}{us}{ages}{prayers}{exc18}{
Stand upright.
}%
\itId{en}{us}{ages}{prayers}{exc19}{
Let us be attentive.
}%
\itId{en}{us}{ages}{prayers}{exc20}{
For Thine is the Kingdom and the power and the glory, of the Father and of the Son and of the Holy Spirit, now and forever and to the ages of ages.
}%
\itId{en}{us}{ages}{prayers}{exc24}{
For You are our sanctification, and to You we give glory, to the Father and to the Son and to the Holy Spirit, now and forever and to the ages of ages.
}%
\itId{en}{us}{ages}{prayers}{gos02}{
Let us listen to the Holy Gospel.
}%
\itId{en}{us}{ages}{prayers}{gos03a}{
The reading is from the Holy Gospel according to
}%
\itId{en}{us}{ages}{prayers}{gos03b}{
}%
\itId{en}{us}{ages}{prayers}{gos04}{
Peace be with you.
}%
\itId{en}{us}{ages}{prayers}{pet00}{
Let us pray to the Lord.
}%
\itId{en}{us}{ages}{prayers}{pet01}{
In peace, let us pray to the Lord.
}%
\itId{en}{us}{ages}{prayers}{pet02}{
For the peace from above and for the salvation of our souls, let us pray to the Lord.
}%
\itId{en}{us}{ages}{prayers}{pet03}{
For the peace of the whole world, for the stability of the holy churches of God, and for the unity of all, let us pray to the Lord.
}%
\itId{en}{us}{ages}{prayers}{pet04}{
For this holy house and for those who enter it with faith, reverence, and the fear of God, let us pray to the Lord.
}%
\itId{en}{us}{ages}{prayers}{pet05}{
For pious and Orthodox Christians, let us pray to the Lord.
}%
\itId{en}{us}{ages}{prayers}{pet06a}{
For
}%
\itId{en}{us}{ages}{prayers}{pet06b}{
for the honorable presbyterate, for the diaconate in Christ, and for all the clergy and the people, let us pray to the Lord.
}%
\itId{en}{us}{ages}{prayers}{pet07S}{
For our country, for the president, and for all in public service, let us pray to the Lord.
}%
\itId{en}{us}{ages}{prayers}{pet08}{
For this city, and for every city and land, and for the faithful who live in them, let us pray to the Lord.
}%
\itId{en}{us}{ages}{prayers}{pet09}{
For favorable weather, for an abundance of the fruits of the earth, and for peaceful times, let us pray to the Lord.
}%
\itId{en}{us}{ages}{prayers}{pet10}{
For those who travel by land, sea, and air, for the sick, the suffering, the captives and for their salvation, let us pray to the Lord.
}%
\itId{en}{us}{ages}{prayers}{pet11}{
For our deliverance from all affliction, wrath, danger and distress, and from the peril of the coronavirus against us, let us pray to the Lord.
}%
\itId{en}{us}{ages}{prayers}{pet12}{
Help us, save us, have mercy on us, and protect us, O God, by Your grace.
}%
\itId{en}{us}{ages}{prayers}{pet13}{
Commemorating our most holy, pure, blessed, and glorious Lady, the Theotokos and ever-virgin Mary, with all the saints, let us commend ourselves and one another and our whole life to Christ our God.
}%
\itId{en}{us}{ages}{prayers}{pet14}{
Again and again, in peace, let us pray to the Lord.
}%
\itId{en}{us}{ages}{prayers}{pet15}{
Let us all say with all our soul and with all our mind, let us all say.
}%
\itId{en}{us}{ages}{prayers}{pet16}{
Lord almighty, God of our fathers, we pray You, hear us and have mercy.
}%
\itId{en}{us}{ages}{prayers}{pet17}{
Have mercy on us, O God, according to Your great mercy, we pray You, hear us and have mercy.
}%
\itId{en}{us}{ages}{prayers}{pet19Sa}{
Also we pray for
}%
\itId{en}{us}{ages}{prayers}{pet20}{
Also we pray for our Sovereign Lord, King Charles, the Royal Family, his Government, and all in authority.
}%
\itId{en}{us}{ages}{prayers}{pet21}{
Again we pray for mercy, life, peace, health, salvation, protection, forgiveness, and remission of the sins of the servants of God, all pious Orthodox Christians residing and visiting in this city: the parishioners, the members of the parish council, the stewards, and benefactors of this holy church.
}%
\itId{en}{us}{ages}{prayers}{pet22}{
Again we pray for the blessed and ever-memorable founders of this holy church, and for all our fathers and brethren who have fallen asleep before us, who here have been piously laid to their rest, as well as the Orthodox everywhere.
}%
\itId{en}{us}{ages}{prayers}{pet23}{
Again we pray for those who bear fruit and do good works in this holy and all-venerable church, for those who labor and those who sing, and for the people here present who await Your great and rich mercy.
}%
\itId{en}{us}{ages}{prayers}{pet24}{
Let us complete our prayer to the Lord.
}%
\itId{en}{us}{ages}{prayers}{pet25m}{
That the whole day may be perfect, holy, peaceful, and sinless, let us ask the Lord.
}%
\itId{en}{us}{ages}{prayers}{pet26}{
For an angel of peace, a faithful guide, a guardian of our souls and bodies, let us ask the Lord.
}%
\itId{en}{us}{ages}{prayers}{pet27}{
For pardon and remission of our sins and transgressions, let us ask the Lord.
}%
\itId{en}{us}{ages}{prayers}{pet28}{
For that which is good and beneficial for our souls, and for peace for the world, let us ask the Lord.
}%
\itId{en}{us}{ages}{prayers}{pet29}{
That we may complete the remaining time of our life in peace and repentance, let us ask the Lord.
}%
\itId{en}{us}{ages}{prayers}{pet30}{
And let us ask for a Christian end to our life, peaceful, without shame and suffering, and for a good defense before the awesome judgment seat of Christ.
}%
\itId{en}{us}{ages}{prayers}{pet31}{
Peace to all.
}%
\itId{en}{us}{ages}{prayers}{pet32}{
Let us bow our heads to the Lord.
}%
\itId{en}{us}{ages}{prayers}{pet37}{
May the blessing and the mercy of the Lord come upon you by His divine grace and love for mankind, always, now and forever and to the ages of ages.
}%
\itId{en}{us}{ages}{prayers}{res01}{
Lord, have mercy.
}%
\itId{en}{us}{ages}{prayers}{res02}{
Grant this, O Lord.
}%
\itId{en}{us}{ages}{prayers}{res03}{
To You, O Lord.
}%
\itId{en}{us}{ages}{prayers}{res04}{
Amen.
}%
\itId{en}{us}{ages}{prayers}{res05}{
And to your spirit.
}%
\itId{en}{us}{ages}{prayers}{res06}{
Lord, have mercy. Lord, have mercy. Lord, have mercy.
}%
\itId{en}{us}{ages}{prayers}{res08}{
Master, give the blessing.
}%
\itId{en}{us}{ages}{prayers}{res10}{
Amen. Amen. Amen.
}%
\itId{en}{us}{ages}{prayers}{res13}{
Holy Master, give the blessing.
}%
\itId{en}{us}{ages}{ps}{psa102.v1.text}{
Bless the Lord, O my soul, and all that is within me, bless his holy name.
}%
\itId{en}{us}{ages}{ps}{psa102.v19.text}{
The Lord has prepared his throne in heaven, and his kingdom rules over all.
}%
\itId{en}{us}{ages}{ps}{psa102.v2.text}{
Bless the Lord, O my soul, and forget none of his benefits.
}%
\itId{en}{us}{ages}{ps}{psa117.v1.text}{
Give thanks to the Lord, for he is good, for his mercy endures for ever.
}%
\itId{en}{us}{ages}{ps}{psa145.v1.text}{
Praise the Lord, O my soul:
}%
\itId{en}{us}{ages}{ps}{psa145.v10.text}{
The Lord will be king for ever: your God, O Sion, will reign throughout all generations.
}%
\itId{en}{us}{ages}{ps}{psa145.v2.text}{
while I live, I will praise the Lord; while I exist, I will praise my God.
}%
\itId{en}{us}{ages}{ps}{psa145.v5.text}{
Blessed are those whose helper is the God of Jacob; whose hope is in the Lord their God.
}%
\itId{en}{us}{ages}{ps}{psa68.v35.text}{
Let the heavens and the earth sing his praise.
}%
\itId{en}{us}{ages}{pub.priest.servicebook}{doxapatrikainyn}{
Glory to the Father, and to the Son, and to the Holy Spirit, both now and for ever, and to the ages of ages. Amen.
}%
\itId{en}{us}{ages}{pub.priest.servicebook}{li.blessboth}{
Master, bless them both.
}%
\itId{en}{us}{ages}{pub.priest.servicebook}{li.blessingmercy}{
May the blessing and mercy of the Lord come upon you.
}%
\itId{en}{us}{ages}{pub.priest.servicebook}{li.blessreader}{
Master, bless the herald of the Good Tidings of the Holy Apostle and Evangelist N.
}%
\itId{en}{us}{ages}{pub.priest.servicebook}{li.blessreader2}{
May God, through the prayers of the holy, glorious Apostle and Evangelist N., grant you to proclaim the word with much power, for the fulfilling of the Gospel of his Beloved Son, our Lord Jesus Christ.
}%
\itId{en}{us}{ages}{pub.priest.servicebook}{li.changebread}{
Master, bless the holy Bread.
}%
\itId{en}{us}{ages}{pub.priest.servicebook}{li.changewine}{
Master, bless the holy Cup.
}%
\itId{en}{us}{ages}{pub.priest.servicebook}{li.dis.oanastas}{
May
}%
\itId{en}{us}{ages}{pub.priest.servicebook}{li.end.title.doc}{
The End of the Divine Liturgy of John Chrysostom
}%
\itId{en}{us}{ages}{pub.priest.servicebook}{li.godisthelord}{
Blessed is he who comes in the name of the Lord. The Lord is God and has appeared to us.
}%
\itId{en}{us}{ages}{pub.priest.servicebook}{li.litanylordsprayer.title.doc}{
LITANY OF THE LORD'S PRAYER
}%
\itId{en}{us}{ages}{pub.priest.servicebook}{li.lordsname}{
In the name of the Lord.
}%
\itId{en}{us}{ages}{pub.priest.servicebook}{li.preparation.mercy}{
God, cleanse me a sinner.
}%
\itId{en}{us}{ages}{pub.priest.servicebook}{li.prokeimenonmode}{
Prokeimenon of the Apostle. Tone... A Psalm of David.
}%
\itId{en}{us}{ages}{pub.priest.servicebook}{li.readings.title.doc}{
The Readings from the New Testament
}%
\itId{en}{us}{ages}{pub.priest.servicebook}{li.rubric.alldays}{
Then, on all days:
}%
\itId{en}{us}{ages}{pub.priest.servicebook}{li.rubric.bede}{
Tone 8. St Bede
}%
\itId{en}{us}{ages}{pub.priest.servicebook}{li.rubric.blesswithgospel}{
The Priest takes the Gospel from the Deacon, kisses it and blesses the people with it. He then replaces it on the Holy Table.
}%
\itId{en}{us}{ages}{pub.priest.servicebook}{li.rubric.bowcommunion}{
Then the Priest, and the Deacon, in his usual place, bow three times, saying
}%
\itId{en}{us}{ages}{pub.priest.servicebook}{li.rubric.catechumens}{
Here may follow the Litany for the Catechumens, this is, those preparing for baptism.
}%
\itId{en}{us}{ages}{pub.priest.servicebook}{li.rubric.catechumens2}{
To each petition the People answer:
}%
\itId{en}{us}{ages}{pub.priest.servicebook}{li.rubric.cuthbert}{
Tone 8. St Cuthbert
}%
\itId{en}{us}{ages}{pub.priest.servicebook}{li.rubric.deaconquietly}{
The Deacon, in a low voice, says:
}%
\itId{en}{us}{ages}{pub.priest.servicebook}{li.rubric.eachpetition}{
And so after each petition.
}%
\itId{en}{us}{ages}{pub.priest.servicebook}{li.rubric.eachpetition2}{
And so after each of the following petitions.
}%
\itId{en}{us}{ages}{pub.priest.servicebook}{li.rubric.giveantidoron}{
The Priest distributes the Antidoron, saying to each recipient:
}%
\itId{en}{us}{ages}{pub.priest.servicebook}{li.rubric.kontakion1}{
The Apolytikia for the day and for the dedication of the Church are sung:
}%
\itId{en}{us}{ages}{pub.priest.servicebook}{li.rubric.notsunday}{
On weekdays, outside Eastertide, or a feast of the Lord, we sing after each verse:
}%
\itId{en}{us}{ages}{pub.priest.servicebook}{li.rubric.preach}{
Then the Preacher instructs the people in the word of God.
}%
\itId{en}{us}{ages}{pub.priest.servicebook}{li.rubric.readgospel}{
The Deacon reads the Gospel for the day. When it is finished the Priest blesses the Deacon saying:
}%
\itId{en}{us}{ages}{pub.priest.servicebook}{li.rubric.resurrectionmode}{
Then the Resurrection Apolytikion of the current Tone.
}%
\itId{en}{us}{ages}{pub.priest.servicebook}{li.rubric.silouan}{
Tone 3. St Silouan
}%
\itId{en}{us}{ages}{pub.priest.servicebook}{li.rubric.smallentrance}{
While the Doxastikon of the Beatitudes, or the Third Antiphon, is being sung, the Priest and Deacon, standing in front of the Holy Table, make three bows; then the Priest takes the holy Gospel and gives it to the Deacon, who kisses the Priest’s hand. And so they come out through the north door, preceded by lights, and make the Little Entrance. Standing in the middle of the Church they bow their heads.
}%
\itId{en}{us}{ages}{pub.priest.servicebook}{li.rubric.sundayantifon3}{
Then the Beatitudes, or the Third Antiphon, are sung. On Sundays the following Antiphon may be used:
}%
\itId{en}{us}{ages}{pub.priest.servicebook}{li.rubric.sundaydismissal}{
(on Sundays: he who rose from the dead,)
}%
\itId{en}{us}{ages}{pub.priest.servicebook}{li.rubric.thriceeach}{
Three times. And so after the remaining petitions.
}%
\itId{en}{us}{ages}{pub.priest.servicebook}{li.thanksdismissal.title.doc}{
THANKSGIVING AND DISMISSAL
}%
\itId{en}{us}{ages}{rubrical}{BeginLiturgy}{
The Priest, lifting up the book of the Gospel, and making the sign of the Cross with it over the Antimension, says in a clear voice:
}%
\itId{en}{us}{ages}{rubrical}{DeaconStart}{
The Deacon, having received a blessing from the Priest, comes out of the Sanctuary by the North Door and, standing in his usual place in front of the Holy Doors, makes three bows and begins:
}%
\itId{en}{us}{ages}{rubrical}{InALowVoice}{
(in a low voice)
}%
\itId{en}{us}{ages}{rubrical}{Or}{
ἤ·
}%
\itId{en}{us}{ages}{rubrical}{Thrice}{
(3)
}%
\itId{en}{us}{ages}{rubrical}{cl.eu.lichrysbasil.R009}{
The Reader reads the title of the Apostle.
}%
\itId{en}{us}{ages}{rubrical}{cl.eu.lichrysbasil.R010}{
The Reader reads the Apostle, and when he has finished the priest says:
}%
\itId{en}{us}{ages}{template.titles}{li2.html.tab}{
The Divine Liturgy of Our Father Among the Saints John Chrysostom
}%
\itId{en}{us}{ages}{template.titles}{li2.html.tab.doc}{
The Divine Liturgy of Our Father Among the Saints John Chrysostom
}%
\itId{en}{us}{ages}{template.titles}{li2.html.tab.header}{
The Divine Liturgy of Our Father Among the Saints John Chrysostom
}%
\itId{en}{us}{ages}{template.titles}{li2.html.tab.toc}{
The Divine Liturgy of Our Father Among the Saints John Chrysostom
}%
\itId{en}{us}{ages}{titles}{Eisodikon}{
Entrance Hymn.
}%
\itId{en}{us}{ages}{titles}{KyriakiProsefchi}{
THE LORD'S PRAYER
}%
\itId{en}{us}{ages}{titles}{LitCatechumens}{
The Liturgy of the Catechumens
}%
\itId{en}{us}{ages}{variables.info}{Antiphon1.title}{
The 1st Antiphon
}%
\itId{en}{us}{ages}{variables.info}{Antiphon2.title}{
The 2nd Antiphon
}%
\itId{en}{us}{ages}{variables.info}{TheotokosHymn.title}{
Hymn to the Theotokos
}%
\itId{en}{us}{ages}{variables.info}{Trisagion.title}{
Trisagion Hymn
}%
\itId{gr}{gr}{ages}{actors}{Deacon}{
ΔΙΑΚΟΝΟΣ
}%
\itId{gr}{gr}{ages}{actors}{Deacon.colon}{
\itRid{actors}{Deacon}:
}%
\itId{gr}{gr}{ages}{actors}{People}{
ΛΑΟΣ
}%
\itId{gr}{gr}{ages}{actors}{People.colon}{
\itRid{actors}{People}:
}%
\itId{gr}{gr}{ages}{actors}{Priest}{
ΙΕΡΕΥΣ
}%
\itId{gr}{gr}{ages}{actors}{Priest.colon}{
\itRid{actors}{Priest}:
}%
\itId{gr}{gr}{ages}{actors}{Reader}{
ΑΝΑΓΝΩΣΤΗΣ
}%
\itId{gr}{gr}{ages}{actors}{Reader.colon}{
\itRid{actors}{Reader}:
}%
\itId{gr}{gr}{ages}{client}{cl.bishop1.name.c}{
(τοῦ δεῖνος),
}%
\itId{gr}{gr}{ages}{client}{cl.bishop1.name.p}{
(τοῦ δεῖνος).
}%
\itId{gr}{gr}{ages}{client}{cl.bishop1.rank}{
τοῦ (ἀρχιερατικοῦ βαθμοῦ) ἡμῶν
}%
\itId{gr}{gr}{ages}{dismissals}{dis01}{
Χριστὸς ὁ ἀληθινὸς Θεὸς ἡμῶν,
}%
\itId{gr}{gr}{ages}{dismissals}{dis02}{
ταῖς πρεσβείαις τῆς παναχράντου καὶ παναμώμου ἁγίας αὐτοῦ Μητρός,
}%
\itId{gr}{gr}{ages}{dismissals}{dis03}{
δυνάμει τοῦ τιμίου καὶ ζωοποιοῦ Σταυροῦ,
}%
\itId{gr}{gr}{ages}{dismissals}{dis04}{
προστασίαις τῶν τιμίων ἐπουρανίων Δυνάμεων Ἀσωμάτων,
}%
\itId{gr}{gr}{ages}{dismissals}{dis05}{
ἱκεσίαις τοῦ τιμίου, ἐνδόξου, προφήτου, Προδρόμου καὶ βαπτιστοῦ Ἰωάννου,
}%
\itId{gr}{gr}{ages}{dismissals}{dis06}{
τῶν ἁγίων ἐνδόξων καὶ πανευφήμων Ἀποστόλων,
}%
\itId{gr}{gr}{ages}{dismissals}{dis07}{
τῶν ἁγίων ἐνδόξων καὶ καλλινίκων μαρτύρων·
}%
\itId{gr}{gr}{ages}{dismissals}{dis08}{
τῶν ὁσίων καὶ θεοφόρων Πατέρων ἡμῶν·
}%
\itId{gr}{gr}{ages}{dismissals}{dis09}{
τῶν ἁγίων καὶ δικαίων Θεοπατόρων Ἰωακεὶμ καὶ Ἄννης,
}%
\itId{gr}{gr}{ages}{dismissals}{dis10}{
καὶ πάντων τῶν Ἁγίων,
}%
\itId{gr}{gr}{ages}{dismissals}{dis89}{
ἐλεήσαι καὶ σώσαι ἡμᾶς, ὡς ἀγαθὸς καὶ φιλάνθρωπος.
}%
\itId{gr}{gr}{ages}{dismissals}{li.dis.chrysostom}{
τοῦ ἐν ἁγίοις πατρὸς ἡμῶν Ἰωάννου ἀριχιεπισκόπου Κωνσταντινουπόλεως τοῦ Χρυσοστόμου,
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key0200.text}{
ΜΕΓΑΛΗ ΣΥΝΑΠΤΗ ἢ ΕΙΡΗΝΙΚΑ
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key0201.text}{
Κύριε ὁ Θεὸς ἡμῶν, οὗ τὸ κράτος ἀνείκαστον καὶ ἡ δόξα ἀκατάληπτος, οὗ τὸ ἔλεος ἀμέτρητον καὶ ἡ φιλανθρωπία ἄφατος. Αὐτὸς Δέσποτα, κατὰ τὴν εὐσπλαχνίαν σου, ἐπίβλεψον ἐφ' ἡμᾶς καὶ ἐπὶ τὸν ἅγιον οἶκον τοῦτον καὶ ποίησον μεθ' ἡμῶν, καί τῶν συνευχομένων ἡμῖν, πλούσια τὰ ἐλέη σου καί τοὺς οἰκτιρμούς σου.
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key0201.title}{
ΕΥΧΗ ΑΝΤΙΦΩΝΟΥ Αʹ
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key0202.title}{
ΜΙΚΡΑ ΣΥΝΑΠΤΗ
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key0301.text}{
Κύριε, ὁ Θεὸς ἡμῶν, σῶσον τὸν λαόν σου καὶ εὐλόγησον τὴν κληρονομίαν σου, τὸ πλήρωμα τῆς ἐκκλησίας σου φύλαξον, ἁγίασον τοὺς ἀγαπῶντας τὴν εὐπρέπειαν τοῦ οἴκου σου. Σὺ αὐτοὺς ἀντιδόξασον τῇ θεϊκῇ σου δυνάμει καὶ μὴ ἐγκαταλίπῃς ἡμᾶς τοὺς ἐλπίζοντας ἐπὶ σέ.
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key0301.title}{
ΕΥΧΗ ΑΝΤΙΦΩΝΟΥ Βʹ
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key0401.text}{
Ὁ τὰς κοινὰς ταύτας καὶ συμφώνους ἡμῖν χαρισάμενος προσευχάς, ὁ καὶ δυσὶ καὶ τρισὶ συμφωνοῦσιν ἐπὶ τῷ ὀνόματί σου τὰς αἰτήσεις παρέχειν ἐπαγγειλάμενος. Αὐτός καὶ νῦν τῶν δούλων σου τὰ αἰτήματα πρὸς τὸ συμφέρον πλήρωσον, χορηγῶν ἡμῖν ἐν τῷ παρόντι αἰῶνι τὴν ἐπίγνωσιν τῆς σῆς ἀληθείας καὶ ἐν τῷ μέλλοντι ζωὴν αἰώνιον χαριζόμενος.
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key0401.title}{
ΕΥΧΗ ΑΝΤΙΦΩΝΟΥ Γʹ
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key0500.title}{
ΜΙΚΡΑ ΕΙΣΟΔΟΣ
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key0501.text}{
Δέσποτα Κύριε, ὁ Θεὸς ἡμῶν, ὁ καταστήσας ἐν οὐρανοῖς τάγματα καὶ στρατιὰς Ἀγγέλων καὶ Ἀρχαγγέλων, εἰς λειτουργίαν τῆς σῆς δόξης, ποίησον σὺν τῇ εἰσόδῳ ἡμῶν εἴσοδον ἁγίων Ἀγγέλων γενέσθαι, συλλειτουργούντων ἡμῖν, καὶ συνδοξολογούντων τὴν σὴν ἀγαθότητα.
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key0501.title}{
ΕΥΧΗ ΤΗΣ ΕΙΣΟΔΟΥ ΤΟΥ ΑΓΙΟΥ ΕΥΑΓΓΕΛΙΟΥ
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key0502.text}{
Εὐλόγησον Δέσποτα, τὴν ἁγίαν εἴσοδον.
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key0503.text}{
Εὐλογημένη ἡ εἴσοδος τῶν Ἁγίων σου, πάντοτε, νῦν καὶ ἀεὶ καὶ εἰς τοὺς αἰῶνας τῶν αἰώνων.
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key0601.text}{
Ὁ Θεὸς ὁ Ἅγιος, ὁ ἐν ἁγίοις ἀναπαυόμενος, ὁ τρισαγίῳ φωνῇ ὑπό τῶν Σεραφεὶμ ἀνυμνούμενος καὶ ὑπό τῶν Χερουβεὶμ δοξολογούμενος, καὶ ὑπὸ πάσης ἐπουρανίου δυνάμεως προσκυνούμενος ὁ ἐκ τοῦ μὴ ὄντος εἰς το εἶναι παραγαγὼν τὰ σύμπαντα ὁ κτίσας τὸν ἄνθρωπον κατ' εἰκόνα σὴν καὶ ὁμοίωσιν καὶ παντί σου χαρίσματι κατακοσμήσας, ὁ διδοὺς αἰτοῦντι σοφίαν καὶ σύνεσιν, καὶ μὴ παρορῶν ἁμαρτάνοντα, ἀλλὰ θέμενος ἐπὶ σωτηρίᾳ μετάνοιαν, ὁ καταξιώσας ἡμᾶς, τοὺς ταπεινοὺς καὶ ἀναξίους δούλους σου, καὶ ἐν τῇ ὥρᾳ ταύτῃ στῆναι κατενώπιον τῆς δόξης τοῦ ἁγίου σου θυσιαστηρίου, καὶ τὴν ὀφειλομένην σοι προσκύνησιν καὶ δοξολογίαν προσάγειν. Αὐτός, Δέσποτα, πρόσδεξαι καὶ ἐκ στόματος ἡμῶν τῶν ἁμαρτωλῶν τὸν Τρισάγιον ὕμνον καὶ ἐπίσκεψαι ἡμᾶς ἐν τῇ χρηστότητί σου. Συγχώρησον ἡμῖν πᾶν πλημμέλημα, ἑκούσιόν τε καὶ ἀκούσιον, ἁγίασον ἡμῶν τὰς ψυχὰς καὶ τὰ σώματα καὶ δὸς ἡμῖν ἐν ὁσιότητι λατρεύειν σοι πάσας τὰς ἡμέρας τῆς ζωῆς ἡμῶν, πρεσβείαις τῆς ἁγίας Θεοτόκου, καὶ πάντων τῶν Ἁγίων, τῶν ἀπ' αἰῶνός σοι εὐαρεστησάντων.
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key0601.title}{
ΕΥΧΗ ΤΟΥ ΤΡΙΣΑΓΙΟΥ ΥΜΝΟΥ
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key0602.text}{
Δύναμις.
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key0704.text}{
Ἔλλαμψον ἐν ταῖς καρδίαις ἡμῶν, φιλάνθρωπε Δέσποτα, τὸ τῆς σῆς θεογνωσίας ἀκήρατον φῶς, καί τοὺς τῆς διανοίας ἡμῶν ὀφθαλμοὺς διάνοιξον εἰς τὴν τῶν εὐαγγελικῶν σου κηρυγμάτων κατανόησιν. Ἔνθες ἡμῖν καὶ τὸν τῶν μακαρίων σου ἐντολῶν φόβον, ἵνα τὰς σαρκικὰς ἐπιθυμίας πάσας καταπατήσαντες, πνευματικὴν πολιτείαν μετέλθωμεν, πάντα τὰ πρὸς εὐαρέστησιν τὴν σὴν καὶ φρονοῦντες καὶ πράττοντες.Σὺ γὰρ εἶ ὁ φωτισμός τῶν ψυχῶν καί τῶν σωμάτων ἡμῶν, Χριστὲ ὁ Θεός, καὶ σοὶ τὴν δόξαν ἀναπέμπομεν, σὺν τῷ ἀνάρχῳ σου Πατρὶ καὶ τῷ παναγίῳ καὶ ἀγαθῷ καὶ ζωοποιῷ σου Πνεύματι, νῦν καὶ ἀεὶ καὶ εἰς τοὺς αἰῶνας τῶν αἰώνων. Ἀμήν.
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key0704.title}{
ΕΥΧΗ ΤΟΥ ΕΥΑΓΓΕΛΙΟΥ
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key0706.title}{
ΤΟ ΚΗΡΥΓΜΑ
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key0708}{
[
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key0709}{
]
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key0800.title}{
Η ΜΕΓΑΛΗ ΕΚΤΕΝΗΣ ΙΚΕΣΙΑ ἢ ΔΕΗΣΙΣ
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key0801.text}{
Κύριε ὁ Θεὸς ἡμῶν, τὴν ἐκτενῆ ταύτην ἱκεσίαν πρόσδεξαι παρά τῶν σῶν δούλων καὶ ἐλέησον ἡμᾶς κατὰ τὸ πλῆθος τοῦ ἐλέους σου, καί τοὺς οἰκτιρμούς σου κατάπεμψον ἐφ' ἡμᾶς, καὶ ἐπὶ πάντα τὸν λαόν σου, ἀπεκδεχόμενον τὸ παρά σοῦ μέγα καὶ πλούσιον ἔλεος.
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key0801.title}{
EΥΧΗ ΤΗΣ ΕΚΤΝΟΥΣ ΙΚΕΣΙΑΣ
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key0900.title}{
ΔΕΗΣΙΣ ΥΠΕΡ ΤΩΝ ΚΑΤΗΧΟΥΜΕΝΩΝ
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key0901.text}{
Εὔξασθε οἱ Κατηχούμενοι τῷ Κυρίῳ.
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key0902.text}{
Οἱ πιστοί, ὑπέρ τῶν Κατηχουμένων δεηθῶμεν.
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key0903.text}{
Ἵνα ὁ Κύριος αὐτοὺς ἐλεήσῃ.
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key0904.text}{
Κατηχήσῃ αὐτοὺς τὸν λόγον τῆς ἀληθείας.
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key0905.text}{
Ἀποκαλύψῃ αὐτοῖς τὸ Εὐαγγέλιον τῆς δικαιοσύνης.
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key0906.text}{
Ἑνώσῃ αὐτοὺς τῇ ἁγίᾳ αὐτοῦ Καθολικῇ καὶ Ἀποστολικῇ Ἐκκλησίᾳ.
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key0907.text}{
Σῶσον, ἐλέησον, ἀντιλαβοῦ, καὶ διαφύλαξον αὐτούς, ὁ Θεός, τῇ σῇ χάριτι.
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key0908.text}{
Οἱ Κατηχούμενοι τὰς κεφαλὰς ὑμῶν τῷ Κυρίῳ κλίνατε.
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key0909.text}{
Κύριε ὁ Θεὸς ἡμῶν, ὁ ἐν ὑψηλοῖς κατοικῶν, καὶ τὰ ταπεινὰ ἐφορῶν, ὁ διὰ τὴν σωτηρίαν τῷ γένει τῶν ἀνθρώπων ἐξαποστείλας, τὸν μονογενῆ σου Υἱὸν καὶ Θεόν, τὸν Κύριον ἡμῶν Ἰησοῦν Χριστόν, ἐπίβλεψον ἐπί τοὺς δούλους σου τοὺς Κατηχουμένους, τοὺς ὑποκεκλικότας σοι τὸν ἑαυτῶν αὐχένα, καὶ καταξίωσον αὐτούς, ἐν καιρῷ εὐθέτῳ, τοῦ λουτροῦ τῆς παλιγγενεσίας, τῆς ἀφέσεως τῶν ἁμαρτιῶν καί τοῦ ἐνδύματος τῆς ἀφθαρσίας, ἕνωσον αὐτοὺς τῇ ἁγίᾳ σου, Καθολικῇ καὶ Ἀποστολικῇ Ἐκκλησίᾳ καὶ συγκαταρίθμησον αὐτοὺς τῇ ἐκλεκτῇ σου ποίμνῃ.
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key0909.title}{
ΕΥΧΗ ΤΩΝ ΚΑΤΗΧΟΥΜΕΝΩΝ
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key0910.text}{
Ἴνα καὶ αὐτοὶ σὺν ἡμῖν δοξάζωσι τὸ πάντιμον καὶ μεγαλοπρεπὲς ὄνομά σου, τοῦ Πατρὸς καί τοῦ Υἱοῦ καί τοῦ Ἁγίου Πνεύματος, νῦν καὶ ἀεὶ καὶ εἰς τοὺς αἰῶνας τῶν αἰώνων.
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key0911.text}{
Ὅσοι κατηχούμενοι, προέλθετε. Οἱ Κατηχούμενοι, προέλθετε. Ὅσοι κατηχούμενοι προέλθετε. Μή τις τῶν κατηχουμένων.
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key0912.text}{
Ὅσοι πιστοί, ἔτι καὶ ἔτι ἐν εἰρήνῃ τοῦ Κυρίου δεηθῶμεν.
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key1000.title}{
ΔΕΗΣΕΙΣ ΤΩΝ ΠΙΣΤΩΝ
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key1001.text}{
Εὐχαριστοῦμέν σοι, Κύριε, ὁ Θεός τῶν δυνάμεων, τῷ καταξιώσαντι ἡμᾶς παραστῆναι καὶ νῦν τῷ ἁγίῳ σου θυσιαστηρίῳ καὶ προσπεσεῖν τοῖς οἰκτιρμοῖς σου ὑπὲρ τῶν ἡμετέρων ἁμαρτημάτων καί τῶν τοῦ λαοῦ ἀγνοημάτων. Πρόσδεξαι, ὁ Θεός, τὴν δέησιν ἡμῶν, ποίησον ἡμᾶς ἀξίους γενέσθαι τοῦ προσφέρειν σοι δεήσεις καὶ ἱκεσίας καὶ θυσίας ἀναιμάκτους ὑπὲρ παντός τοῦ λαοῦ σου, καὶ ἱκάνωσον ἡμᾶς, οὕς ἔθου εἰς τὴν διακονίαν σου ταύτην, ἐν τῇ δυνάμει τοῦ Πνεύματός σου τοῦ Ἁγίου, ἀκαταγνώστως καὶ ἀπροσκόπτως, ἐν καθαρῷ τῷ μαρτυρίῳ τῆς συνειδήσεως ἡμῶν, ἐπικαλεῖσθαί σε ἐν παντὶ καιρῷ καὶ τόπῳ, ἵνα εἰσακούων ἡμῶν, ἵλεως ἡμῖν εἴης, ἐν τῷ πλήθει τῆς σῆς ἀγαθότητος.
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key1001.title}{
ΕΥΧΗ ΤΩΝ ΠΙΣΤΩΝ Αʹ
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key1002.text}{
Πάλιν καὶ πολλάκις σοι προσπίπτομεν καί σοῦ δεόμεθα, ἀγαθὲ καὶ φιλάνθρωπε, ὅπως, ἐπιβλέψας ἐπὶ τὴν δέησιν ἡμῶν, καθαρίσῃς ἡμῶν τὰς ψυχὰς καὶ τὰ σώματα ἀπὸ παντὸς μολυσμοῦ σαρκὸς καὶ πνεύματος, καὶ δῴης ἡμῖν ἀνένοχον καὶ ἀκατάκριτον τὴν παράστασιν τοῦ ἁγίου σου θυσιαστηρίου. Χάρισαι δέ, ὁ Θεός, καὶ τοῖς συνευχομένοις ἡμῖν προκοπὴν βίου καὶ πίστεως καὶ συνέσεως πνευματικῆς, δὸς αὐτοῖς πάντοτε, μετὰ φόβου καὶ ἀγάπης λατρεύειν σοι, ἀνενόχως καὶ ἀκατακρίτως μετέχειν τῶν ἁγίων σου μυστηρίων, καί τῆς ἐπουρανίου σου βασιλείας ἀξιωθῆναι.
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key1002.title}{
ΕΥΧΗ ΤΩΝ ΠΙΣΤΩΝ Bʹ
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key1003.text}{
Ὅπως ὑπό τοῦ κράτους σου πάντοτε φυλαττόμενοι, σοὶ δόξαν ἀναπέμπωμεν, τῷ Πατρὶ καὶ τῷ Υἱῷ καὶ τῷ Ἁγίῳ Πνεύματι, νῦν καὶ ἀεὶ καὶ εἰς τοὺς αἰῶνας τῶν αἰώνων.
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key1100.title}{
Η ΜΕΓΑΛΗ ΕΙΣΟΔΟΣ
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key1101.text}{
Οὐδεὶς ἄξιος τῶν συνδεδεμένων ταῖς σαρκικαῖς ἐπιθυμίαις καὶ ἡδοναῖς προσέρχεσθαι ἢ προσεγγίζειν, ἢ λειτουργεῖν σοι, Βασιλεῦ τῆς δόξης· τὸ γὰρ διακονεῖν σοι μέγα καὶ φοβερόν, καὶ αὐταῖς ταῖς ἐπουρανίαις δυνάμεσιν. Ἀλλ' ὅμως, διὰ τὴν ἄφατον καὶ ἀμέτρητόν σου φιλανθρωπίαν, ἀτρέπτως καὶ ἀναλλοιώτως γέγονας ἄνθρωπος καὶ ἀρχιερεὺς ἡμῶν ἐχρημάτισας, καί τῆς λειτουργικῆς ταύτης καὶ ἀναιμάκτου θυσίας τὴν ἱερουργίαν παρέδωκας ἡμῖν, ὡς Δεσπότης τῶν ἁπάντων. Σὺ γὰρ μόνος, Κύριε ὁ Θεὸς ἡμῶν, δεσπόζεις τῶν ἐπουρανίων καί τῶν ἐπιγείων, ὁ ἐπὶ θρόνου Χερουβικοῦ ἐποχούμενος, ὁ τῶν Σεραφεὶμ Κύριος, καὶ βασιλεύς τοῦ Ἰσραήλ, ὁ Μόνος Ἅγιος καὶ ἐν ἁγίοις ἀναπαυόμενος, σὲ τοίνυν δυσωπῶ τὸν μόνον ἀγαθὸν καὶ εὐήκοον, ἐπίβλεψον ἐπ' ἐμὲ τὸν ἁμαρτωλὸν καὶ ἀχρεῖον δούλόν σου, καὶ καθάρισόν μου τὴν ψυχὴν καὶ τὴν καρδίαν ἀπὸ συνειδήσεως πονηρᾶς, καὶ ἱκάνωσόν με τῇ δυνάμει τοῦ Ἁγίου σου Πνεύματος, ἐνδεδυμένον τὴν τῆς ἱερατείας χάριν, παραστῆναι τῇ ἁγίᾳ σου ταύτῃ τραπέζῃ καὶ ἱερουργῆσαι τὸ ἅγιον καὶ ἄχραντόν σου Σῶμα καὶ τὸ τίμιον Αἷμα. Σοὶ γὰρ προσέρχομαι, κλίνας τὸν ἐμαυτοῦ αὐχένα καὶ δέομαί σου, μὴ ἀποστρέψῃς τὸ πρόσωπόν σου ἀπ' ἐμοῦ, μηδὲ ἀποδοκιμάσῃς με ἐκ παίδων σου, ἀλλ' ἀξίωσον προσενεχθῆναί σοι ὑπ' ἐμοῦ τοῦ ἁμαρτωλοῦ καὶ ἀναξίου δούλου σου τὰ δῶρα ταῦτα. Σὺ γὰρ εἶ ὁ προσφέρων καὶ προσφερόμενος καὶ προσδεχόμενος καὶ διαδιδόμενος, Χριστὲ ὁ Θεὸς ἡμῶν, καὶ σοὶ τὴν δόξαν ἀναπέμπομεν, σὺν τῷ ἀνάρχῳ σου Πατρὶ καὶ τῷ Παναγίῳ καὶ ἀγαθῷ καὶ ζωοποιῷ σου Πνεύματι, νῦν καὶ ἀεὶ καὶ εἰς τοὺς αἰῶνας τῶν αἰώνων. Ἀμήν.
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key1101.title}{
ΕΥΧΗ ΤΟΥ ΧΕΡΟΥΒΙΚΟΥ ΥΜΝΟΥ
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key1102.text}{
Οἱ τὰ Χερουβεὶμ μυστικῶς εἰκονίζοντες, καὶ τῇ ζωοποιῷ Τριάδι τὸν τρισάγιον ὕμνον προσᾴδοντες, πᾶσαν νῦν βιοτικὴν ἀποθώμεθα μέριμναν.
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key1102.title}{
Τὸ Χερουβικόν.
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key1103.text}{
Ὡς τὸν Βασιλέα τῶν ὅλων ὑποδεξόμενοι.
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key1110.text}{
Πάντων ἡμῶν μνησθείη Κύριος ὁ Θεὸς ἐν τῇ Βασιλείᾳ Αὐτοῦ, πάντοτε, νῦν καὶ ἀεὶ καὶ εἰς τοὺς αἰῶνας τῶν αἰώνων.
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key1200.title}{
ΤΑ ΠΛΗΡΩΤΙΚΑ
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key1201.text}{
Ὑπὲρ τῶν προτεθέντων τιμίων Δώρων, τοῦ Κυρίου δεηθῶμεν.
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key1202.text}{
Κύριε ὁ Θεὸς ὁ παντοκράτωρ, ὁ μόνος ἅγιος, ὁ δεχόμενος θυσίαν αἰνέσεως παρά τῶν ἐπικαλουμένων σε ἐν ὅλῃ καρδίᾳ, πρόσδεξαι καὶ ἡμῶν τῶν ἁμαρτωλῶν τὴν δέησιν καὶ προσάγαγε τῷ ἁγίῳ σου θυσιαστηρίῳ, καὶ ἱκάνωσον ἡμᾶς προσενεγκεῖν σοι δῶρα τε καὶ θυσίας πνευματικὰς ὑπέρ τῶν ἡμετέρων ἁμαρτημάτων καί τῶν τοῦ λαοῦ ἀγνοημάτων. Καὶ καταξίωσον ἡμᾶς εὑρεῖν χάριν ἐνώπιόν σου, τοῦ γενέσθαι σοι εὐπρόσδεκτον τὴν θυσίαν ἡμῶν, καὶ ἐπισκηνῶσαι τὸ Πνεῦμα τῆς χάριτός σου τὸ ἀγαθόν ἐφ' ἡμᾶς, καὶ ἐπὶ τὰ προκείμενα δῶρα ταῦτα καὶ ἐπὶ πάντα τὸν λαόν σου.
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key1202.title}{
Η ΕΥΧΗ ΤΗΣ ΠΡΟΣΚΟΜΙΔΗΣ
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key1203.text}{
Διά τῶν οἰκτιρμῶν τοῦ μονογενοῦς σου Υἱοῦ, μεθ' οὗ εὐλογητὸς εἶ, σὺν τῷ Παναγίῳ καὶ ἀγαθῷ καὶ ζωοποιῷ σου Πνεύματι, νῦν καὶ ἀεὶ καὶ εἰς τοὺς αἰῶνας τῶν αἰώνων.
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key1204.text}{
Ἀγαπήσωμεν ἀλλήλους, ἵνα ἐν ὁμονοίᾳ ὁμολογήσωμεν.
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key1205.text}{
Πατέρα, Υἱὸν καὶ Ἅγιον Πνεῦμα, Τριάδα ὁμοούσιον καὶ ἀχώριστον.
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key1208.text}{
Τὰς θύρας, τὰς θύρας. Ἐν σοφίᾳ πρόσχωμεν.
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key1209.title}{
ΤΟ ΣΥΜΒΟΛΟΝ ΤΗΣ ΠΙΣΤΕΟΣ
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key1300.title}{
Η ΑΓΙΑ ΑΝΑΦΟΡΑ
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key1301.text}{
Στῶμεν καλῶς, στῶμεν μετὰ φόβου, πρόσχωμεν, τὴν ἁγίαν ἀναφοράν, ἐν εἰρήνῃ προσφέρειν.
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key1302.text}{
Ἔλεον εἰρήνης, θυσίαν αἰνέσεως.
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key1303.text}{
Ἡ χάρις τοῦ Κυρίου ἡμῶν Ἰησοῦ Χριστοῦ καὶ ἡ ἀγάπη τοῦ Θεοῦ καί Πατρὸς καὶ ἡ κοινωνία τοῦ Ἁγίου Πνεύματος εἴη μετὰ πάντων ὑμῶν.
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key1304.text}{
Καὶ μετά τοῦ πνεύματός σου.
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key1305.text}{
Ἄνω σχῶμεν τὰς καρδίας.
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key1306.text}{
Ἔχομεν πρὸς τὸν Κύριον.
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key1307.text}{
Εὐχαριστήσωμεν τῷ Κυρίῳ.
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key1308.text}{
Ἄξιον καὶ δίκαιον.
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key1309.text}{
Ἄξιον καὶ δίκαιον σὲ ὑμνεῖν, σὲ εὐλογεῖν, σὲ αἰνεῖν, σοὶ εὐχαριστεῖν, σὲ προσκυνεῖν ἐν παντὶ τόπῳ τῆς δεσποτείας σου. Σὺ γὰρ εἶ Θεὸς ἀνέκφραστος, ἀπερινόητος, ἀόρατος, ἀκατάληπτος, ἀεὶ ὤν, ὡσαύτως ὤν, σὺ καὶ ὁ μονογενής σου Υἱός, καὶ τὸ Πνεῦμά σου τὸ Ἅγιον. Σὺ ἐκ τοῦ μὴ ὄντος εἰς το εἶναι ἡμᾶς παρήγαγες, καὶ παραπεσόντας ἀνέστησας πάλιν καὶ οὐκ ἀπέστης πάντα ποιῶν, ἕως ἡμᾶς εἰς τὸν οὐρανὸν ἀνήγαγες, καὶ τὴν βασιλείαν σου, ἐχαρίσω τὴν μέλλουσαν. Ὑπὲρ τούτων ἁπάντων εὐχαριστοῦμέν σοι, καὶ τῷ μονογενεῖ σου Υἱῷ καὶ τῷ Πνεύματί σου τῷ Ἁγίῳ. Ὑπὲρ πάντων, ὧν ἴσμεν, καὶ ὥν οὐκ ἴσμεν, τῶν φανερῶν καὶ ἀφανῶν εὐεργεσιῶν, τῶν εἰς ἡμᾶς γεγενημένων. Εὐχαριστοῦμέν σοι καὶ ὑπέρ τῆς λειτουργίας ταύτης, ἥν ἐκ τῶν χειρῶν ἡμῶν δέξασθαι καταξίωσας, καίτοι σοι παρεστήκασι χιλιάδες Ἀρχαγγέλων καὶ μυριάδες Ἀγγέλων, τὰ Χερουβεὶμ καὶ τὰ Σεραφείμ, ἑξαπτέρυγα, πολυόμματα, μετάρσια, πτερωτά.
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key1310.text}{
Τὸν ἐπινίκιον ὕμνον ᾄδοντα, βοῶντα, κεκραγότα, καὶ λέγοντα·
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key1311.text}{
Ἅγιος, ἅγιος, ἅγιος, Κύριος Σαβαώθ· πλήρης, ὁ οὐρανὸς καὶ ἡ γῆ τῆς δόξης σου. Ὡσαννά, ἐν τοῖς ὑψίστοις· εὐλογημένος ὁ ἐρχόμενος ἐν ὀνόματι Κυρίου. Ὡσαννά, ὁ ἐν τοῖς ὑψίστοις.
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key1312.text}{
Μετὰ τούτων καὶ ἡμεῖς τῶν μακαρίων δυνάμεων, Δέσποτα φιλάνθρωπε, βοῶμεν καὶ λέγομεν· Ἅγιος εἶ καὶ πανάγιος, σὺ καὶ ὁ μονογενής σου Υἱὸς καὶ τὸ Πνεῦμά σου τὸ Ἅγιον. Ἅγιος εἶ καὶ πανάγιος καὶ μεγαλοπρεπὴς ἡ δόξα σου. Ὃς τὸν κόσμον σου οὕτως ἠγάπησας, ὥστε τὸν Υἱόν σου τὸν μονογενῆ δοῦναι, ἵνα πᾶς ὁ πιστεύων εἰς αὐτὸν μὴ ἀπόλυται, ἀλλ' ἔχῃ ζωὴν αἰώνιον. 'Ὃς ἐλθὼν καὶ πᾶσαν τὴν ὑπὲρ ἡμῶν οἰκονομίαν πληρώσας, τῇ νυκτί, ᾖ παρεδίδοτο, μᾶλλον δὲ ἑαυτὸν παρεδίδου ὑπέρ τῆς τοῦ κόσμου ζωῆς, λαβὼν ἄρτον ἐν ταῖς ἁγίαις αὐτοῦ καὶ ἀχράντοις καὶ ἀμωμήτοις χερσίν, εὐχαριστήσας καὶ εὐλογήσας, ἁγιάσας, κλάσας, ἔδωκε τοῖς ἁγίοις αὐτοῦ Μαθηταῖς καὶ Ἀποστόλοις, εἰπών·
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key1313.text}{
Λάβετε, φάγετε, τοῦτό μού ἐστι τὸ Σῶμα, τὸ ὑπὲρ ὑμῶν κλώμενον εἰς ἄφεσιν ἁμαρτιῶν.
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key1314.text}{
Ὁμοίως καὶ τὸ ποτήριον μετὰ τὸ δειπνῆσαι, λέγων·
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key1315.text}{
Πίετε ἐξ αὐτοῦ πάντες, τοῦτό ἐστι τὸ Αἷμά μου, το τῆς Καινῆς Διαθήκης, τὸ ὑπὲρ ὑμῶν καὶ πολλῶν ἐκχυνόμενον εἰς ἄφεσιν ἁμαρτιῶν.
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key1316.text}{
Μεμνημένοι τοίνυν τῆς σωτηρίου ταύτης ἐντολῆς, καὶ πάντων τῶν ὑπὲρ ἡμῶν γεγενημένων, τοῦ σταυροῦ, τοῦ τάφου, τῆς τριημέρου ἀναστάσεως, τῆς εἰς οὐρανούς ἀναβάσεως, τῆς ἐκ δεξιῶν καθέδρας, τῆς δευτέρας καὶ ἐνδόξου πάλιν παρουσίας,
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key1317.text}{
Τὰ Σὰ ἐκ τῶν Σῶν, σοὶ προσφέρομεν κατὰ πάντα, καὶ διὰ πάντα.
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key1318.text}{
Σὲ ὑμνοῦμεν, σὲ εὐλογοῦμεν, σοὶ εὐχαριστοῦμεν, Κύριε, καὶ δεόμεθά σου, ὁ Θεὸς ἡμῶν.
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key1319.text}{
Ἔτι προσφέρομέν σοι τὴν λογικὴν ταύτην καὶ ἀναίμακτον λατρείαν, καὶ παρακαλοῦμέν σε καὶ δεόμεθα, καὶ ἱκετεύομεν. Κατάπεμψον τὸ Πνεῦμά σου τὸ Ἅγιον ἐφ' ἡμᾶς, καὶ ἐπὶ τὰ προκείμενα δῶρα ταῦτα.
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key1321.text}{
Καὶ ποίησον τὸν μὲν ἄρτον τοῦτον, τίμιον Σῶμα τοῦ Χριστοῦ σου.
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key1323.text}{
Τὸ δὲ ἐν τῷ ποτηρίῳ τούτῳ, τίμιον Αἷμα τοῦ Χριστοῦ σου.
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key1325.text}{
Μεταβαλὼν τῷ Πνεύματί σου τῷ Ἁγίῳ.
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key1326.text}{
Ὥστε γενέσθαι τοῖς μεταλαμβάνουσιν εἰς νῆψιν ψυχῆς, εἰς ἄφεσιν ἁμαρτιῶν, εἰς κοινωνίαν τοῦ Ἁγίου σου Πνεύματος, εἰς Βασιλίας οὐρανῶν πλήρωμα, εἰς παῤῥησίαν τὴν πρὸς σέ, μὴ εἰς κρῖμα ἢ εἰς κατάκριμα. Ἔτι προσφέρομέν σοι τὴν λογικὴν ταύτην λατρείαν ὑπὲρ τῶν ἐν πίστει ἀναπαυσαμένων Προπατόρων, Πατέρων, Πατριαρχῶν, Προφητῶν, Ἀποστόλων, Κηρύκων, Εὐαγγελιστῶν, Μαρτύρων, Ὁμολογητῶν, Ἐγκρατευτῶν, Διδασκάλων, καὶ παντὸς πνεύματος δικαίου ἐν πίστει τετελειωμένου.
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key1327.text}{
Ἐξαιρέτως τῆς Παναγίας, ἀχράντου, ὑπερευλογημένης, ἐνδόξου, Δεσποίνης ἡμῶν Θεοτόκου καὶ ἀειπαρθένου Μαρίας.
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key1329.text}{
Τοῦ Ἁγίου Ἰωάννου, προφήτου προδρόμου καὶ Βαπτιστοῦ, τῶν ἁγίων ἐνδόξων καὶ πανευφήμων Ἀποστόλων, (του ἁγίου τῆς ἡμέρας) οὗ καὶ τὴν μνήμην ἐπιτελοῦμεν, καὶ πάντων σου τῶν Ἁγίων, ὧν ταῖς ἱκεσίαις ἐπίσκεψαι ἡμᾶς, ὁ Θεός. Καὶ μνήσθητι πάντων τῶν κεκοιμημένων, ἐπ' ἐλπίδι ἀναστάσεως, ζωῆς αἰωνίου [ὧδε λέγονται τὰ ὀνόματα τῶν κεκοιμημένων] καὶ ἀνάπαυσον αὐτούς, ὁ Θεὸς ἡμῶν, ὅπου ἐπισκοπεῖ τὸ φῶς τοῦ προσώπου σου. Ἔτι παρακαλοῦμέν σε, μνήσθητι, Κύριε, πάσης ἐπισκοπῆς ὀρθοδόξων, τῶν ὀρθοτομούντων τὸν λόγον τῆς σῆς ἀληθείας, παντός τοῦ πρεσβυτερίου, τῆς ἐν Χριστῷ διακονίας καὶ παντὸς ἱερατικοῦ καὶ μοναχικοῦ τάγματος. Ἔτι προσφέρομέν σοι τὴν λογικὴν ταύτην λατρείαν ὑπέρ τῆς οἰκουμένης, ὑπέρ τῆς ἁγίας σου Καθολικῆς καὶ Ἀποστολικῆς Ἐκκλησίας, ὑπέρ τῶν ἐν ἁγνείᾳ καὶ σεμνῇ πολιτείᾳ διαγόντων· ὑπέρ τῶν ἀρχόντων καὶ τοῦ στρατοῦ ἡμῶν. Δὸς αὐτοῖς, Κύριε, εἰρηνικὸν τὸ Βασίλειον, ἵνα καὶ ἡμεῖς, ἐν τῇ γαλήνῃ αὐτῶν, ἤρεμον καὶ ἡσύχιον βίον διάγωμεν, ἐν πάσῃ εὐσεβείᾳ καὶ σεμνότητι.
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key1330a.text}{
Ἐν πρώτοις, μνήσθητι, Κύριε,
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key1330b.text}{
ὂν χάρισαι ταῖς ἁγίαις σου Ἐκκλησίαις ἐν εἰρήνῃ, σῷον, ἔντιμον, ὑγιᾶ, μακροημερεύοντα, καὶ ὀρθοτομοῦντα τὸν λόγον τῆς σῆς ἀληθείας.
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key1331.text}{
Καὶ ὧν ἕκαστος κατὰ διάνοιαν ἔχει, καὶ πάντων καὶ πασῶν.
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key1332.text}{
Καὶ πάντων καὶ πασῶν.
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key1333.text}{
Μνήσθητι, Κύριε, τῆς πόλεως ταύτης, ἐν ᾖ παροικοῦμεν καὶ πάσης πόλεως καὶ χώρας καὶ τῶν πίστει οἰκούντων ἐν αὐταῖς. Μνήσθητι, Κύριε, πλεόντων, ὁδοιπορούντων, νοσούντων, καμνόντων, αἰχμαλώτων καὶ τῆς σωτηρίας αὐτῶν. Μνήσθητι, Κύριε, τῶν καρποφορούντων καὶ καλλιεργούντων ἐν ταῖς ἁγίαις σου Ἐκκλησίαις καὶ μεμνημένων τῶν πενήτων, καὶ ἐπὶ πάντας ἡμᾶς τὰ ἐλέη σου ἐξαπόστειλον.
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key1334.text}{
Καὶ δὸς ἡμῖν ἐν ἑνὶ στόματι καὶ μιᾷ καρδίᾳ, δοξάζειν καὶ ἀνυμνεῖν τὸ πάντιμον καὶ μεγαλοπρεπὲς ὄνομά σου, τοῦ Πατρὸς καί τοῦ Υἱοῦ καί τοῦ Ἁγίου Πνεύματος, νῦν καὶ ἀεὶ καὶ εἰς τοὺς αἰῶνας τῶν αἰώνων.
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key1335.text}{
Καὶ ἔσται τὰ ἐλέη τοῦ μεγάλου Θεοῦ καὶ Σωτῆρος ἡμῶν Ἰησοῦ Χριστοῦ, μετὰ πάντων ὑμῶν.
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key1336.text}{
Καὶ μετὰ τοῦ πνεύματός σου.
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key1401.text}{
Πάντων τῶν ἁγίων μνημονεύσαντες, ἔτι καὶ ἔτι ἐν εἰρήνῃ τοῦ Κυρίου δεηθῶμεν.
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key1402.text}{
Ὑπέρ τῶν προσκομισθέντων καὶ ἁγιασθέντων τιμίων δώρων, τοῦ Κυρίου δεηθῶμεν.
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key1403.text}{
Ὅπως ὁ φιλάνθρωπος Θεὸς ἡμῶν, ὁ προσδεξάμενος αὐτὰ εἰς τὸ ἅγιον καὶ ὑπερουράνιον καὶ νοερὸν αὐτοῦ θυσιαστήριον εἰς ὀσμὴν εὐωδίας πνευματικῆς, ἀντικαταπέμψῃ ἡμῖν τὴν θείαν Χάριν καὶ τὴν δωρεὰν τοῦ Ἁγίου Πνεύματος δεηθῶμεν.
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key1404.text}{
Τὴν ἑνότητα τῆς πίστεως καὶ τὴν κοινωνίαν τοῦ Ἁγίου Πνεύματος αἰτησάμενοι, ἑαυτοὺς καὶ ἀλλήλους καὶ πᾶσαν τὴν ζωὴν ἡμῶν Χριστῷ τῷ Θεῷ παραθώμεθα.
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key1405.text}{
Σοὶ παρακατατιθέμεθα τὴν ζωὴν ἡμῶν ἅπασαν καὶ τὴν ἐλπίδα, Δέσποτα φιλάνθρωπε, καὶ παρακαλοῦμέν σε καὶ δεόμεθα καὶ ἱκετεύομεν, καταξίωσον ἡμᾶς μεταλαβεῖν τῶν ἐπουρανίων σου καὶ φρικτῶν μυστηρίων ταύτης τῆς ἱερᾶς καὶ πνευματικῆς τραπέζης, μετὰ καθαροῦ συνειδότος, εἰς ἄφεσιν ἁμαρτιῶν, εἰς συγχώρησιν πλημμελημάτων, εἰς Πνεύματος Ἁγίου κοινωνίαν, εἰς Βασιλείας οὐρανῶν κληρονομίαν, εἰς παῤῥησίαν τὴν πρὸς σέ, μὴ εἰς κρῖμα ἢ εἰς κατάκριμα.
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key1406.text}{
Καὶ καταξίωσον ἡμᾶς, Δέσποτα, μετὰ παῤῥησίας, ἀκατακρίτως, τολμᾶν ἐπικαλεῖσθαι σὲ τὸν ἐπουράνιον Θεὸν Πατέρα, καὶ λέγειν·
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key1407.text}{
Εὐχαριστοῦμέν σοι, Βασιλεῦ ἀόρατε, ὁ τῇ ἀμετρήτῳ σου δυνάμει τὰ πάντα δημιούργησας καὶ τῷ πλήθει τοῦ ἐλέους σου ἐξ οὐκ ὄντων εἰς τὸ εἶναι τὰ πάντα παραγαγών· Αὐτὸς Δέσποτα, οὐρανόθεν ἔπιδε ἐπί τοὺς ὑποκεκλικότας τὰς ἑαυτῶν κεφαλάς. Οὐ γὰρ ἔκλιναν σαρκὶ καὶ αἵματι, ἀλλὰ σοί, τῷ φοβερῷ Θεῷ. Σὺ οὖν, Δέσποτα, τὰ προκείμενα πᾶσιν ἡμῖν εἰς ἀγαθὸν ἐξομάλισον, κατὰ τὴν ἑκάστου ἰδίαν χρείαν, τοῖς πλέουσι σύμπλευσον, τοῖς ὁδοιποροῦσι συνόδευσον, τοὺς νοσοῦντας ἴασαι, ὁ ἰατρός τῶν ψυχῶν καί τῶν σωμάτων ἡμῶν.
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key1409.text}{
Πρόσχες, Κύριε Ἰησοῦ Χριστὲ ὁ Θεὸς ἡμῶν, ἐξ ἁγίου κατοικητηρίου σου, καὶ ἀπὸ θρόνου δόξης τῆς Βασιλείας σου, καὶ ἐλθὲ εἰς τὸ ἁγιάσαι ἡμᾶς, ὁ ἄνω τῷ Πατρὶ συγκαθήμενος καὶ ὧδε ἡμῖν ἀοράτως συνών. Καὶ καταξίωσον τῇ κραταιᾷ σου χειρὶ μεταδοῦναι ἡμῖν τοῦ ἀχράντου Σώματός σου καί τοῦ τιμίου Αἵματος καὶ δι' ἡμῶν παντὶ τῷ λαῷ.
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key1409.title}{
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key1410.text}{
Τα Ἅγια τοῖς Ἁγίοις.
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key1411.text}{
Εἷς ἅγιος, εἷς Κύριος, Ἰησοῦς Χριστός, εἰς δόξαν Θεοῦ Πατρός. Ἀμήν.
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key1526.text}{
Μετὰ φόβου Θεοῦ, πίστεως καὶ ἀγάπης προσέλθετε.
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key1527.text}{
Μεταλαμβάνει ὁ δοῦλος τοῦ Θεοῦ (Ὄνομα) Σῶμα καὶ Αἷμα Χριστοῦ, εἰς ἄφεσιν ἁμαρτιῶν καὶ ζωὴν αἰώνιον. Ἀμήν.
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key1528.rubric}{
Καὶ γίνεται ἡ μετάληψις τοῦ Λαοῦ. Λαμβάνει ὁ Ἱερεὺς ἀπὸ τῶν τοῦ Διακόνου χειρῶν τὸ ἅγιον Ποτήριον καὶ μεταδίδωσιν αὐτοῖς λέγων·
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key1529.text}{
Σῶσον, ὁ Θεός, τὸν λαόν σου καὶ εὐλόγησον τὴν κληρονομίαν σου.
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key1530.text}{
Εἴδομεν τὸ φῶς τὸ ἀληθινόν, ἐλάβομεν Πνεῦμα ἐπουράνιον, εὓρομεν πίστιν ἀληθῆ, ἀδιαίρετον Τριάδα προσκυνοῦντες· αὕτη γὰρ ἡμᾶς ἔσωσεν.
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key1603.text}{
Πληρωθήτω τὸ στόμα ἡμῶν αἰνέσεως Κύριε, ὅπως ἀνυμνήσωμεν τὴν δόξαν σου, ὅτι ἠξίωσας ἡμᾶς τῶν ἁγίων σου μετασχεῖν μυστηρίων· τήρησον ἡμᾶς ἐν τῷ σῷ ἁγιασμῷ, ὅλην τὴν ἡμέραν μελετῶντας τὴν δικαιοσύνην σου. Ἀλληλούϊα, ἀλληλούϊα, ἀλληλούϊα.
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key1604.text}{
Ὀρθοί, μεταλαβόντες τῶν θείων, ἁγίων, ἀχράντων, ἀθανάτων, ἐπουρανίων καὶ ζωοποιῶν, φρικτῶν τοῦ Χριστοῦ μυστηρίων, ἀξίως εὐχαριστήσωμεν τῷ Κυρίῳ.
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key1605.text}{
Τὴν ἡμέραν πᾶσαν, τελείαν, ἁγίαν, εἰρηνικὴν καὶ ἀναμάρτητον αἰτησάμενοι, ἑαυτοὺς καὶ ἀλλήλους καὶ πᾶσαν τὴν ζωὴν ἡμῶν, Χριστῷ τῷ Θεῷ παραθώμεθα.
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key1606.text}{
Εὐχαριστοῦμέν σοι, Δέσποτα φιλάνθρωπε, εὐεργέτα τῶν ψυχῶν ἡμῶν, ὅτι καὶ τῇ παρούσῃ ἡμέρᾳ κατηξίωσας ἡμᾶς τῶν ἐπουρανίων σου καὶ ἀθανάτων μυστηρίων. Ὀρθοτόμησον ἡμῶν τὴν ὁδόν, στήριξον πάντας ἡμᾶς ἐν τῷ φόβῳ σου, φρούρησον ἡμῶν τὴν ζωήν, ἀσφάλισαι ἡμῶν τὰ διαβήματα, εὐχαῖς καὶ ἱκεσίαις τῆς ἐνδόξου Θεοτόκου καὶ ἀειπαρθένου Μαρίας, καὶ πάντων τῶν ἁγίων σου.
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key1606.title}{
Η ΕΥΧΑΡΙΣΤΗΡΙΟΣ ΕΥΧΗ
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key1700.title}{
ΑΠΟΛΥΣΙΣ
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key1701.text}{
Ἐν εἰρήνῃ προέλθωμεν.
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key1702.text}{
Ὁ εὐλογῶν τοὺς εὐλογοῦντάς σε, Κύριε καὶ ἁγιάζων τοὺς ἐπὶ σοὶ πεποιθότας, σῶσον τὸν λαόν σου καὶ εὐλόγησον τὴν κληρονομίαν σου. Τὸ πλήρωμα τῆς Ἐκκλησίας σου φύλαξον, ἁγίασον τοὺς ἀγαπῶντας τὴν εὐπρέπειαν τοῦ οἴκου σου. Σὺ αὐτοὺς ἀντιδόξασον τῇ θεϊκῇ σου δυνάμει καὶ μὴ ἐγκαταλίπῃς ἡμᾶς τοὺς ἐλπίζοντας ἐπὶ σέ. Εἰρήνην τῷ κόσμῳ σου δώρησαι, ταῖς Ἐκκλησίαις σου, τοῖς ἱερεῦσι, τοῖς ἄρχουσιν ἡμῶν, τῷ στρατῷ καὶ παντὶ τῷ λαῷ σου. Ὅτι πᾶσα δόσις ἀγαθὴ καὶ πᾶν δώρημα τέλειον ἄνωθέν ἐστι καταβαῖνον ἐκ σοῦ τοῦ Πατρός τῶν φώτων, καὶ σοὶ τὴν δόξαν καὶ εὐχαριστίαν καὶ προσκύνησιν ἀναπέμπομεν τῷ Πατρὶ καὶ τῷ Υἱῷ καὶ τῷ Ἁγίῳ Πνεύματι, νῦν καὶ ἀεὶ καὶ εἰς τοὺς αἰῶνας τῶν αἰώνων.
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key1702.title}{
ΕΥΧΗ ΟΠΙΣΘΑΜΒΩΝΟΣ
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.Key1704.text}{
Τὸ πλήρωμα τοῦ Νόμου καί τῶν Προφητῶν, αὐτὸς ὑπάρχων, Χριστὲ ὁ Θεὸς ἡμῶν, ὁ πληρώσας πᾶσαν τὴν πατρικὴν οἰκονομίαν, πλήρωσον χαρᾶς καὶ εὐφροσύνης τὰς καρδίας ἡμῶν πάντοτε, νῦν καὶ ἀεὶ καὶ εἰς τοὺς αἰῶνας τῶν αἰώνων. Ἀμήν.
}%
\itId{gr}{gr}{ages}{eu.lichrysbasil}{euLI.MM.HymnsDuringCommunion.title}{
Ὗμνοι καθῶς μεταλαμβάνει ὁ λαός.
}%
\itId{gr}{gr}{ages}{ho.s07}{hoLI.Antiphon1.text}{
Ταῖς πρεσβείαις τῆς Θεοτόκου, Σῶτερ, σῶσον ἡμᾶς.
}%
\itId{gr}{gr}{ages}{ho.s07}{hoLI.Antiphon21.text}{
Σῶσον ἡμᾶς Υἱὲ Θεοῦ,
}%
\itId{gr}{gr}{ages}{ho.s07}{hoLI.Antiphon22.text}{
ψάλλοντάς σοι, Ἀλληλούϊα.
}%
\itId{gr}{gr}{ages}{ho.s07}{hoLI.Antiphon2s.text}{
ὁ ἀναστὰς ἐκ νεκρῶν,
}%
\itId{gr}{gr}{ages}{ho.s07}{hoLI.EntranceHymn.text}{
Δεῦτε προσκυνήσωμεν καὶ προσπέσωμεν Χριστῷ. Σῶσον ἡμᾶς Υἱὲ Θεοῦ, ὁ ἀναστὰς ἐκ νεκρῶν, ψάλλοντάς σοι, Ἀλληλούϊα.
}%
\itId{gr}{gr}{ages}{ho.s07}{hoLI.OnlyBegotten.text}{
Ὁ Μονογενὴς Υἱὸς καὶ Λόγος τοῦ Θεοῦ, ἀθάνατος ὑπάρχων καὶ καταδεξάμενος διὰ τὴν ἡμετέραν σωτηρίαν σαρκωθῆναι ἐκ τῆς ἁγίας Θεοτόκου καὶ ἀειπαρθένου Μαρίας, ἀτρέπτως ἐνανθρωπήσας, σταυρωθείς τε, Χριστὲ ὁ Θεός, θανάτῳ θάνατον πατήσας, εἷς ὢν τῆς Ἁγίας Τριάδος, συνδοξαζόμενος τῷ Πατρὶ καὶ τῷ Ἁγίῳ Πνεύματι, σῶσον ἡμᾶς.
}%
\itId{gr}{gr}{ages}{ho.s07}{hoLI.TrisagiosHymn.text}{
Ἅγιος ὁ Θεός, ἅγιος ἰσχυρός, ἅγιος ἀθάνατος, ἐλέησον ἡμᾶς.
}%
\itId{gr}{gr}{ages}{ho.s07}{hoLI.TrisagiosHymn3.text}{
Ἅγιος ἀθάνατος,
}%
\itId{gr}{gr}{ages}{ho.s07}{hoLI.TrisagiosHymn4.text}{
ἐλέησον ἡμᾶς.
}%
\itId{gr}{gr}{ages}{ho.s21}{hoPrayer.Key101.text}{
Πιστεύω, Κύριε, καὶ ὁμολογῶ, ὅτι σὺ εἶ ἀληθῶς ὁ Χριστός, ὁ Υἱὸς τοῦ Θεοῦ τοῦ ζῶντος, ὁ ἐλθὼν εἰς τὸν κόσμον ἁμαρτωλοὺς σῶσαι, ὧν πρῶτός εἰμι ἐγώ. Ἔτι πιστεύω, ὅτι τοῦτο αὐτό ἐστι τὸ ἄχραντον Σῶμά σου καὶ τοῦτο αὐτό ἐστι τὸ τίμιον Αἷμά σου. Δέομαι οὖν σου· ἐλέησόν με καὶ συγχώρησόν μοι τὰ παραπτώματά μου, τὰ ἑκούσια καὶ τὰ ἀκούσια, τὰ ἐν λόγῳ, τὰ ἐν ἕργῳ, τὰ ἐν γνώσει καὶ ἀγνοίᾳ· καὶ ἀξίωσόν με ἀκατακρίτως μετασχεῖν τῶν ἀχράντων σου μυστηρίων, εἰς ἄφεσιν ἁμαρτιῶν καὶ εἰς ζωὴν αἰώνιον. Ἀμήν.
}%
\itId{gr}{gr}{ages}{ho.s21}{hoPrayer.Key110.text}{
Ἰδού, βαδίζω πρὸς θείαν Κοινωνίαν· Πλαστουργέ, μὴ φλέξῃς με τῇ μετουσίᾳ· Πῦρ γὰρ ὑπάρχεις τοὺς ἀναξίους φλέγον. Ἀλλ' οὖν κάθαρον ἐκ πάσης με κηλῖδος.
}%
\itId{gr}{gr}{ages}{ho.s21}{hoPrayer.Key121.text}{
Τοῦ Δείπνου σου τοῦ μυστικοῦ, σήμερον Υἱὲ Θεοῦ, κοινωνόν με παράλαβε· οὐ μὴ γὰρ τοῖς ἐχθροῖς σου τὸ Μυστήριον εἴπω, οὐ φίλημά σοι δώσω, καθάπερ ὁ Ἰούδας, ἀλλ' ὡς ὁ Λῃστὴς ὁμολογῶ σοι. Μνήσθητί μου Κύριε, [ὅταν ἔλθῃς] ἐν τῇ Βασιλείᾳ σου.
}%
\itId{gr}{gr}{ages}{ho.s21}{hoPrayer.Key161.text}{
Δέσποτα φιλάνθρωπε, Κύριε Ἰησοῦ Χριστέ, ὁ Θεός μου, μὴ εἰς κρῖμά μοι γένοιτο τὰ ἅγια ταῦτα, διὰ τὸ ἀνάξιον εἶναί με, ἀλλ' εἰς κάθαρσιν καὶ ἁγιασμὸν ψυχῆς τε καὶ σώματος, καὶ εἰς ἀῤῥαβῶνα τῆς μελλούσης ζωῆς καὶ βασιλείας. Ἐμοὶ δὲ τὸ προσκολλᾶσθαι τῷ Θεῷ ἀγαθόν ἐστι, τίθεσθαι ἐν τῷ Κυρίῳ τὴν ἐλπίδα τῆς σωτηρίας μου.
}%
\itId{gr}{gr}{ages}{ho.s21}{hoPrayer.title}{
ΕΥΧΑΙ ΠΡΟ ΤΗΣ ΘΕΙΑΣ ΚΟΙΝΩΝΙΑΣ
}%
\itId{gr}{gr}{ages}{ho.s99}{bede.text}{
Orthodoxy's guide, teacher of piety and reverence, beacon of the world, fair ornament of monks. Inspired by God, o, wise Bede, by your teaching you have enlightened all; o, harp of the Spirit, intercede with Christ God, that our souls may be saved.
}%
\itId{gr}{gr}{ages}{ho.s99}{cuthbert.text}{
Faithful guide of Northumbria's Church an example of meekness and humility in fasting, vigils and in prayer an adornment of bishops and the glory of monks. O Holy Cuthbert, you dwell now in the light which knows no evening standing at the throne of God. Remember those that honour you and ask of Christ to have mercy on us.
}%
\itId{gr}{gr}{ages}{ho.s99}{silouan.text}{
You received and knew the Holy Spirit and acquired fully Adam’s tears. With unquenchable thirst and desire for Christ you kept your mind in hell by repentance and thus obtained the great love for all nations. Father Silouan, ever pray before God to grant to us His Holy Sprit and His great mercy.
}%
\itId{gr}{gr}{ages}{liturgical.verses}{psLI.aftercommunion.v1.text}{
Εἴη τὸ ὄνομα Κυρίου εὐλογημένον ἀπὸ τοῦ νῦν καὶ ἕως τοῦ αἰῶνος.
}%
\itId{gr}{gr}{ages}{me.m10.d28}{alt1.meLI.Antiphon2.text}{
Σῶσον ἡμὰς Υἱὲ Θεοῦ, ὁ ἐν ἁγίοις θαυμαστός, ψάλλοντάς σοι, Ἀλληλούϊα.
}%
\itId{gr}{gr}{ages}{misc}{vVerse1}{
Στίχ. αʹ.
}%
\itId{gr}{gr}{ages}{misc}{vVerse2}{
Στίχ. βʹ.
}%
\itId{gr}{gr}{ages}{misc}{vVerse3}{
Στίχ. γʹ.
}%
\itId{gr}{gr}{ages}{prayers}{Allilouia3.text}{
Ἀλληλούϊα. Ἀλληλούϊα. Ἀλληλούϊα.
}%
\itId{gr}{gr}{ages}{prayers}{AxionEstinComplete.text}{
Ἄξιόν ἐστιν ὡς ἀληθῶς μακαρίζειν σε τὴν Θεοτόκον, τὴν ἀειμακάριστον καὶ παναμώμητον καὶ μητέρα τοῦ Θεοῦ ἡμῶν. Τὴν τιμιωτέραν τῶν Χερουβεὶμ καὶ ἐνδοξοτέραν ἀσυγκρίτως τῶν Σεραφείμ, τὴν ἀδιαφθόρως Θεὸν Λόγον τεκοῦσαν, τὴν ὄντως Θεοτόκον, σὲ μεγαλύνομεν.
}%
\itId{gr}{gr}{ages}{prayers}{DiEfchonPateron.text}{
Δι' εὐχῶν τῶν ἁγίων πατέρων ἡμῶν, Κύριε Ἰησοῦ Χριστὲ ὁ Θεός, ἐλέησον καὶ σῶσον ἡμᾶς.
}%
\itId{gr}{gr}{ages}{prayers}{DoxaPatri}{
(Δόξα Πατρὶ καὶ Υἱῷ καὶ Ἁγίῳ Πνεύματι.)
}%
\itId{gr}{gr}{ages}{prayers}{DoxaSoiKyrie}{
Δόξα σοι, Κύριε, δόξα σοι.
}%
\itId{gr}{gr}{ages}{prayers}{DoxaSoiOTheosImon.text}{
Δόξα σοι ὁ Θεὸς ἡμῶν, δόξα σοι.
}%
\itId{gr}{gr}{ages}{prayers}{KaiNynKaiAei.text}{
Καὶ νῦν καὶ ἀεί, καὶ εἰς τοὺς αἰῶνας τῶν αἰώνων. Ἀμήν.
}%
\itId{gr}{gr}{ages}{prayers}{PantoteNyn.text}{
Πάντοτε, νῦν καὶ ἀεὶ καὶ εἰς τοὺς αἰῶνας τῶν αἰώνων.
}%
\itId{gr}{gr}{ages}{prayers}{PaterImon.text}{
Πάτερ ἡμῶν ὁ ἐν τοῖς οὐρανοῖς, ἁγιασθήτω τὸ ὄνομά σου. Ἐλθέτω ἡ βασιλεία σου. Γενηθήτω τὸ θέλημά σου, ὡς ἐν οὐρανῷ καὶ ἐπὶ τῆς γῆς. Τὸν ἄρτον ἡμῶν τὸν ἐπιούσιον δὸς ἡμῖν σήμερον. Καὶ ἄφες ἡμῖν τὰ ὀφειλήματα ἡμῶν, ὡς καὶ ἡμεῖς ἀφίεμεν τοῖς ὀφειλέταις ἡμῶν. Καὶ μὴ εἰσενέγκῃς ἡμᾶς εἰς πειρασμόν, ἀλλὰ ρῦσαι ἡμᾶς ἀπὸ τοῦ πονηροῦ.
}%
\itId{gr}{gr}{ages}{prayers}{Pistevo.text}{
Πιστεύω εἰς ἕνα Θεόν, Πατέρα, Παντοκράτορα, ποιητὴν οὐρανοῦ καὶ γῆς, ὁρατῶν τε πάντων καὶ ἀοράτων. Καὶ εἰς ἕνα Κύριον Ἰησοῦν Χριστόν, τὸν Υἱὸν τοῦ Θεοῦ τὸν μονογενῆ, τὸν ἐκ τοῦ Πατρὸς γεννηθέντα πρὸ πάντων τῶν αἰώνων· φῶς ἐκ φωτός, Θεὸν ἀληθινὸν ἐκ Θεοῦ ἀληθινοῦ, γεννηθέντα οὐ ποιηθέντα, ὁμοούσιον τῷ Πατρί, δι' οὗ τὰ πάντα ἐγένετο. Τὸν δι' ἡμᾶς τοὺς ἀνθρώπους καὶ διὰ τὴν ἡμετέραν σωτηρίαν κατελθόντα ἐκ τῶν οὐρανῶν καὶ σαρκωθέντα ἐκ Πνεύματος Ἁγίου καὶ Μαρίας τῆς Παρθένου καὶ ἐνανθρωπήσαντα. Σταυρωθέντα τε ὑπὲρ ἡμῶν ἐπὶ Ποντίου Πιλάτου, καὶ παθόντα καὶ ταφέντα. Καὶ ἀναστάντα τῇ τρίτῃ ἡμέρα κατὰ τὰς Γραφάς. Καὶ ἀνελθόντα εἰς τοὺς οὐρανοὺς καὶ καθεζόμενον ἐκ δεξιῶν τοῦ Πατρός. Καὶ πάλιν ἐρχόμενον μετὰ δόξης κρῖναι ζῶντας καὶ νεκρούς, οὗ τῆς βασιλείας οὐκ ἔσται τέλος. Καὶ εἰς τὸ Πνεῦμα τὸ Ἅγιον, τὸ Κύριον, τὸ ζωοποιόν, τὸ ἐκ τοῦ Πατρὸς ἐκπορευόμενον, τὸ σὺν Πατρὶ καὶ Υἱῷ συμπροσκυνούμενον καὶ συνδοξαζόμενον, τὸ λαλῆσαν διὰ τῶν προφητῶν. Εἰς μίαν, Ἁγίαν, Καθολικὴν καὶ Ἀποστολικὴν Ἐκκλησίαν. Ὁμολογῶ ἓν βάπτισμα εἰς ἄφεσιν ἁμαρτιῶν. Προσδοκῶ ἀνάστασιν νεκρῶν. Καὶ ζωὴν τοῦ μέλλοντος αἰῶνος. Ἀμήν.
}%
\itId{gr}{gr}{ages}{prayers}{enarxis02}{
Εὐλογημένη ἡ Βασιλεία τοῦ Πατρὸς καὶ τοῦ Υἱοῦ καὶ τοῦ Ἁγίου Πνεύματος, νῦν καὶ ἀεί, καὶ εἰς τοὺς αἰῶνας τῶν αἰώνων.
}%
\itId{gr}{gr}{ages}{prayers}{epi02}{
Εἰρήνη σοι τῷ ἀναγινώσκοντι.
}%
\itId{gr}{gr}{ages}{prayers}{exc01}{
Ὅτι πρέπει σοι πᾶσα δόξα, τιμὴ καὶ προσκύνησις, τῷ Πατρὶ καὶ τῷ Υἱῷ καὶ τῷ Ἁγίῳ Πνεύματι, νῦν καὶ ἀεὶ καὶ εἰς τοὺς αἰῶνας τῶν αἰώνων.
}%
\itId{gr}{gr}{ages}{prayers}{exc02}{
Ὅτι σὸν τὸ κράτος καὶ σοῦ ἐστιν ἡ βασιλεία καὶ ἡ δύναμις καὶ ἡ δόξα, τοῦ Πατρὸς καὶ τοῦ Υἱοῦ καὶ τοῦ Ἁγίου Πνεύματος, νῦν καὶ ἀεὶ εἰς τοὺς αἰῶνας τῶν αἰώνων.
}%
\itId{gr}{gr}{ages}{prayers}{exc03}{
Ὅτι ἀγαθὸς καὶ φιλάνθρωπος Θεὸς ὑπάρχεις καὶ σοὶ τὴν δόξαν ἀναπέμπομεν, τῷ Πατρὶ καὶ τῷ Υἱῷ καὶ τῷ Ἁγίῳ Πνεύματι, νῦν καὶ ἀεὶ καὶ εἰς τοὺς αἰῶνας τῶν αἰώνων.
}%
\itId{gr}{gr}{ages}{prayers}{exc05a}{
Ὅτι Ἅγιος εἶ ὁ Θεὸς ἡμῶν, καὶ σοὶ τὴν δόξαν ἀναπέμπομεν, τῷ Πατρὶ καὶ τῷ Υἱῷ καὶ τῷ Ἁγίῳ Πνεύματι, νῦν καὶ ἀεί...
}%
\itId{gr}{gr}{ages}{prayers}{exc05b}{
...καὶ εἰς τοὺς αἰῶνας τῶν αἰώνων.
}%
\itId{gr}{gr}{ages}{prayers}{exc07a}{
Χάριτι καὶ οἰκτιρμοῖς καὶ φιλανθρωπίᾳ τοῦ μονογενοῦς σου Υἱοῦ, μεθ' οὗ εὐλογητὸς εἰ, σὺν τῷ παναγίῳ καὶ ἀγαθῷ καὶ ζωοποιῷ σου Πνεύματι, νῦν καὶ ἀεὶ καὶ εἰς τοὺς αἰῶνας τῶν αἰώνων.
}%
\itId{gr}{gr}{ages}{prayers}{exc11}{
Ὅτι ἐλεήμων καὶ φιλάνθρωπος Θεὸς ὑπάρχεις, καὶ σοὶ τὴν δόξαν ἀναπέμπομεν, τῷ Πατρὶ καὶ τῷ Υἱῷ καὶ τῷ Ἁγίῳ Πνεύματι, νῦν καὶ ἀεὶ καὶ εἰς τοὺς αἰῶνας τῶν αἰώνων.
}%
\itId{gr}{gr}{ages}{prayers}{exc17}{
Σοφία.
}%
\itId{gr}{gr}{ages}{prayers}{exc18}{
Ὀρθοί.
}%
\itId{gr}{gr}{ages}{prayers}{exc19}{
Πρόσχωμεν.
}%
\itId{gr}{gr}{ages}{prayers}{exc20}{
Ὅτι σοῦ ἐστιν ἡ βασιλεία καὶ ἡ δύναμις καὶ ἡ δόξα τοῦ Πατρὸς καὶ τοῦ Υἱοῦ καὶ τοῦ Ἁγίου Πνεύματος, νῦν καὶ ἀεὶ καὶ εἰς τοὺς αἰῶνας τῶν αἰώνων.
}%
\itId{gr}{gr}{ages}{prayers}{exc24}{
Ὅτι σὺ εἶ ὁ ἁγιασμὸς ἡμῶν, καὶ σοὶ τὴν δόξαν ἀναπέμπομεν, τῷ Πατρὶ καὶ τῷ Υἱῷ καὶ τῷ Ἁγίῳ Πνεύματι, νῦν καὶ ἀεὶ καὶ εἰς τοὺς αἰῶνας τῶν αἰώνων.
}%
\itId{gr}{gr}{ages}{prayers}{gos02}{
Ἀκούσωμεν τοῦ ἁγίου Εὐαγγελίου.
}%
\itId{gr}{gr}{ages}{prayers}{gos03a}{
Ἐκ τοῦ κατὰ
}%
\itId{gr}{gr}{ages}{prayers}{gos03b}{
ἁγίου Εὐαγγελίου τὸ ἀνάγνωσμα.
}%
\itId{gr}{gr}{ages}{prayers}{gos04}{
Εἰρήνη σοι.
}%
\itId{gr}{gr}{ages}{prayers}{pet00}{
Τοῦ Κυρίου δεηθῶμεν.
}%
\itId{gr}{gr}{ages}{prayers}{pet01}{
Ἐν εἰρήνῃ τοῦ Κυρίου δεηθῶμεν.
}%
\itId{gr}{gr}{ages}{prayers}{pet02}{
Ὑπὲρ τῆς ἄνωθεν εἰρήνης καὶ τῆς σωτηρίας τῶν ψυχῶν ἡμῶν, τοῦ Κυρίου δεηθῶμεν.
}%
\itId{gr}{gr}{ages}{prayers}{pet03}{
Ὑπὲρ τῆς εἰρήνης τοῦ σύμπαντος κόσμου, εὐσταθείας τῶν ἁγίων τοῦ Θεοῦ Ἐκκλησιῶν καὶ τῆς τῶν πάντων ἑνώσεως, τοῦ Κυρίου δεηθῶμεν.
}%
\itId{gr}{gr}{ages}{prayers}{pet04}{
Ὑπὲρ τοῦ ἁγίου οἴκου τούτου, καὶ τῶν μετὰ πίστεως, εὐλαβείας καὶ φόβου Θεοῦ εἰσιόντων ἐν αὐτῷ, τοῦ Κυρίου δεηθῶμεν.
}%
\itId{gr}{gr}{ages}{prayers}{pet05}{
Ὑπὲρ τῶν εὐσεβῶν καὶ Ὀρθοδόξων Χριστιανῶν, τοῦ Κυρίου δεηθῶμεν.
}%
\itId{gr}{gr}{ages}{prayers}{pet06a}{
Ὑπὲρ
}%
\itId{gr}{gr}{ages}{prayers}{pet06b}{
τοῦ τιμίου πρεσβυτερίου, τῆς ἐν Χριστῷ διακονίας, παντὸς τοῦ κλήρου καὶ τοῦ λαοῦ, τοῦ Κυρίου δεηθῶμεν.
}%
\itId{gr}{gr}{ages}{prayers}{pet07S}{
Ὑπὲρ τοῦ εὐσεβοῦς ἡμῶν ἔθνους, πάσης ἀρχῆς καὶ ἐξουσίας ἐν αὐτῷ, τοῦ Κυρίου δεηθῶμεν.
}%
\itId{gr}{gr}{ages}{prayers}{pet08}{
Ὑπὲρ τῆς πόλεως ταύτης, πάσης πόλεως, χώρας καὶ τῶν πίστει οἰκούντων ἐν αὐταῖς, τοῦ Κυρίου δεηθῶμεν.
}%
\itId{gr}{gr}{ages}{prayers}{pet09}{
Ὑπὲρ εὐκρασίας ἀέρων, εὐφορίας τῶν καρπῶν τῆς γῆς, καὶ καιρῶν εἰρηνικῶν, τοῦ Κυρίου δεηθῶμεν.
}%
\itId{gr}{gr}{ages}{prayers}{pet10}{
Ὑπὲρ πλεόντων, ὁδοιπορούντων, νοσούντων, καμνόντων, αἰχμαλώτων καὶ τῆς σωτηρίας αὐτῶν, τοῦ Κυρίου δεηθῶμεν.
}%
\itId{gr}{gr}{ages}{prayers}{pet11}{
Ὑπὲρ τοῦ ῥυσθῆναι ἡμᾶς ἀπὸ πάσης θλίψεως, ὀργῆς, κινδύνου καὶ ἀνάγκης, καὶ ἀπὸ τοῦ ἀπειλοῦντος ἡμᾶς λοιμοῦ τοῦ κορονοϊοῦ, τοῦ Κυρίου δεηθῶμεν.
}%
\itId{gr}{gr}{ages}{prayers}{pet12}{
Ἀντιλαβοῦ, σῶσον, ἐλέησον καὶ διαφύλαξον ἡμᾶς ὁ Θεὸς τῇ σῇ χάριτι.
}%
\itId{gr}{gr}{ages}{prayers}{pet13}{
Τῆς Παναγίας ἀχράντου, ὑπερευλογημένης, ἐνδόξου Δεσποίνης ἡμῶν Θεοτόκου καὶ ἀειπαρθένου Μαρίας μετὰ πάντων τῶν Ἁγίων μνημονεύσαντες, ἑαυτοὺς καὶ ἀλλήλους καὶ πᾶσαν τὴν ζωὴν ἡμῶν Χριστῷ τῷ Θεῷ παραθώμεθα.
}%
\itId{gr}{gr}{ages}{prayers}{pet14}{
Ἔτι καὶ ἔτι ἐν εἰρήνῃ τοῦ Κυρίου δεηθῶμεν.
}%
\itId{gr}{gr}{ages}{prayers}{pet15}{
Εἴπωμεν πάντες ἐξ ὅλης τῆς ψυχῆς καὶ ἐξ ὅλης τῆς διανοίας ἡμῶν εἴπωμεν.
}%
\itId{gr}{gr}{ages}{prayers}{pet16}{
Κύριε παντοκράτορ ὁ Θεὸς τῶν πατέρων ἡμῶν, δεόμεθά Σου, ἐπάκουσον καὶ ἐλέησον
}%
\itId{gr}{gr}{ages}{prayers}{pet17}{
Ἐλέησον ἡμᾶς ὁ Θεὸς κατὰ τὸ μέγα ἒλεός Σου, δεόμεθά Σου, ἐπάκουσον καὶ ἐλέησον.
}%
\itId{gr}{gr}{ages}{prayers}{pet19Sa}{
Ἔτι δεόμεθα ὑπὲρ
}%
\itId{gr}{gr}{ages}{prayers}{pet20}{
Ἔτι δεόμεθα ὑπὲρ τῶν ἀδελφῶν ἡμῶν, τῶν ἱερέων, ἱερομονάχων, ἱεροδιακόνων καὶ μοναχῶν, καὶ πάσης τῆς ἐν Χριστῷ ἡμῶν ἀδελφότητος.
}%
\itId{gr}{gr}{ages}{prayers}{pet21}{
Ἔτι δεόμεθα ὑπὲρ ἐλέους, ζωῆς, εἰρήνης, ὑγείας, σωτηρίας, ἐπισκέψεως, συγχωρήσεως καὶ ἀφέσεως τῶν ἁμαρτιῶν τῶν δούλων τοῦ Θεοῦ, πάντων τῶν εὐσεβῶν καὶ Ὀρθοδόξων Χριστιανῶν, τῶν κατοικούντων καὶ παρεπιδημούντων ἐν τῇ (πόλει, κώμῃ), ταύτῃ, τῶν ἐνοριτῶν, ἐπιτρόπων, συνδρομητῶν καὶ ἀφιερωτῶν τοῦ ἁγίου ναοῦ τούτου.
}%
\itId{gr}{gr}{ages}{prayers}{pet22}{
Ἔτι δεόμεθα ὑπέρ τῶν μακαρίων καὶ ἀοιδίμων κτιτόρων τῆς ἁγίας Ἐκκλησίας ταύτης, καὶ ὑπὲρ πάντων τῶν προαναπαυσαμένων πατέρων καὶ ἀδελφῶν ἡμῶν, τῶν ἐνθάδε εὐσεβῶς, κειμένων, καὶ ἁπανταχοῦ Ὀρθοδόξων.
}%
\itId{gr}{gr}{ages}{prayers}{pet23}{
Ἔτι δεόμεθα ὑπὲρ τῶν καρποφορούντων καὶ καλλιεργούντων ἐν τῷ ἁγίῳ καὶ πανσέπτῳ ναῷ τούτῳ, κοπιώντων, ψαλλόντων καὶ ὑπὲρ τοῦ περιεστῶτος λαοῦ, τοῦ ἀπεκδεχομένου τὸ παρὰ σοῦ μέγα καὶ πλούσιον ἔλεος.
}%
\itId{gr}{gr}{ages}{prayers}{pet24}{
Πληρώσωμεν τὴν δέησιν ἡμῶν τῷ Κυρίῳ.
}%
\itId{gr}{gr}{ages}{prayers}{pet25m}{
Τὴν ἡμέραν πᾶσαν τελείαν, ἁγίαν, εἰρηνικὴν καὶ ἀναμάρτητον, παρὰ τοῦ Κυρίου αἰτησώμεθα.
}%
\itId{gr}{gr}{ages}{prayers}{pet26}{
Ἄγγελον εἰρήνης, πιστὸν ὁδηγόν, φύλακα τῶν ψυχῶν καὶ τῶν σωμάτων ἡμῶν, παρὰ τοῦ Κυρίου αἰτησώμεθα.
}%
\itId{gr}{gr}{ages}{prayers}{pet27}{
Συγγνώμην καὶ ἄφεσιν τῶν ἁμαρτιῶν καὶ τῶν πλημμελημάτων ἡμῶν, παρὰ τοῦ Κυρίου αἰτησώμεθα.
}%
\itId{gr}{gr}{ages}{prayers}{pet28}{
Τὰ καλὰ καὶ συμφέροντα ταῖς ψυχαῖς ἡμῶν καὶ εἰρήνην τῷ κόσμῳ, παρὰ τοῦ Κυρίου αἰτησώμεθα.
}%
\itId{gr}{gr}{ages}{prayers}{pet29}{
Τὸν ὑπόλοιπον χρόνον τῆς ζωῆς ἡμῶν ἐν εἰρήνῃ καὶ μετανοίᾳ ἐκτελέσαι, παρὰ τοῦ Κυρίου αἰτησώμεθα.
}%
\itId{gr}{gr}{ages}{prayers}{pet30}{
Χριστιανὰ τὰ τέλη τῆς ζωῆς ἡμῶν, ἀνώδυνα, ἀνεπαίσχυντα, εἰρηνικά, καὶ καλὴν ἀπολογίαν τὴν ἐπὶ τοῦ φοβεροῦ βήματος τοῦ Χριστοῦ αἰτησώμεθα.
}%
\itId{gr}{gr}{ages}{prayers}{pet31}{
Εἰρήνη πᾶσι.
}%
\itId{gr}{gr}{ages}{prayers}{pet32}{
Τὰς κεφαλὰς ἡμῶν τῷ Κυρίῳ κλίνωμεν.
}%
\itId{gr}{gr}{ages}{prayers}{pet37}{
Εὐλογία Κυρίου καὶ ἔλεος αὐτοῦ ἔλθοι ἐφ' ὑμᾶς, τῇ αὐτοῦ θεία χάριτι καὶ φιλανθρωπία πάντοτε, νῦν καὶ ἀεὶ καὶ εἰς τοὺς αἰῶνας τῶν αἰώνων.
}%
\itId{gr}{gr}{ages}{prayers}{res01}{
Κύριε, ἐλέησον.
}%
\itId{gr}{gr}{ages}{prayers}{res02}{
Παράσχου, Κύριε.
}%
\itId{gr}{gr}{ages}{prayers}{res03}{
Σοί, Κύριε.
}%
\itId{gr}{gr}{ages}{prayers}{res04}{
Ἀμήν.
}%
\itId{gr}{gr}{ages}{prayers}{res05}{
Καὶ τῷ πνεύματί σου.
}%
\itId{gr}{gr}{ages}{prayers}{res06}{
Κύριε, ἐλέησον. Κύριε, ἐλέησον. Κύριε, ἐλέησον.
}%
\itId{gr}{gr}{ages}{prayers}{res08}{
Εὐλόγησον, Δέσποτα.
}%
\itId{gr}{gr}{ages}{prayers}{res10}{
Ἀμήν. Ἀμήν. Ἀμήν.
}%
\itId{gr}{gr}{ages}{prayers}{res13}{
Δέσποτα ἅγιε, εὐλόγησον.
}%
\itId{gr}{gr}{ages}{ps}{psa102.v1.text}{
Εὐλόγει, ἡ ψυχή μου, τὸν Κύριον, καὶ πάντα τὰ ἐντός μου τὸ ὄνομα τὸ ἅγιον αὐτοῦ.
}%
\itId{gr}{gr}{ages}{ps}{psa102.v19.text}{
Κύριος ἐν τῷ οὐρανῷ ἡτοίμασε τὸν θρόνον αὐτοῦ, καὶ ἡ βασιλεία αὐτοῦ πάντων δεσπόζει.
}%
\itId{gr}{gr}{ages}{ps}{psa102.v2.text}{
Εὐλόγει, ἡ ψυχή μου, τὸν Κύριον καὶ μὴ ἐπιλανθάνου πάσας τὰς ἀνταποδόσεις αὐτοῦ.
}%
\itId{gr}{gr}{ages}{ps}{psa117.v1.text}{
Ἐξομολογεῖσθε τῷ Κυρίῳ, ὅτι ἀγαθός, ὅτι εἰς τὸν αἰῶνα τὸ ἔλεος αὐτοῦ.
}%
\itId{gr}{gr}{ages}{ps}{psa145.v1.text}{
Αἴνει, ἡ ψυχή μου, τὸν Κύριον.
}%
\itId{gr}{gr}{ages}{ps}{psa145.v10.text}{
Βασιλεύσει Κύριος εἰς τὸν αἰῶνα, ὁ Θεός σου, Σιών, εἰς γενεὰν καὶ γενεάν.
}%
\itId{gr}{gr}{ages}{ps}{psa145.v2.text}{
Αἰνέσω Κύριον ἐν τῇ ζωῇ μου, ψαλῶ τῷ Θεῷ μου ἕως ὑπάρχω.
}%
\itId{gr}{gr}{ages}{ps}{psa145.v5.text}{
Μακάριος οὗ ὁ Θεὸς Ἰακὼβ βοηθὸς αὐτοῦ, ἡ ἐλπὶς αὐτοῦ ἐπὶ Κύριον τὸν Θεὸν αὐτοῦ.
}%
\itId{gr}{gr}{ages}{ps}{psa68.v35.text}{
Αἰνεσάτωσαν αὐτὸν οἱ οὐρανοὶ καὶ ἡ γῆ, θάλασσα καὶ πάντα τὰ ἕρποντα ἐν αὐτῇ.
}%
\itId{gr}{gr}{ages}{pub.priest.servicebook}{doxapatrikainyn}{
Δόξα Πατρὶ καὶ Υἱῷ καὶ Ἁγίῳ Πνεύματι˙ καὶ νῦν καὶ ἀεὶ καὶ εἰς τοὺς αἰῶνας τῶν αἰώνων. Ἀμήν.
}%
\itId{gr}{gr}{ages}{pub.priest.servicebook}{li.blessboth}{
Εὐλόγησον, Δέσποτα, ἀμφότερα τὰ Ἅγια.
}%
\itId{gr}{gr}{ages}{pub.priest.servicebook}{li.blessingmercy}{
Εὐλογία Κυρίου καὶ ἔλεος ἔλθοι ἐπὶ σέ.
}%
\itId{gr}{gr}{ages}{pub.priest.servicebook}{li.blessreader}{
Εὐλόγησον, δέσποτα, τὸν εὐαγγελιστὴν τοῦ ἁγίου ἐνδόξου ἀποστόλου καὶ εὐαγγελιστοῦ (δεῖνος).
}%
\itId{gr}{gr}{ages}{pub.priest.servicebook}{li.blessreader2}{
Ὁ Θεὸς διὰ πρεσβειῶν τοῦ ἁγίου ἐνδόξου ἀποστόλου καὶ εὐαγγελιστοῦ (δεῖνος) δῴη σοι ῥῆμα τῷ εὐαγγελιζομένῳ δυνάμει πολλῇ εἰς ἐκπλήωσιν τοῦ Εὐαγγελίου τοῦ ἀγαηπτοῦ Υἱοῦ αὐτοῦ, Κυρίου δὲ ἡμῶν Ἰησοῦ Χριστοῦ.
}%
\itId{gr}{gr}{ages}{pub.priest.servicebook}{li.changebread}{
Εὐλόγησον, Δέσποτα, τὸν ἅγιον Ἄρτον.
}%
\itId{gr}{gr}{ages}{pub.priest.servicebook}{li.changewine}{
Εὐλόγησον, Δέσποτα, τὸ ἅγιον Ποτήριον.
}%
\itId{gr}{gr}{ages}{pub.priest.servicebook}{li.dis.oanastas}{
Ὁ ἀναστὰς ἐκ νεκρῶν
}%
\itId{gr}{gr}{ages}{pub.priest.servicebook}{li.end.title.doc}{
ΤΕΛΟΣ ΤΗΣ ΘΕΙΑΣ ΛΕΙΤΟΥΡΓΙΑ ΙΩΑΝΝΟΥ ΤΟΥ ΧΡΥΣΟΣΤΟΜΟΥ
}%
\itId{gr}{gr}{ages}{pub.priest.servicebook}{li.godisthelord}{
Εὐλογημένος ὁ ἐρχόμενος ἐν ὀνόματι Κυρίου. Θεὸς Κύριος καὶ ἐπεφανεν ἡμῖν.
}%
\itId{gr}{gr}{ages}{pub.priest.servicebook}{li.litanylordsprayer.title.doc}{
ΕΚΤΕΝΗΣ ΠΡΟ ΤΗΣ ΚΥΡΙΑΚΗΣ ΠΡΟΣΕΥΧΗΣ
}%
\itId{gr}{gr}{ages}{pub.priest.servicebook}{li.lordsname}{
Ἐν ὀνόματι Κυρίου.
}%
\itId{gr}{gr}{ages}{pub.priest.servicebook}{li.preparation.mercy}{
Ὁ Θεός, ἱλάσθητι μοι τῷ ἁμαρτωλῷ.
}%
\itId{gr}{gr}{ages}{pub.priest.servicebook}{li.prokeimenonmode}{
Προκείμενον τοῦ Ἀποστόλου. Ἦχος… . Ψαλμός τῷ Δαβίδ.
}%
\itId{gr}{gr}{ages}{pub.priest.servicebook}{li.readings.title.doc}{
ΤΑ ΑΝΑΓΝΩΣΜΑΤΑ ΤΗΣ ΚΑΙΝΗΣ ΔΙΑΘΗΚΗΣ
}%
\itId{gr}{gr}{ages}{pub.priest.servicebook}{li.rubric.alldays}{
Εἶτα κατὰ πᾶσαν Λειτουργἰαν·
}%
\itId{gr}{gr}{ages}{pub.priest.servicebook}{li.rubric.bede}{
Ἦχος πλ. δʹ. Άγιος Μπεντ
}%
\itId{gr}{gr}{ages}{pub.priest.servicebook}{li.rubric.blesswithgospel}{
Δεχόμενος δὲ ὁ Ἱερεὺς τὸ ἅγιον Εὐαγγέλιον ἀσπάζεται αὐτὸ καὶ χαράξας μετ’ αὐτοῦ τύπον σταυροῦ πρὸς τὸν λάον, ἐπιτίθησιν αὐτὸ ἐπὶ τῆς ἁγίας Τραπέζης.
}%
\itId{gr}{gr}{ages}{pub.priest.servicebook}{li.rubric.bowcommunion}{
Εἶτα προσκυνεῖ ὁ Ἱερεύς, ὁμοίως καὶ ὁ Διάκονος, ἐν ᾧ ἷσταται τόπῳ, λέγοντες μυστικῶς τρίς
}%
\itId{gr}{gr}{ages}{pub.priest.servicebook}{li.rubric.catechumens}{
Εἶτα ἄρχεται ὁ Διάκονος τῆς δεήσεως ὑπὲρ τῶν Κατηχουμένων.
}%
\itId{gr}{gr}{ages}{pub.priest.servicebook}{li.rubric.catechumens2}{
Ὁ Λαός, μετὰ πᾶσαν δέησιν˙
}%
\itId{gr}{gr}{ages}{pub.priest.servicebook}{li.rubric.cuthbert}{
Ἦχος πλ. δʹ. Άγιος Κάθμπερτ
}%
\itId{gr}{gr}{ages}{pub.priest.servicebook}{li.rubric.deaconquietly}{
Καὶ ὁ Διάκονος λέγει ἠρέμα·
}%
\itId{gr}{gr}{ages}{pub.priest.servicebook}{li.rubric.eachpetition}{
Μετὰ πᾶσαν δέησιν.
}%
\itId{gr}{gr}{ages}{pub.priest.servicebook}{li.rubric.eachpetition2}{
Μετὰ ἑκάστην δέησιν.
}%
\itId{gr}{gr}{ages}{pub.priest.servicebook}{li.rubric.giveantidoron}{
Ὁ Ἱερεὺς διανέμει τὸ Ἀντίδωρον, λέγων ἑνὶ ἑκάστῷ˙
}%
\itId{gr}{gr}{ages}{pub.priest.servicebook}{li.rubric.kontakion1}{
Εἶτα ψάλλεται τὰ Ἀπολυτίκια τῆς ἡμέρας, τοῦ Ναοῦ καὶ μετὰ τὸ·
}%
\itId{gr}{gr}{ages}{pub.priest.servicebook}{li.rubric.notsunday}{
Τις καθημερινές, έξω από το Πάσχα, ή τη γιορτή του Κυρίου, τραγουδάμε μετά από κάθε στίχο·
}%
\itId{gr}{gr}{ages}{pub.priest.servicebook}{li.rubric.preach}{
Ἐνταῦθα ὁ Ἱεροκήρυξ διδάσκει τὸν λόγον τοῦ Θεοῦ.
}%
\itId{gr}{gr}{ages}{pub.priest.servicebook}{li.rubric.readgospel}{
Ὁ δὲ Διάκόνος ἀναγινώσκει τὴν τεταγμένην περικοπὴν τοῦ ἁγίου Εὐαγγελίου. Καὶ πληρωθέντος τοῦ Εὐαγγελίου, λέγει ὁ Ἱερεύς˙
}%
\itId{gr}{gr}{ages}{pub.priest.servicebook}{li.rubric.resurrectionmode}{
Τὸ ἀναστάσιμον ἀπολυτίκιον τοῦ τυχόντος ἤχου
}%
\itId{gr}{gr}{ages}{pub.priest.servicebook}{li.rubric.silouan}{
Ἦχος γʹ. Άγιος Σιλουανός
}%
\itId{gr}{gr}{ages}{pub.priest.servicebook}{li.rubric.smallentrance}{
Ψαλλομένου δὲ τοῦ Δοξαστικοῦ τῶν Μακαρισμῶν, ἤ τοῦ τρίτου Ἀντιφώνου, ὁ Ἱερεὺς καὶ ὁ Διάκονος, στάντες πρὸ τῆς ἁγίας Τραπέζης, ποιοῦσι προσκυνήματα τρία˙ εἴτα λαβὼν ὁ Ἱερεὺς τὸ ἅγιον Εὐαγγέλιον, δίδωσι τῷ Διακόνῳ, ἀσπαζομένῳ τὴν χεῖρα αὐτου. Καὶ οὕτως ἐξελθόντες διὰ` τοῦ βορείου μέρους, προπορευομένων αὐτῶν λαμπάδων, ἤ ἑξαπτερύγων, ποιοῦσιν τήν Μικρὰν Εἴσοδον, καὶ στάντες ἐν τῷ μέσῳ τοῦ Ναοῦ, κλίνουσιν ἀμφότεροι τὰς κεφαλάς.
}%
\itId{gr}{gr}{ages}{pub.priest.servicebook}{li.rubric.sundayantifon3}{
Εἶτα ψάλλονται οἱ Μακαρισμοί, ἢ τὸ τρίτον Ἀντίφωνον. Ἐν δὲ ταῖς Κυριακαῖς νῦν ψάλλεται τὸ παρόν˙·
}%
\itId{gr}{gr}{ages}{pub.priest.servicebook}{li.rubric.sundaydismissal}{
(εἰπέρ ἐστι Κυριακή)
}%
\itId{gr}{gr}{ages}{pub.priest.servicebook}{li.rubric.thriceeach}{
γ’ μετὰ πάσαν δέησιν
}%
\itId{gr}{gr}{ages}{pub.priest.servicebook}{li.thanksdismissal.title.doc}{
Η ΕΥΧΑΡΙΣΤΗΡΙΟΣ ΕΥΧΗ ΚΑΙ ΑΠΟΛΥΣΙΣ
}%
\itId{gr}{gr}{ages}{rubrical}{BeginLiturgy}{
Ὁ Ἱερεύς, ὑψῶν τὸ ἅγιον Εὐαγγέλιον καὶ ποιῶν τύπον Σταυροῦ δι’ αὐτοῦ ἐπὶ τοῦ Ἀντιμηνσίου, ἐκφωνεῖ λαμπρᾷ τῇ φωνῇ·
}%
\itId{gr}{gr}{ages}{rubrical}{DeaconStart}{
Ὁ Διάκονος, λαβὼν εὐλογίαν παρὰ τοῦ Ἱερέως, ἐξέρχεται τοῦ βήματος διὰ τῆς βορείας πύλης καί, ἱστάμενος ἐν τῷ συνήθει αὐτοῦ τόπῳ πρὸ τῆς ̔Ωραίας Πύλης, προσκυνεῖ τρὶς καὶ ἐκφωνεῖ·
}%
\itId{gr}{gr}{ages}{rubrical}{InALowVoice}{
(χαμηλοφώνως)
}%
\itId{gr}{gr}{ages}{rubrical}{Thrice}{
(ἐκ γʹ)
}%
\itId{gr}{gr}{ages}{rubrical}{cl.eu.lichrysbasil.R009}{
Ὁ Ἀναγνώστης λέγει τὴν ἐπιγραφήν τοῦ Ἀποστόλου.
}%
\itId{gr}{gr}{ages}{rubrical}{cl.eu.lichrysbasil.R010}{
(Ὁ Ἀναγνώστης ἀναγινώσκει τὴν τετραγμένην ἀποστολικὴν περικοπὴν.)
}%
\itId{gr}{gr}{ages}{template.titles}{li2.html.tab}{
ΛΕΙΤΟΥΡΓΙΑ ΑΓΙΟΥ ΧΡΥΣΟΣΤΟΜΟΥ
}%
\itId{gr}{gr}{ages}{template.titles}{li2.html.tab.doc}{
ΛΕΙΤΟΥΡΓΙΑ ΑΓΙΟΥ ΧΡΥΣΟΣΤΟΜΟΥ
}%
\itId{gr}{gr}{ages}{template.titles}{li2.html.tab.header}{
ΛΕΙΤΟΥΡΓΙΑ ΑΓΙΟΥ ΧΡΥΣΟΣΤΟΜΟΥ
}%
\itId{gr}{gr}{ages}{template.titles}{li2.html.tab.toc}{
ΛΕΙΤΟΥΡΓΙΑ ΑΓΙΟΥ ΧΡΥΣΟΣΤΟΜΟΥ
}%
\itId{gr}{gr}{ages}{titles}{Eisodikon}{
Εἰσοδικόν.
}%
\itId{gr}{gr}{ages}{titles}{KyriakiProsefchi}{
ΚΥΡΙΑΚΗ ΠΡΟΣΕΥΧΗ
}%
\itId{gr}{gr}{ages}{titles}{LitCatechumens}{
Η ΛΕΙΤΟΥΡΓΙΑ ΤΩΝ ΚΑΤΗΧΟΥΜΕΝΩΝ
}%
\itId{gr}{gr}{ages}{variables.info}{Antiphon1.title}{
Ἀντίφωνον Αʹ
}%
\itId{gr}{gr}{ages}{variables.info}{Antiphon2.title}{
Ἀντίφωνον Βʹ
}%
\itId{gr}{gr}{ages}{variables.info}{TheotokosHymn.title}{
Ὗμνον τῆς Θεοτόκου
}%
\itId{gr}{gr}{ages}{variables.info}{Trisagion.title}{
Τὸ Τρισάγιον
}%
\itId{ro}{uk}{dur}{actors}{Deacon}{
\textsc{diaconul}
}%
\itId{ro}{uk}{dur}{actors}{Deacon.colon}{
\itRid{actors}{Deacon}:
}%
\itId{ro}{uk}{dur}{actors}{People}{
\textsc{strana}
}%
\itId{ro}{uk}{dur}{actors}{People.colon}{
\itRid{actors}{People}:
}%
\itId{ro}{uk}{dur}{actors}{Priest}{
\textsc{preotul}
}%
\itId{ro}{uk}{dur}{actors}{Priest.colon}{
\itRid{actors}{Priest}:
}%
\itId{ro}{uk}{dur}{actors}{Reader}{
\textsc{citețul}
}%
\itId{ro}{uk}{dur}{actors}{Reader.colon}{
\itRid{actors}{Reader}:
}%
\itId{ro}{uk}{dur}{client}{cl.bishop1.name.c}{
(nume)
}%
\itId{ro}{uk}{dur}{client}{cl.bishop1.name.p}{
(nume)
}%
\itId{ro}{uk}{dur}{client}{cl.bishop1.rank}{
(Înalt-) Prea Sfințitul (Arhi-) Episcopul (și Mitropolitul) nostru
}%
\itId{ro}{uk}{dur}{dismissals}{dis01}{
Hristos, Adevăratul nostru Dumnezeu,
}%
\itId{ro}{uk}{dur}{dismissals}{dis02}{
pentru rugăciunile Preacuratei Maicii Sale,
}%
\itId{ro}{uk}{dur}{dismissals}{dis03}{
ale Sfinților,
}%
\itId{ro}{uk}{dur}{dismissals}{dis04}{
}%
\itId{ro}{uk}{dur}{dismissals}{dis05}{
}%
\itId{ro}{uk}{dur}{dismissals}{dis06}{
măriților și întru tot lăudaților Apostoli,
}%
\itId{ro}{uk}{dur}{dismissals}{dis07}{
}%
\itId{ro}{uk}{dur}{dismissals}{dis08}{
ale Sfântului (N.) (al cărui hram îl poartă biserica),
}%
\itId{ro}{uk}{dur}{dismissals}{dis09}{
ale Sfântului (N.), a cărui pomenire o săvârșim,
}%
\itId{ro}{uk}{dur}{dismissals}{dis10}{
ale Sfinților și drepților dumnezeiești Părinți Ioachim și Ana și pentru ale tuturor sfinților,
}%
\itId{ro}{uk}{dur}{dismissals}{dis89}{
să ne miluiască și să ne mântuiască pe noi, ca un bun și de oameni iubitor.
}%
\itId{ro}{uk}{dur}{dismissals}{li.dis.chrysostom}{
ale celui între Sfinți Părintelui nostru Ioan Gură de Aur, arhiepiscopul Constantinopolului,
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key0200.text}{
ECTENIA MARE
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key0201.text}{
Doamne Dumnezeul nostru, a Cărui stăpânire este neasemănată și slavă neajunsă, a Cărui milă este nemăsurată și iubire de oameni negrăită, Însuți Stăpâne, după milostivirea Ta, caută spre noi și spre sfântă biserica aceasta, și fă bogate milele Tale și îndurările Tale cu noi și cu cei ce se roagă împreună cu noi.
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key0201.title}{
RUGĂCIUNEA ANTIFONULUI ÎNTÂI
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key0202.title}{
ECTENIA MICĂ
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key0301.text}{
Doamne Dumnezeul nostru, mântuiește poporul Tău și binecuvintează moștenirea Ta; plinirea Bisericii Tale o păzește, sfințește pe cei ce iubesc podoaba casei Tale, Tu pe aceștia îi prea mărește cu dumnezeiască puterea Ta și nu ne lăsa pe noi, cei ce nădăjduim întru Tine.
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key0301.title}{
RUGĂCIUNEA ANTIFONULUI AL DOILEA
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key0401.text}{
Cel ce ne-ai dăruit nouă aceste rugăciuni obștești și împreună-glăsuite, Cel ce și la doi și la trei, care se unesc în numele Tău, ai făgăduit să le împlinești cererile, Însuți, și acum, plinește cererile cele de folos ale robilor Tăi dându-ne nouă, în veacul de acum, cunoștința adevărului Tău, și în cel ce va să fie, viață veșnică dăruindu-ne.
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key0401.title}{
RUGĂCIUNEA ANTIFONULUI AL TREILEA
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key0500.title}{
INTRAREA MICĂ CU SFÂNTA EVANGHELIE
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key0501.text}{
Stăpâne Doamne, Dumnezeul nostru, Cel ce ai așezat în ceruri cetele și oștile înge rilor și ale arhanghelilor spre slujba slavei Tale, fă ca împreună cu intrarea noastră să fie și intrarea sfinților îngeri, care slujesc împreună cu noi și împreună slăvesc bunătatea Ta. Că Ție se cuvine toată slava, cinstea și închi nă ciunea, Tatălui și Fiului și Sfântului Duh, acum și pururea și în vecii vecilor. Amin.
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key0501.title}{
RUGĂCIUNEA INTRĂRII
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key0502.text}{
Binecuvântează, părinte, sfânta intrare.
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key0503.text}{
Binecuvântată este intrarea sfinților Tăi, totdeauna, acum și pururea și în vecii vecilor.
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key0601.text}{
Dumnezeule cel sfânt, Care întru sfinți Te odihnești, Cel ce cu glas întreit-sfânt ești lăudat de serafimi și slăvit de heruvimi și de toată puterea cerească închinat; Cel ce dintru neființă întru ființă ai adus toate; Care ai zidit pe om după chipul și asemănarea Ta și cu tot harul Tău l-ai împodobit; Cel ce dai înțelepciune și pricepere celui ce cere, și nu treci cu vederea pe cel ce greșește, ci pui pocăința spre mântuire; Care ne-ai învrednicit pe noi, smeriții și nevrednicii robii Tăi, și în ceasul acesta, a sta înaintea slavei sfântului Tău jertfelnic și a-Ți aduce datorita închinare și preaslăvire;  Însuți Stăpâne, primește și din gurile noastre, ale păcătoșilor, întreit-sfânta cântare și ne cercetează pe noi întru bunătatea Ta. Iartă-ne nouă toată greșeala cea de voie și cea fără de voie; sfințește sufletele și trupurile noastre și ne dă nouă să slujim Ție cu cuvioșie în toate zilele vieții noastre. Pentru rugăciunile Preasfintei Născătoarei de Dumnezeu și ale tuturor sfinților care din veac au bine-plăcut Ție. Că sfânt ești Dumnezeul nostru și Ție slavă înălțăm, Tatălui și Fiului și Sfântului Duh, acum și pururea și în vecii vecilor. Amin.
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key0601.title}{
RUGĂCIUNEA CÂNTĂRII CELEI ÎNTREIT-SFINTE
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key0602.text}{
Puternic
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key0704.text}{
Strălucește în inimile noastre, Iubitorule de oameni, Stăpâne, lumina cea curată a cunoașterii Dumnezeirii Tale și deschide ochii gândului nostru spre înțelegerea evanghelicelor Tale propovăduiri. Pune în noi și frica fericitelor Tale porunci, ca toate poftele trupului călcând, viețuire duhovnicească să petrecem, cugetând și făcând toate cele ce sunt spre bună-plăcerea Ta. Că Tu ești luminarea sufletelor și a trupurilor noastre, Hristoase Dumnezeule și Ție slavă înălțăm, împreună și Celui fără de început al Tău Părinte și Preasfântului și bunului și de viață făcătorului Tău Duh, acum și pururea și în vecii vecilor. Amin.
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key0704.title}{
RUGĂCIUNEA DINAINTEA EVANGHELIEI
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key0706.title}{
PREDICA
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key0708}{
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key0709}{
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key0800.title}{
ECTENIA CERERII STĂRUITOARE
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key0801.text}{
Doamne Dumnezeul nostru, primește această rugăciune stăruitoare de la robii Tăi și ne miluiește pe noi, după mulțimea milei Tale, și trimite îndurările Tale peste noi și peste tot poporul Tău, care așteaptă de la Tine mare și multă milă.
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key0801.title}{
RUGĂCIUNEA CERERII STĂRUITOARE
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key0900.title}{
ECTENIA PENTRU CEI CHEMAȚI
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key0901.text}{
Rugați-vă cei chemați, Domnului.
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key0902.text}{
Cei credincioși, pentru cei chemați să ne rugăm.
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key0903.text}{
Ca Domnul să-i miluiască pe ei.
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key0904.text}{
Să-i învețe pe ei cuvântul adevărului.
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key0905.text}{
Să le descopere lor Evanghelia dreptății.
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key0906.text}{
Să-i unească pe ei cu Sfânta Sa sobornicescă și apostolească Biserică.
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key0907.text}{
Mântuiește, miluiește, apără și-i păzește pe ei, Dumnezeule, cu harul Tău.
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key0908.text}{
Cei chemați, capetele voastre Domnului să le plecați.
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key0909.text}{
Doamne Dumnezeul nostru, Cel ce întru cele de sus locuiești și spre cei smeriți privești, Care ai trimis mântuire neamului omenesc pe Unul-Născut Fiul Tău și Dumnezeu, pe Domnul nostru Iisus Hristos , caută spre robii Tăi cei chemați, care și-au plecat grumajii înaintea Ta, și-i învrednicește pe dânșii, la vremea potrivită, de baia nașterii celei de a doua, de iertarea păcatelor și de veșmântul nestricăciunii; unește-i pe dânșii cu sfânta Ta sobornicească și apostolească Biserică și-i numără pe dânșii cu turma Ta cea aleasă
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key0909.title}{
RUGĂCIUNEA PENTRU CEI CHEMAȚI
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key0910.text}{
Ca și aceștia împreună cu noi să slăvească preacinstitul și de mare cuviință numele Tău, al Tatălui și al Fiului și al Sfântului Duh, acum și pururea și în vecii vecilor.
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key0911.text}{
Câți sunteți chemați, ieșiți. Cei chemați, ieșiți. Câți sunteți chemați, ieșiți. Ca nimeni dintre cei chemați (să nu rămână).
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key0912.text}{
Câți suntem credincioși, iară și iară cu pace Domnului să ne rugăm.
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key1000.title}{
LITURGHIA CREDINCIOȘILOR
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key1001.text}{
Mulțumim Ție, Doamne, Dumnezeul Puterilor, Care ne-ai învrednicit pe noi a sta și acum înaintea sfântului Tău jertfelnic și a cădea la îndurările Tale, pentru păcatele noastre și pentru păcatele cele din neștiință ale poporului. Primește Dumnezeule, rugăciunea noastră; fă-ne să fim vrednici a-Ți aduce rugăciuni, cereri și jertfe fără de sânge pentru tot poporul Tău;  și ne învrednicește pe noi, pe care ne-ai pus întru această slujbă a Ta, cu puterea Duhului Tău celui Sfânt, ca fără de osândă și fără de sminteală, întru mărturia curată a cugetului nostru, să Te chemăm pe Tine în toată vremea și în tot locul și, auzindu-ne pe noi, milostiv să ne fii nouă, întru mulțimea bunătății Tale.
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key1001.title}{
RUGĂCIUNEA ÎNTÂI PENTRU CREDINCIOȘI
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key1002.text}{
Iarăși și de multe ori cădem la Tine și ne rugăm Ție, Bunule și Iubitorule de oameni, ca privind spre rugăciunea noastră, să curățești sufletele și trupurile noastre de toată necurăția trupului și a duhului și să ne dai nouă să stăm nevinovați și fără de osândă înaintea sfântului Tău jertfelnic. Și dăruiește, Dumnezeule, și celor ce se roagă împreună cu noi spor în viață, în credință și în înțelegerea cea duhovnicească. Dă lor să-Ți slujească totdeauna cu frică și cu dragoste și întru nevinovăție și fără osândă să se împărtășească cu Sfintele Tale Taine și să se învrednicească de cereasca Ta împărăție.
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key1002.title}{
RUGĂCIUNEA A DOUA PENTRU CREDINCIOȘI
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key1003.text}{
Ca sub stăpânirea Ta totdeauna fiind păziți, Ție slavă să înălțăm, Tatălui și Fiului și Sfântului Duh, acum și pururea și în vecii vecilor.
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key1100.title}{
INTRAREA MARE
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key1101.text}{
Nimeni din cei legați cu pofte și cu desfătări trupești nu este vrednic să vină, să se apropie, sau să slujească Ție, Împăratul slavei; căci a sluji Ție este lucru mare și înfricoșător chiar pentru puterile cele cerești. Dar, totuși, pentru iubirea Ta de oameni cea negrăită și nemăsurată, fără mutare și fără schimbare Te-ai făcut om, și Arhiereu al nostru Te-ai făcut, și, ca un Stăpân a toate, ne-ai dat slujba sfântă a acestei jertfe liturgice și fără sânge ; că singur Tu, Doamne Dumnezeul nostru, stăpânești cele cerești și cele pământești, Care Te porți pe scaunul heruvimilor, Domnul serafimilor și Împăratul lui Israel, Cel ce singur ești Sfânt și întru sfinți Te odihnești. Deci pe Tine Te rog, Cel ce singur ești bun și binevoitor, caută spre mine păcătosul și netrebnicul robul Tău, și-mi curățește sufletul și inima de cugete viclene; și învrednicește-mă, cu puterea Sfântului Tău Duh, pe mine, cel ce sunt îmbrăcat cu harul preoției, să stau înaintea sfintei Tale mese acesteia și să jertfesc sfântul și preacuratul Tău Trup și scumpul Tău Sânge. Căci la Tine vin, plecându-mi grumajii mei și mă rog Ție: Să nu întorci fața Ta de la mine, nici să mă lepezi dintre slujitorii Tăi, ci binevoiește să-Ți fie aduse darurile acestea de mine păcătosul și nevrednicul robul Tău. Că Tu ești Cel ce aduci și Cel ce Te aduci, Cel ce primești și Cel ce Te împarți, Hristoase, Dumnezeul nostru, și Ție slavă înălțăm, împreună și Celui fără de început al Tău Părinte și Preasfântului și bunului și de viață făcătorului Tău Duh, acum și pururea și în vecii vecilor. Amin
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key1101.title}{
RUGĂCIUNEA DIN TIMPUL CÂNTĂRII HERUVIMICE
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key1102.text}{
Noi, care pe heruvimi cu taină închipuim și făcătoarei de viață Treimi întreit-sfântă cântare aducem, toată grija cea lumească să o lepădăm.
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key1102.title}{
CÂNTAREA HERUVIMICĂ
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key1103.text}{
Ca pe Împăratul tuturor să-L primim. Ca pe Împăratul tuturor, să primim pe Cel înconjurat în chip nevăzut de cetele îngerești. Aliluia, aliluia, aliluia.
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key1110.text}{
Pe voi pe toți, dreptmăritorilor creștini, să vă pomenească Domnul Dumnezeu întru împărăția Sa, totdeauna, acum și pururea și în vecii vecilor.
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key1200.title}{
ECTENIA DARURILOR
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key1201.text}{
Pentru Cinstitele Daruri ce sunt puse înainte, Domnului să ne rugăm.
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key1202.text}{
Doamne, Dumnezeule, Atotțiitorule, Cel ce ești singur Sfânt, Care primești jertfă de laudă de la cei ce Te cheamă pe Tine cu toată inima, primește și rugăciunea noastră a păcătoșilor și o du la sfântul Tău jertfelnic; fă-ne vrednici a-Ți aduce Ție daruri și jertfe duhovnicești, pentru păcatele noastre și pentru cele din neștiință ale poporului. Și ne învrednicește să aflăm har înaintea Ta, ca să fie bineprimită jertfa noastră și să se sălășluiască Duhul cel bun al harului Tău peste noi, peste aceste daruri puse înainte și peste tot poporul Tău
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key1202.title}{
RUGĂCIUNEA PUNERII - ÎNAINTE
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key1203.text}{
Cu îndurările Unuia-Născut Fiului Tău, cu Care ești binecuvântat, împreună cu Preasfântul și bunul și de viață făcătorul Tău Duh, acum și pururea și în vecii vecilor.
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key1204.text}{
Să ne iubim unii pe alții, ca într-un gând să mărturisim.
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key1205.text}{
Pe Tatăl, pe Fiul și pe Sfântul Duh, Treimea cea de o ființă și nedespărțită.
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key1208.text}{
Ușile, ușile, cu înțelepciune să luăm aminte!
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key1209.title}{
SIMBOLUL CREDINȚEI (CREZUL)
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key1300.title}{
PREGĂTIREA PENTRU SFINȚIREA CINSTITELOR DARURI
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key1301.text}{
Să stăm bine, să stăm cu frică, să luăm aminte, Sfânta Jertfă cu pace a o aduce.
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key1302.text}{
Mila păcii, jertfa laudei.
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key1303.text}{
Harul Domnului nostru Iisus Hristos și dragostea lui Dumnezeu Tatăl și împărtășirea Sfântului Duh, să fie cu voi cu toți.
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key1304.text}{
Și cu duhul tău.
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key1305.text}{
Sus să avem inimile.
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key1306.text}{
Avem către Domnul.
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key1307.text}{
Să mulțumim Domnului.
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key1308.text}{
Cu vrednicie și cu dreptate este a ne închina Tatălui și Fiului și Sfântului Duh, Treimei celei de o ființă și nedespărțită.
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key1309.text}{
Cu vrednicie și cu dreptate este a-Ți cânta Ție, pe Tine a Te binecuvânta, pe Tine a Te lăuda, Ție a-Ți mulțumi, Ție a ne închina, în tot locul stăpânirii Tale; căci Tu ești Dumnezeu negrăit și necuprins cu gândul, nevăzut, neajuns, pururea fiind și același fiind: Tu și Unul-Născut Fiul Tău și Duhul Tău cel Sfânt. Tu din neființă la ființă ne-ai adus pe noi, și căzând noi, iarăși ne-ai ridicat și nu Te-ai depărtat, toate făcându-le, până ce ne-ai suit la cer și ne-ai dăruit împărăția Ta ce va să fie. Pentru toate acestea mulțumim Ție și Unuia-Născut Fiului Tău și Duhului Tău celui Sfânt, pentru toate pe care le știm și pe care nu le știm; pentru binefacerile Tale cele arătate și cele nearătate, ce ni s-au făcut nouă. Mulțumim Ție și pentru Liturghia aceasta, pe care ai binevoit a o primi din mâinile noastre, deși stau înaintea Ta mii de arhangheli și zeci de mii de îngeri, heruvimii cei cu ochi mulți și se rafimii cei cu câte șase aripi, care se înalță zburând.
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key1310.text}{
Cântare de biruință cântând, strigând, glas înălțând și grăind:
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key1311.text}{
Sfânt, Sfânt, Sfânt, Domnul Savaot! Plin este cerul și pământul de slava Ta! Osana întru cei de sus! Binecuvântat este cel ce vine întru numele Domnului! Osana întru cei de sus!
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key1312.text}{
Cu aceste fericite Puteri și noi, Iubitorule de oameni, Stăpâne, strigăm și grăim: Sfânt ești și Preasfânt, Tu și Unul-Născut Fiul Tău și Duhul Tău cel Sfânt. Sfânt ești și Preasfânt și slava Ta este plină de măreție. Căci Tu ai iubit lumea Ta atât de mult încât pe Unul-Născut Fiul Tău L-ai dat, ca tot cel ce crede într-Însul să nu piară, ci să aibă viață veșnică. Și Acesta venind și toată rânduiala cea pentru noi plinind, în noaptea întru care a fost vândut și mai vârtos Însuși pe Sine S-a dat pentru viața lumii, luând pâinea cu sfintele și preacuratele și fără prihană mâinile Sale, mulțumind și binecuvântând, sfințind și frângând, a dat Sfinților Săi Ucenici și Apostoli, zicând:
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key1313.text}{
Luați, mâncați, acesta este Trupul Meu, Care se frânge pentru voi spre iertarea păcatelor.
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key1314.text}{
Asemenea și paharul după cină zicând:
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key1315.text}{
Beți dintru acesta toți, acesta este Sângele Meu, al Legii celei noi, Care pentru voi și pentru mulți se varsă, spre iertarea păcatelor.
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key1316.text}{
Aducându-ne aminte, așadar, de această poruncă mântuitoare și de toate cele ce s-au făcut pentru noi: de cruce, de groapă, de învierea cea de a treia zi, de suirea la ceruri, de șederea cea de-a dreapta, și de cea de a doua și slăvită iarăși venire.
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key1317.text}{
Ale Tale dintru ale Tale, Ție Ți-aducem de toate și pentru toate.
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key1318.text}{
Pe Tine Te lăudăm, pe Tine Te binecuvântăm, Ție Îți mulțumim, Doamne, și ne rugăm Ție, Dumnezeul nostru.
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key1319.text}{
Încă aducem Ție această slujbă duhovnicească și fără de sânge, și Te chemăm, Te rugăm și cu umilință la Tine cădem: Trimite Duhul Tău cel Sfânt peste noi și peste aceste Daruri, ce sunt puse înainte.
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key1321.text}{
Și fă, adică, pâinea aceasta, Cinstit Trupul Hristosului Tău.
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key1323.text}{
Iar ceea ce este în potirul acesta, Cinstit Sângele Hristosului Tău.
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key1325.text}{
Prefăcându-le cu Duhul Tău cel Sfânt.
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key1326.text}{
Pentru ca să fie celor ce se vor împărtăși, spre trezirea sufletului, spre iertarea păcatelor, spre împărtășirea cu Sfântul Tău Duh, spre plinirea împărăției cerurilor, spre îndrăznirea cea către Tine, iar nu spre judecată sau spre osândă.
Încă aducem Ție această slujbă duhovnicească pentru cei adormiți întru credință: strămoși, părinți, patriarhi, prooroci, apostoli, propovăduitori, evangheliști, mucenici, mărturisitori, pustnici și pentru tot sufletul cel drept, care s-a săvârșit întru credință.
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key1327.text}{
Mai ales pentru Preasfânta, curata, prea binecuvântata, mărita stăpâna noastră, de Dumnezeu Născătoarea și pururea Fecioara Maria:
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key1329.text}{
Pentru Sfântul Ioan Proorocul, Înaintemergătorul și Botezătorul, pentru Sfinții măriții și întru tot lăudații Apostoli, pentru Sfântul (N), a cărui pomenire o săvârșim, și pentru toți sfinții Tăi; cu ale căror rugăciuni, cercetează-ne pe noi, Dumnezeule. Și pomenește pe toți cei adormiți întru nădejdea învierii și a vieții celei de veci și-i odihnește pe dânșii, Dumnezeul nostru, acolo unde strălucește lumina feței Tale. Încă Te rugăm: Pomenește, Doamne, pe toți episcopii ortodocși, care drept învață cuvântul adevărului Tău, toată preoțimea, cea întru Hristos diaconime și tot cinul preoțesc și monahicesc. Încă aducem Ție această slujbă duhovnicească pentru toată lumea, pentru sfânta sobornicească și apostolească Biserică; pentru cei ce în curăție și în viață cinstită viețuiesc, pentru (aici se pomenește cârmuirea țării, după îndrumările Sfântului Sinod). Dă lor, Doamne, pașnică ocârmuire, ca și noi, întru liniștea lor, viață pașnică și netulburată să trăim, în toată cucernicia și curăția.
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key1330a.text}{
Întâi pomenește, Doamne, pe
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key1330b.text}{
pe care-l dăruiește sfintelor Tale biserici în pace, întreg, cinstit, sănătos, îndelungat în zile, drept învățând cuvântul adevărului Tău.
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key1331.text}{
Și pomenește Doamne pe toti cei din inimile noastre.
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key1332.text}{
Pe toți și pe toate.
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key1333.text}{
Adu-Ți aminte, Doamne, de orașul (sau: de satul, sau: de sfânt locașul) acesta, în care viețuim și de toate orașele și satele și de cei ce cu credință viețuiesc într-însele. Adu-Ți aminte, Doamne, de cei ce călătoresc pe ape, pe uscat și prin aer, de cei bolnavi, de cei ce pătimesc, de cei robiți și de mântuirea lor. Adu-Ți aminte, Doamne, de cei ce aduc daruri și fac bine în sfintele Tale biserici, și își aduc aminte de cei săraci; și trimite peste noi toți milele Tale.
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key1334.text}{
Și ne dă nouă, cu o gură și cu o inimă, a slăvi și a cânta preacinstitul și de mare cuviință numele Tău, al Tatălui și al Fiului și al Sfântului Duh, acum și pururea și în vecii vecilor.
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key1335.text}{
Și să fie milele marelui Dumnezeu și Mântuitorului nostru Iisus Hristos cu voi cu toți.
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key1336.text}{
Și cu duhul tău.
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key1401.text}{
Pe toți sfinții pomenindu-i, iară și iară în pace, Domnului să ne rugăm.
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key1402.text}{
Pentru Cinstitele Daruri ce s-au adus și s-au sfințit, Domnului să ne rugăm.
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key1403.text}{
Ca Iubitorul de oameni, Dumnezeul nostru, Cel ce le-a primit pe Dânsele în sfântul, cel mai presus de ceruri și duhovnicescul Său jertfelnic, întru miros de bună mireasmă duhovnicească, să ne trimită nouă dumnezeiescul har și darul Sfântului Duh, să ne rugăm.
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key1404.text}{
Unirea credinței și împărtășirea Sfântului Duh cerând, pe noi înșine și unii pe alții și toată viața noastră lui Hristos Dumnezeu să o dăm.
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key1405.text}{
Ție, Stăpâne, Iubitorule de oameni, Îți încredințăm toată viața și nădejdea noastră și cerem și ne rugăm și cu umilință cădem înaintea Ta: Învrednicește-ne să ne împărtășim cu cuget curat, cu cereștile și înfricoșătoarele Tale Taine ale acestor sfinte și duhovnicești mese, spre lăsarea păcatelor, spre iertarea greșelilor spre împărtășirea cu Sfântul Duh, spre moștenirea împărăției cerurilor, spre îndrăznirea cea către Tine, iar nu spre judecată, sau spre osândă.
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key1406.text}{
Și ne învrednicește pe noi, Stăpâne, cu îndrăznire, fără de osândă, să cutezăm a Te chema pe Tine, Dumnezeul cel ceresc, Tată, și a zice:
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key1407.text}{
Mulțumim Ție, Împărate nevăzut, Cel ce toate le-ai făcut cu puterea Ta cea nemăsurată și cu mulțimea milei Tale din neființă la ființă toate le-ai adus. Însuți, Stăpâne, caută din cer spre cei ce și-au plecat Ție capetele lor; că nu le-au plecat trupului și sângelui, ci Ție, înfricoșătorului Dumnezeu. Tu deci, Stăpâne, cele puse înainte nouă tuturor, spre bine le întocmește, după trebuința deosebită a fiecăruia: cu cei ce călătoresc pe ape, pe uscat și prin aer împreună călătorește, pe cei bolnavi îi tămăduiește, Cel ce ești doctorul sufletelor și al trupurilor noastre.
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key1409.text}{
Ia aminte, Doamne Iisuse Hristoase, Dumnezeul nostru, din sfânt locașul Tău și de pe scaunul slavei împărăției Tale și vino ca să ne sfințești pe noi, Cel ce sus împreună cu Tatăl șezi și aici în chip nevăzut, împreună cu noi ești. Și ne învrednicește, prin mâna Ta cea puternică, a ni se da nouă Preacuratul Tău Trup și Scumpul Tău Sânge și prin noi la tot poporul.
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key1409.title}{
SFÂNTA ÎMPĂRTĂȘANIE
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key1410.text}{
...cele Sfinte celor sfinți.
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key1411.text}{
Unul Sfânt, unul Domn, Iisus Hristos, întru slava lui Dumnezeu-Tatăl. Amin.
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key1526.text}{
Cu frică de Dumnezeu, cu credință și cu dragoste să vă apropiați.
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key1527.text}{
Se împărtășește robul lui Dumnezeu (N) cu Cinstitul și Sfântul Trup și Sânge al Domnului și Dumnezeului și Mântuitorului nostru Iisus Hristos, spre iertarea păcatelor lui și spre viața de veci.
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key1528.rubric}{
Întorcându-se spre sfântul altar, diaconul dă sfântul potir preotului. Credincioșii se apropie, unul câte unul, să se împărtășească cu Sfintele Daruri.
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key1529.text}{
Mântuiește, Dumnezeule, poporul Tău și binecuvântează moștenirea Ta.
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key1530.text}{
Am văzut Lumina cea adevărată, am primit Duhul cel ceresc, am aflat credința cea
adevărată, nedespărțitei Sfintei Treimi închinăndu-ne, că Aceasta ne-a mântuit pe noi.
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key1603.text}{
Să se umple gurile noastre de lauda Ta, Doamne, ca să lăudăm slava Ta; că ne-ai învrednicit pe noi să ne împărtășim cu sfintele, dumnezeieștile, nemuritoarele, preacuratele și de viață făcătoarele Tale Taine. Întărește-ne pe noi întru sfințenia Ta, toată ziua să ne învățăm dreptatea Ta. Aliluia, aliluia, aliluia!
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key1604.text}{
Drepți, primind dumnezeieștile, sfintele, preacuratele, nemuritoarele, cereștile și de viață făcătoarele, înfricoșătoarele lui Hristos Taine, cu vrednicie să mulțumim Domnului.
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key1605.text}{
Ziua toată desăvârșită, sfântă, în pace și fără de păcat cerând, pe noi înșine și unii pe alții și toată viața noastră, lui Hristos Dumnezeu, să o dăm.
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key1606.text}{
Multumim Tie, Stapâne, Iubitorule de oameni, Datatorule de bine al sufletelor noastre, ca si în ziua de acum ne-ai învrednicit pe noi de cerestile si nemuritoarele Tale Taine. Îndrepteaza calea noastra, întareste-ne pe noi, pe toti, întru frica Ta; pazeste viata noastra, întareste pasii nostri, pentru rugaciunile si mijlocirile maritei Nascatoarei de Dumnezeu si pururea Fecioarei Maria si pentru ale tuturor sfintilor Tai.
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key1606.title}{
RUGĂCIUNEA DE MULȚUMIRE
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key1700.title}{
OTPUSTUL
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key1701.text}{
Cu pace să ieșim.
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key1702.text}{
Cel ce binecuvântezi pe cei ce Te binecuvântează, Doamne, și sfințești pe cei ce nădăjduiesc întru Tine, mântuiește poporul Tău și binecuvântează moștenirea Ta. Plinirea Bisericii Tale o păzește; sfințește pe cei ce iubesc podoaba casei Tale; Tu pe aceștia îi preamărește cu dumnezeiască puterea Ta; și nu ne lăsa pe noi cei ce nădăjduim întru Tine. Pace lumii Tale dăruiește, bisericilor Tale, preoților, (aici se pomenește Cârmuirea țării, după îndrumările Sfântului Sinod) și la tot poporul Tău. Că toată darea cea bună și tot darul desăvârșit de sus este, pogorând de la Tine, Părintele luminilor, și Ție slavă și mulțumire și închinăciune înălțăm, Tatălui și Fiului și Sfântului Duh, acum și pururea și în vecii vecilor.
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key1702.title}{
RUGĂCIUNEA AMVONULUI
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.Key1704.text}{
Plinirea Legii și a proorocilor Tu însuți fiind, Hristoase, Dumnezeul nostru, Cel ce ai plinit toată rânduiala părintească, umple de bucurie și de veselie inimile noastre, totdeauna, acum și pururea și în vecii vecilor. Amin.
}%
\itId{ro}{uk}{dur}{eu.lichrysbasil}{euLI.MM.HymnsDuringCommunion.title}{
IMNUL DIN TIMPUL SFINTEI ÎMPĂRTĂȘANII
}%
\itId{ro}{uk}{dur}{ho.s07}{hoLI.Antiphon1.text}{
Pentru rugăciunile Născătoarei de Dumnezeu, Mântuitorule, mântuiește-ne pe noi.
}%
\itId{ro}{uk}{dur}{ho.s07}{hoLI.Antiphon21.text}{
Mântuiește-ne pe noi, Fiul lui Dumnezeu,
}%
\itId{ro}{uk}{dur}{ho.s07}{hoLI.Antiphon22.text}{
pe noi cei ce-Ți cântăm. Aliluia.
}%
\itId{ro}{uk}{dur}{ho.s07}{hoLI.Antiphon2s.text}{
Cel ce ai înviat din morți,
}%
\itId{ro}{uk}{dur}{ho.s07}{hoLI.EntranceHymn.text}{
Veniti să ne închinam și să cădem la Hristos. Mântuiește-ne pe noi, Fiul lui Dumnezeu,
(Duminica) Cel ce ai înviat din morti, pe noi, cei ce-Ți cântam Ție: Aliluia.
(în zilele săptămânii) Cel ce ești minunat întru sfinți...
}%
\itId{ro}{uk}{dur}{ho.s07}{hoLI.OnlyBegotten.text}{
Unule-Născut, Fiule și Cuvântul lui Dumnezeu, Cel ce ești fără de moarte și ai primit, pentru mântuirea noastră, a Te întrupa din Sfânta Născătoare de Dumnezeu și pururea Fecioara Maria; Care neschimbat Te-ai întrupat. Și, răstignindu-Te, Hristoase Dumnezeule, cu moartea pe moarte ai călcat. Unul fiind din Sfânta Treime, împreună-slăvit cu Tatăl și cu Duhul Sfânt, mântuiește-ne pe noi!
}%
\itId{ro}{uk}{dur}{ho.s07}{hoLI.TrisagiosHymn.text}{
Sfinte Dumnezeule, Sfinte tare, Sfinte fără de moarte, miluiește-ne pe noi.
}%
\itId{ro}{uk}{dur}{ho.s07}{hoLI.TrisagiosHymn3.text}{
Sfinte fără de moarte,
}%
\itId{ro}{uk}{dur}{ho.s07}{hoLI.TrisagiosHymn4.text}{
miluiește-ne pe noi.
}%
\itId{ro}{uk}{dur}{ho.s21}{hoPrayer.Key101.text}{
Cred, Doamne, și mărturisesc că Tu ești cu adevărat Hristos, Fiul lui Dumnezeu celui viu, Care ai venit în lume să mântuiești pe cei păcătoși, dintre care cel dintâi sunt eu. Încă cred că Acesta este însuși Preacurat Trupul Tău și Acesta este însuși Scump Sângele Tău. Deci mă rog Ție: Miluiește-mă și-mi iartă greșelile mele cele de voie și cele fără de voie, cele cu cuvântul sau cu lucrul, cele întru știință și întru neștiință. Și mă învrednicește, fără osândă, să mă împărtășesc cu Preacuratele Tale Taine, spre iertarea păcatelor și spre viața de veci. Amin.
}%
\itId{ro}{uk}{dur}{ho.s21}{hoPrayer.Key110.text}{
Cinei Tale celei de taină, Fiul lui Dumnezeu, astăzi, părtaș mă primește, că nu voi spune vrăjmașilor Tăi, Taina Ta, nici sărutare Îți voi da ca Iuda, ci ca tâlharul mărturisindu-mă strig Ție: Pomenește-mă, Doamne, întru împărăția Ta.
}%
\itId{ro}{uk}{dur}{ho.s21}{hoPrayer.Key121.text}{
Nu spre judecată sau spre osândă să-mi fie mie împărtășirea cu Sfintele Tale Taine, Doamne, ci spre tămăduirea sufletului și a trupului. Amin.
}%
\itId{ro}{uk}{dur}{ho.s21}{hoPrayer.Key161.text}{
Stăpâne, Iubitorule de oameni, Doam­ne, Iisuse Hristoase, Dumne­zeul meu, să nu-mi fie mie spre osândă Sfintele acestea, pentru că sunt nevrednic, ci spre curățirea și sfințirea sufletului și a trupului și spre arvunirea vieții și a împărăției ce va să fie. „Iar mie bine-mi este a mă alipi de Dumnezeu și a pune în Domnul nădejdea mântuirii mele”.
}%
\itId{ro}{uk}{dur}{ho.s21}{hoPrayer.title}{
RUGĂCIUNEA SFINTEI ÎMPĂRTĂȘANII
}%
\itId{ro}{uk}{dur}{ho.s99}{bede.text}{
Întru negura veacului tău, o, Beda, spălat-ai pământurile Angliei și întreg Apusul cu râuri de Har, și ca un iscusit semănător ai sădit în lung și-n lat în ogorul Stăpânului tău sămânța cunoașterii dumnezeiești, de unde, răsărind, rod I-a adus însutit. Drept care, luând astfel îndrăzneală către El, o, Cuvioase, roagă-te neîncetat pentru mântuirea sufletelor noastre.
}%
\itId{ro}{uk}{dur}{ho.s99}{cuthbert.text}{
Călăuză vrednică a bisericii Northumbriei, întrecându-ți frații cu postul, cu privegherea și cu rugăciunea, vrednic ai fost găsit să primești un înger călător. Și ca o făclie strălucitoare, cu smerenie luminând în înălțime, ai primit darul facerilor de minuni. Și acum, locuind în Împărăția cea cerească, drepte părinte Cuthbert, roagă-L pe Hristos Dumnezeu să mântuiască sufletele noastre.
}%
\itId{ro}{uk}{dur}{ho.s99}{silouan.text}{
Pre Hristos, Învățător în calea smereniei, rugându-te, ai aflat, Duhul mărturisind în inima ta mântuirea; pentru aceasta, neamurile toate, acum la nădejde chemate, se veselesc întru pomenirea ta. Cuvioase Părinte Siluane, roagă pre Hristos Dumnezeu, să se mântuiască sufletele noastre.
}%
\itId{ro}{uk}{dur}{liturgical.verses}{psLI.aftercommunion.v1.text}{
Fie numele Domnului binecuvântat, de acum și până în veac.
}%
\itId{ro}{uk}{dur}{me.m10.d28}{alt1.meLI.Antiphon2.text}{
Mântuiește-ne pe noi, Fiule al lui Dumnezeu, Cel ce ești minunat întru sfinți, pe noi cei ce-Ți cântăm. Aliluia.
}%
\itId{ro}{uk}{dur}{misc}{vVerse1}{
Primul vers
}%
\itId{ro}{uk}{dur}{misc}{vVerse2}{
Al doilea vers
}%
\itId{ro}{uk}{dur}{misc}{vVerse3}{
Al treilea vers
}%
\itId{ro}{uk}{dur}{prayers}{Allilouia3.text}{
}%
\itId{ro}{uk}{dur}{prayers}{AxionEstinComplete.text}{
Cuvine-se cu adevărat să te fericim Născătoare de Dumnezeu, cea pururea fericită
și prea nevinovată și Maica Dumnezeului nostru. Ceea ce ești mai cinstită decât Heruvimii și mai
mărită fără de asemănare decât Serafimii, care fără stricăciune pe Dumnezeu-Cuvântul ai născut, pe
tine, cea cu adevărat Născătoare de Dumnezeu, te mărim.
}%
\itId{ro}{uk}{dur}{prayers}{DiEfchonPateron.text}{
Pentru rugăciunile sfinților părinților noștri, Doamne Iisuse Hristoase, Dumnezeul nostru, miluiește-ne pe noi.
}%
\itId{ro}{uk}{dur}{prayers}{DoxaPatri}{
Mărire Tatălui și Fiului și Sfântului Duh.
}%
\itId{ro}{uk}{dur}{prayers}{DoxaSoiKyrie}{
Slavă Ție, Doamne, slavă Ție.
}%
\itId{ro}{uk}{dur}{prayers}{DoxaSoiOTheosImon.text}{
Slavă Ție, Doamne, slavă Ție.
}%
\itId{ro}{uk}{dur}{prayers}{KaiNynKaiAei.text}{
Și acum și pururea și în vecii vecilor. Amin.
}%
\itId{ro}{uk}{dur}{prayers}{PantoteNyn.text}{
...totdeauna, acum și pururea și în vecii vecilor.
}%
\itId{ro}{uk}{dur}{prayers}{PaterImon.text}{
Tatăl nostru, Care ești în ceruri, sfințească-se numele Tău, vie împărăția Ta, facă-se voia Ta, precum în cer așa și pe pământ; pâinea noastră cea spre ființă dă-ne-o nouă astăzi, și ne iartă nouă greșalele noastre, precum și noi iertăm greșiților noștri, și nu ne duce pe noi în ispită, ci ne izbăvește de cel rău.
}%
\itId{ro}{uk}{dur}{prayers}{Pistevo.text}{
Cred într-unul Dumnezeu, Tatăl atotțiitorul, Făcătorul cerului și al pământului, al tuturor celor văzute și nevăzute.  
Și întru unul Domn Iisus Hristos, Fiul lui Dumnezeu, Unul Născut, Care din Tatăl S-a născut mai înainte de toți vecii: Lumină din Lumină, Dumnezeu adevărat din Dumnezeu adevărat, născut iar nu făcut, Cel de o ființă cu Tatăl, prin Care toate s-au făcut; 
Care pentru noi oamenii și pentru a noastră mântuire, S-a pogorât din ceruri și S-a întrupat de la Duhul Sfânt și din Fecioara Maria și S-a făcut om; 
Și S-a răstignit pentru noi în zilele lui Ponțiu Pilat și a pătimit
și S-a îngropat;  
Și a înviat a treia zi, după Scripturi;  
Și S-a înălțat la ceruri și șade de-a dreapta Tatălui; 
Și iarăși va să vină cu slavă să judece viii și morții, a Cărui împărăție nu va avea sfârșit.  
Și întru Duhul Sfânt, Domnul de viață Făcătorul, Care din Tatăl purcede, Cel ce împreună cu Tatăl și cu Fiul este închinat și slăvit, Care a grăit prin prooroci.  
Întru una, sfântă, sobornicească și apostolească Biserică;  
Mărturisesc un botez spre iertarea păcatelor;  
Aștept învierea morților; 
Și viața veacului ce va să fie. Amin.
}%
\itId{ro}{uk}{dur}{prayers}{enarxis02}{
Binecuvântată este împărăția Tatălui și a Fiului și a Sfântului Duh, acum și pururea și în vecii vecilor.
}%
\itId{ro}{uk}{dur}{prayers}{epi02}{
Pace tuturor.
}%
\itId{ro}{uk}{dur}{prayers}{exc01}{
Că Ție se cuvine toată slava, cinstea și închinăciunea, Tatălui și Fiului și Sfântului Duh, acum și pururea și în vecii vecilor.
}%
\itId{ro}{uk}{dur}{prayers}{exc02}{
Că a Ta este stăpânirea și a Ta este împărăția și puterea și slava, a Tatălui și a Fiului și a Sfântului Duh, acum și pururea și în vecii vecilor.
}%
\itId{ro}{uk}{dur}{prayers}{exc03}{
Că Dumnezeu bun și iubitor de oameni ești și Ție slavă înălțăm, Tatălui și Fiului și Sfântului Duh, acum și pururea și în vecii vecilor.
}%
\itId{ro}{uk}{dur}{prayers}{exc05a}{
Că sfânt ești Dumnezeul nostru și Ție slavă înălțăm, Tatălui și Fiului și Sfântului Duh, acum și pururea,
}%
\itId{ro}{uk}{dur}{prayers}{exc05b}{
Și în vecii vecilor.
}%
\itId{ro}{uk}{dur}{prayers}{exc07a}{
Cu harul și cu îndurările și cu iubirea de oameni a Unuia-Născut Fiului Tău, cu Care ești binecuvântat, împreună cu Preasfântul și bunul și de viață făcătorul Tău Duh, acum și pururea și în vecii vecilor.
}%
\itId{ro}{uk}{dur}{prayers}{exc11}{
Că milostiv și iubitor de oameni Dumnezeu ești și Ție slavă înălțăm, Tatălui și Fiului și Sfântului Duh, acum și pururea și în vecii vecilor.
}%
\itId{ro}{uk}{dur}{prayers}{exc17}{
Înțelepciune!
}%
\itId{ro}{uk}{dur}{prayers}{exc18}{
Drepți!
}%
\itId{ro}{uk}{dur}{prayers}{exc19}{
Să luăm aminte.
}%
\itId{ro}{uk}{dur}{prayers}{exc20}{
Că a Ta este împărăția și puterea și slava, a Tatălui și a Fiului și a Sfântului Duh, acum și pururea și în vecii vecilor.
}%
\itId{ro}{uk}{dur}{prayers}{exc24}{
Că Tu ești sfințirea noastră și Ție slavă înălțăm, Tatălui și Fiului și Sfântului Duh, acum și pururea și în vecii vecilor.
}%
\itId{ro}{uk}{dur}{prayers}{gos02}{
Să ascultăm Sfânta Evanghelie.
}%
\itId{ro}{uk}{dur}{prayers}{gos03a}{
Din Sfânta Evanghelie
}%
\itId{ro}{uk}{dur}{prayers}{gos03b}{
de la (N) citire.
}%
\itId{ro}{uk}{dur}{prayers}{gos04}{
(în taină) Pace ție, celui ce ai binevestit.
}%
\itId{ro}{uk}{dur}{prayers}{pet00}{
Domnului să ne rugăm.
}%
\itId{ro}{uk}{dur}{prayers}{pet01}{
În pace, Domnului sa ne rugăm.
}%
\itId{ro}{uk}{dur}{prayers}{pet02}{
Pentru pacea de sus și pentru mântuirea sufletelor noastre, Domnului să ne rugăm.
}%
\itId{ro}{uk}{dur}{prayers}{pet03}{
Pentru pacea a toată lumea, pentru bună starea sfintelor lui Dumnezeu Biserici și pentru unirea tuturor, Domnului să ne rugăm.
}%
\itId{ro}{uk}{dur}{prayers}{pet04}{
Pentru sfântă biserica aceasta și pentru cei ce cu credință, cu evlavie și cu frică de Dumnezeu intră într-însa, Domnului să ne rugăm.
}%
\itId{ro}{uk}{dur}{prayers}{pet05}{
Pentru binecredincioasele popoare creștine ale lumii, Domnului să ne rugăm.
}%
\itId{ro}{uk}{dur}{prayers}{pet06a}{
Pentru
}%
\itId{ro}{uk}{dur}{prayers}{pet06b}{
pentru cinstita preoțime și cea întru Hristos diaconime, și pentru tot clerul și poporul, Domnului să ne rugăm.
}%
\itId{ro}{uk}{dur}{prayers}{pet07S}{
Pentru (aici se pomenește Cârmuirea țării, după îndrumările Sfântului Sinod ), Domnului să ne rugăm.
}%
\itId{ro}{uk}{dur}{prayers}{pet08}{
Pentru sfânt locașul acesta, țara aceasta și pentru toate orașele și satele și pentru cei ce cu credință locuiesc într-însele, Domnului să ne rugăm.
}%
\itId{ro}{uk}{dur}{prayers}{pet09}{
Pentru buna-întocmire a văzduhului, pentru îmbelșugarea roadelor pământului și pentru vremuri cu pace, Domnului să ne rugăm.
}%
\itId{ro}{uk}{dur}{prayers}{pet10}{
Pentru cei ce călătoresc pe ape, pe uscat și prin aer, pentru cei bolnavi, pentru cei ce se ostenesc, pentru cei robiți și pentru mântuirea lor, Domnului să ne rugăm.
}%
\itId{ro}{uk}{dur}{prayers}{pet11}{
Pentru ca să fim izbăviți noi de tot necazul, mânia, primejdia și nevoia, Domnului să ne rugăm.
}%
\itId{ro}{uk}{dur}{prayers}{pet12}{
Apără, mântuiește, miluiește și ne păzește pe noi, Dumnezeule, cu harul Tău.
}%
\itId{ro}{uk}{dur}{prayers}{pet13}{
Pe Preasfânta, curata, preabinecuvântata, mărita stăpâna noastră, de Dumnezeu Născătoarea și pururea Fecioara Maria, cu toți sfinții să o pomenim.
Pe noi înșine și unii pe alții și toată viața noastră lui Hristos Dumnezeu să o dăm.
}%
\itId{ro}{uk}{dur}{prayers}{pet14}{
Iară și iară în pace, Domnului să ne rugăm.
}%
\itId{ro}{uk}{dur}{prayers}{pet15}{
Să zicem toți, din tot sufletul și din tot cugetul nostru să zicem.
}%
\itId{ro}{uk}{dur}{prayers}{pet16}{
Doamne, Atotstăpânitorule, Dumnezeul părinților noștri, rugămu-ne Ție, auzi-ne și ne miluiește.
}%
\itId{ro}{uk}{dur}{prayers}{pet17}{
Miluiește-ne pe noi, Dumnezeule, după mare mila Ta, rugămu-ne Ție, auzi-ne și ne miluiește.
}%
\itId{ro}{uk}{dur}{prayers}{pet19Sa}{
Încă ne rugăm pentru
}%
\itId{ro}{uk}{dur}{prayers}{pet20}{
Încă ne rugăm pentru frații noștri: preoți, ieromonahi, ierodiaconi, diaconi, monahi și monahii și pentru toți cei întru Hristos frați ai noștri.
}%
\itId{ro}{uk}{dur}{prayers}{pet21}{
Încă ne rugăm pentru mila, viața, pacea, sănătatea, mântuirea, cercetarea, lăsarea și iertarea păcatelor robilor lui Dumnezeu enoriași, ctitori și binefăcători ai sfântului locașului acestuia.
}%
\itId{ro}{uk}{dur}{prayers}{pet22}{
Încă ne rugăm pentru fericiții și pururea pomeniții ctitori ai sfânt locașului acestuia și pentru toți cei mai dinainte adormiți părinți și frați ai noștri dreptmăritori creștini, care odihnesc aici și pretutindeni.
}%
\itId{ro}{uk}{dur}{prayers}{pet23}{
Încă ne rugăm pentru cei ce aduc daruri și fac bine în sfânta și întru tot cinstită biserica aceasta, pentru cei ce se ostenesc, pentru cei ce cântă și pentru poporul ce stă înainte și așteaptă de la Tine mare și multă milă.
}%
\itId{ro}{uk}{dur}{prayers}{pet24}{
Să plinim rugăciunea noastră Domnului.
}%
\itId{ro}{uk}{dur}{prayers}{pet25m}{
Ziua toată desăvârșită, sfântă, în pace și fără de păcat, la Domnul să cerem.
}%
\itId{ro}{uk}{dur}{prayers}{pet26}{
Înger de pace, credincios îndreptător, păzitor al sufletelor și al trupurilor noastre, la Domnul să cerem.
}%
\itId{ro}{uk}{dur}{prayers}{pet27}{
Milă și iertare de păcatele și de greșelile noastre, la Domnul să cerem.
}%
\itId{ro}{uk}{dur}{prayers}{pet28}{
Cele bune și de folos sufletelor noastre și pace lumii, la Domnul să cerem.
}%
\itId{ro}{uk}{dur}{prayers}{pet29}{
Cealaltă vreme a vieții noastre în pace și întru pocăință a o săvârși, la Domnul să cerem.
}%
\itId{ro}{uk}{dur}{prayers}{pet30}{
Sfârșit creștinesc vieții noastre, fără durere, neînfruntat, în pace și răspuns bun la înfricoșătoarea judecată a lui Hristos, să cerem.
}%
\itId{ro}{uk}{dur}{prayers}{pet31}{
Pace tuturor!
}%
\itId{ro}{uk}{dur}{prayers}{pet32}{
Capetele voastre, Domnului să le plecați.
}%
\itId{ro}{uk}{dur}{prayers}{pet37}{
Binecuvântarea Domnului peste voi toți cu al Său har și cu a Sa iubire de oameni, totdeauna, acum și pururea și în vecii vecilor.
}%
\itId{ro}{uk}{dur}{prayers}{res01}{
Doamne, miluiește.
}%
\itId{ro}{uk}{dur}{prayers}{res02}{
Dă, Doamne.
}%
\itId{ro}{uk}{dur}{prayers}{res03}{
Ție, Doamne.
}%
\itId{ro}{uk}{dur}{prayers}{res04}{
Amin.
}%
\itId{ro}{uk}{dur}{prayers}{res05}{
Și duhului tău.
}%
\itId{ro}{uk}{dur}{prayers}{res06}{
Doamne miluieste. Doamne miluieste. Doamne miluieste.
}%
\itId{ro}{uk}{dur}{prayers}{res08}{
Binecuvântează, stăpâne.
}%
\itId{ro}{uk}{dur}{prayers}{res10}{
Amin. Amin. Amin.
}%
\itId{ro}{uk}{dur}{prayers}{res13}{
Întru numele Domnului, parinte, binecuvânteaza.
}%
\itId{ro}{uk}{dur}{ps}{psa102.v1.text}{
Binecuvintează, suflete al meu pe Domnul, și toate cele dinlăuntrul meu, numele cel sfânt al Lui.
}%
\itId{ro}{uk}{dur}{ps}{psa102.v19.text}{
Domnul în cer a gătit scaunul Său și împărăția Lui peste toți stăpânește.
}%
\itId{ro}{uk}{dur}{ps}{psa102.v2.text}{
Binecuvintează, suflete al meu, pe Domnul și nu uita toate răsplătirile Lui.
}%
\itId{ro}{uk}{dur}{ps}{psa117.v1.text}{
Lăudați pe Domnul, că este bun, că în veac este mila Lui!
}%
\itId{ro}{uk}{dur}{ps}{psa145.v1.text}{
Laudă, suflete al meu, pe Domnul:
}%
\itId{ro}{uk}{dur}{ps}{psa145.v10.text}{
Împărăți-va Domnul în veci, Dumnezeul tău, Sioane, în neam și în neam.
}%
\itId{ro}{uk}{dur}{ps}{psa145.v2.text}{
Lăuda-voi pe Domnul în viața mea, cânta-voi Dumnezeului meu cât voi trăi.
}%
\itId{ro}{uk}{dur}{ps}{psa145.v5.text}{
Fericit e cel căruia Dumnezeul lui Iacob îi este ajutor, a cărui nădejde e în Domnul Dumnezeul lui.
}%
\itId{ro}{uk}{dur}{ps}{psa68.v35.text}{
Să-L laude pe El cerurile și pământul.
}%
\itId{ro}{uk}{dur}{pub.priest.servicebook}{doxapatrikainyn}{
Mărire Tatălui și Fiului și Sfântului Duh. Și acum și pururea și în vecii vecilor. Amin.
}%
\itId{ro}{uk}{dur}{pub.priest.servicebook}{li.blessboth}{
Binecuvânteaza-le, părinte, pe amândouă.
}%
\itId{ro}{uk}{dur}{pub.priest.servicebook}{li.blessingmercy}{
Ajutorul meu de la Domnul, Cel ce a făcut cerul și pământul.
}%
\itId{ro}{uk}{dur}{pub.priest.servicebook}{li.blessreader}{
Binecuvânteaza, parinte, pe binevestitorul Sfântului Apostol si Evanghelist (N)
}%
\itId{ro}{uk}{dur}{pub.priest.servicebook}{li.blessreader2}{
Dumnezeu, pentru rugăciunile Sfântului, întru tot lăudatului Apostol si Evanghelist (N) să-ți dea ție, celui ce binevestești, cuvânt cu putere multă, spre plinirea Evangheliei iubitului Său Fiu, a Domnului nostru Iisus Hristos.
}%
\itId{ro}{uk}{dur}{pub.priest.servicebook}{li.changebread}{
Binecuvânteaza, părinte, sfânta pâine.
}%
\itId{ro}{uk}{dur}{pub.priest.servicebook}{li.changewine}{
Binecuvânteaza, părinte, sfântul potir.
}%
\itId{ro}{uk}{dur}{pub.priest.servicebook}{li.dis.oanastas}{
}%
\itId{ro}{uk}{dur}{pub.priest.servicebook}{li.end.title.doc}{
SFÂRȘITUL SFINTEI LITURGHII A SFÂNTULUI IOAN GURĂ DE AUR
}%
\itId{ro}{uk}{dur}{pub.priest.servicebook}{li.godisthelord}{
Bine este cuvântat Cel ce vine întru numele Domnului; Dumnezeu este Domnul și s-a arătat nouă.
}%
\itId{ro}{uk}{dur}{pub.priest.servicebook}{li.litanylordsprayer.title.doc}{
ECTENIA DE DINAINTEA RUGĂCIUNII DOMNEȘTI
}%
\itId{ro}{uk}{dur}{pub.priest.servicebook}{li.lordsname}{
Întru Numele Domnului.
}%
\itId{ro}{uk}{dur}{pub.priest.servicebook}{li.preparation.mercy}{
Dumnezeule, curățește-mă pe mine păcătosul și mă miluiește.
}%
\itId{ro}{uk}{dur}{pub.priest.servicebook}{li.prokeimenonmode}{
Prochimenul
}%
\itId{ro}{uk}{dur}{pub.priest.servicebook}{li.readings.title.doc}{
DIN EPISTOLELE SFINȚILOR APOSTOLI CITIRE
}%
\itId{ro}{uk}{dur}{pub.priest.servicebook}{li.rubric.alldays}{
Iar apoi, în toate zilele:
}%
\itId{ro}{uk}{dur}{pub.priest.servicebook}{li.rubric.bede}{
Tonul al 8-lea. Troparul Sfântului Beda
}%
\itId{ro}{uk}{dur}{pub.priest.servicebook}{li.rubric.blesswithgospel}{
Preotul, primind Sfânta Evanghelie de la diacon, o săruta și-i binecuvântează pe credincioși cu ea în semnul crucii după care o așeaza pe Sfânta Masă deasupra sfântului antimis.
}%
\itId{ro}{uk}{dur}{pub.priest.servicebook}{li.rubric.bowcommunion}{
Preotul și diaconul se închină de trei ori, zicând în taină de fiecare dată:
}%
\itId{ro}{uk}{dur}{pub.priest.servicebook}{li.rubric.catechumens}{
Aici poate urma ectenia pentru catehumeni.
}%
\itId{ro}{uk}{dur}{pub.priest.servicebook}{li.rubric.catechumens2}{
După fiecare ectenie, Strana zice:
}%
\itId{ro}{uk}{dur}{pub.priest.servicebook}{li.rubric.cuthbert}{
Tonul al 8-lea. Troparul Sfântului Cuthbert
}%
\itId{ro}{uk}{dur}{pub.priest.servicebook}{li.rubric.deaconquietly}{
Diaconul zice în taină:
}%
\itId{ro}{uk}{dur}{pub.priest.servicebook}{li.rubric.eachpetition}{
Și apoi după fiecare ectenie.
}%
\itId{ro}{uk}{dur}{pub.priest.servicebook}{li.rubric.eachpetition2}{
(Aici și la următoarele cereri)
}%
\itId{ro}{uk}{dur}{pub.priest.servicebook}{li.rubric.giveantidoron}{
Preotul și diaconul împart anafura oamenilor, zicând:
}%
\itId{ro}{uk}{dur}{pub.priest.servicebook}{li.rubric.kontakion1}{
Troparele zilei și cele dedicate parohiei se cântă:
}%
\itId{ro}{uk}{dur}{pub.priest.servicebook}{li.rubric.notsunday}{
În zilele de peste săptămână, se cântă:
}%
\itId{ro}{uk}{dur}{pub.priest.servicebook}{li.rubric.preach}{
Dupa citirea textului Evangheliei, urmează de obicei predica.
}%
\itId{ro}{uk}{dur}{pub.priest.servicebook}{li.rubric.readgospel}{
Dupa citirea Sfintei Evanghelii, diaconul îndreaptă cartea către preot care zice:
}%
\itId{ro}{uk}{dur}{pub.priest.servicebook}{li.rubric.resurrectionmode}{
Apoi imnul Învierii în tonul curent.
}%
\itId{ro}{uk}{dur}{pub.priest.servicebook}{li.rubric.silouan}{
Tonul al 3-lea. Troparul Sfântului Siluan
}%
\itId{ro}{uk}{dur}{pub.priest.servicebook}{li.rubric.smallentrance}{
În timp ce strana cânta antifonul al treilea sau Fericirile, preotul și diaconul fac trei închinăciuni înaintea Sfintei Mese. Preotul ridică Sfânta Evanghelie și o dă diaconului. Diaconul merge înaintea preotului în jurul altarului. Ei ies pe ușa dinspre miazănoapte și se opresc în mijlocul bisericii.
}%
\itId{ro}{uk}{dur}{pub.priest.servicebook}{li.rubric.sundayantifon3}{
Se cânta Fericirile sau al Treilea Antifon
}%
\itId{ro}{uk}{dur}{pub.priest.servicebook}{li.rubric.sundaydismissal}{
(Duminica: Cel ce a înviat din morți,)
}%
\itId{ro}{uk}{dur}{pub.priest.servicebook}{li.rubric.thriceeach}{
De trei ori, si la fel după fiecare cerere.
}%
\itId{ro}{uk}{dur}{pub.priest.servicebook}{li.thanksdismissal.title.doc}{
ECTENIA DE MULȚUMIRE
}%
\itId{ro}{uk}{dur}{rubrical}{BeginLiturgy}{
Preotul ia Sfânta Evanghelie cu amândouă mâinile, o ridică puțin și face semnul Sfintei Cruci pe sfântul antimis, începând cu capătul de sus, apoi cu cel de jos, la stânga și la dreapta zicând:
}%
\itId{ro}{uk}{dur}{rubrical}{DeaconStart}{
Sfintele uși sunt deschise și perdeaua ridicată. Diaconul, stând în fata ușilor împărătești zice cu glas mare:
}%
\itId{ro}{uk}{dur}{rubrical}{InALowVoice}{
(citește în taină)
}%
\itId{ro}{uk}{dur}{rubrical}{Or}{
\emph{sau:}
}%
\itId{ro}{uk}{dur}{rubrical}{Thrice}{
}%
\itId{ro}{uk}{dur}{rubrical}{cl.eu.lichrysbasil.R009}{
Din Faptele Sfinților Apostoli citire
}%
\itId{ro}{uk}{dur}{rubrical}{cl.eu.lichrysbasil.R010}{
Se citește Apostolul zilei și apoi preotul zice:
}%
\itId{ro}{uk}{dur}{template.titles}{li2.html.tab}{
DUMNEZEIASCA LITURGHIE A CELUI ÎNTRE SFINȚI, PĂRINTELUI NOSTRU IOAN GURĂ DE AUR
}%
\itId{ro}{uk}{dur}{template.titles}{li2.html.tab.doc}{
DUMNEZEIASCA LITURGHIE A CELUI ÎNTRE SFINȚI, PĂRINTELUI NOSTRU IOAN GURĂ DE AUR
}%
\itId{ro}{uk}{dur}{template.titles}{li2.html.tab.header}{
DUMNEZEIASCA LITURGHIE A CELUI ÎNTRE SFINȚI, PĂRINTELUI NOSTRU IOAN GURĂ DE AUR
}%
\itId{ro}{uk}{dur}{template.titles}{li2.html.tab.toc}{
DUMNEZEIASCA LITURGHIE A CELUI ÎNTRE SFINȚI, PĂRINTELUI NOSTRU IOAN GURĂ DE AUR
}%
\itId{ro}{uk}{dur}{titles}{Eisodikon}{
IMNUL INTRĂRII
}%
\itId{ro}{uk}{dur}{titles}{KyriakiProsefchi}{
RUGĂCIUNEA DOMNEASCĂ
}%
\itId{ro}{uk}{dur}{titles}{LitCatechumens}{
LITURGHIA CATEHUMENILOR
}%
\itId{ro}{uk}{dur}{variables.info}{Antiphon1.title}{
ANTIFONUL ÎNTÂI
}%
\itId{ro}{uk}{dur}{variables.info}{Antiphon2.title}{
ANTIFONUL AL DOILEA
}%
\itId{ro}{uk}{dur}{variables.info}{TheotokosHymn.title}{
AXIONUL NĂSCĂTOAREI DE DUMNEZEU
}%
\itId{ro}{uk}{dur}{variables.info}{Trisagion.title}{
CÂNTAREA CEA ÎNTREIT-SFÂNTĂ
}%
\itId{en}{uk}{durlash}{pdf}{title.doc}{
}%
\itId{en}{uk}{durlash}{pdf}{title.toc}{
}%
\itId{en}{uk}{durlash}{pdf}{title.header}{
}%
\itId{en}{uk}{durlash}{pdf}{title.date}{
}%
\itId{ro}{uk}{dur}{pdf}{title.doc}{
}%
\itId{ro}{uk}{dur}{pdf}{title.toc}{
}%
\itId{ro}{uk}{dur}{pdf}{title.header}{
}%
\itId{ro}{uk}{dur}{pdf}{title.date}{
}%

\ltColumnsOn
\ltChapter{pdf}{title}
\ltParaRedBold{template.titles}{li2.html.tab}
\ltRubricItalics{rubrical}{DeaconStart}
\ltDialog{prayers}{res08}
\ltRubricItalics{rubrical}{BeginLiturgy}
\ltDialog{prayers}{enarxis02}
\ltActorSingleLine{actors}{People}
\ltDialog{prayers}{res04}
\ltSmallTitle{eu.lichrysbasil}{euLI.Key0200.text}
\ltActorSingleLine{actors}{Deacon}
\ltDialog{prayers}{pet01}
\ltActorSingleLine{actors}{People}
\ltDialogItalics{prayers}{res01}{pub.priest.servicebook}{li.rubric.eachpetition}
\ltDialog{prayers}{pet02}
\ltDialog{prayers}{pet03}
\ltDialog{prayers}{pet04}
\ltDialog{prayers}{pet05}
\ltDialog{prayers}{pet06a}{client}{cl.bishop1.rank}{client}{cl.bishop1.name.c}{prayers}{pet06b}
\ltDialog{prayers}{pet07S}
\ltDialog{prayers}{pet08}
\ltDialog{prayers}{pet09}
\ltDialog{prayers}{pet10}
\ltDialog{prayers}{pet11}
\ltDialog{prayers}{pet12}
\ltDialog{prayers}{pet13}
\ltActorSingleLine{actors}{People}
\ltDialog{prayers}{res03}
\ltSmallTitle{eu.lichrysbasil}{euLI.Key0201.title}
\ltActorRubric{actors}{Priest}{rubrical}{InALowVoice}
\ltDialogInaudible{eu.lichrysbasil}{euLI.Key0201.text}
\ltActorSingleLine{actors}{Priest}
\ltDialog{prayers}{exc01}
\ltActorSingleLine{actors}{People}
\ltDialog{prayers}{res04}
\ltSmallTitle{variables.info}{Antiphon1.title}
\ltDialog{pub.priest.servicebook}{doxapatrikainyn}
\ltUnknown{misc}{vVerse1}
\ltDialog{ps}{psa102.v1.text}
\ltActorSingleLine{actors}{People}
\ltDialog{ho.s07}{hoLI.Antiphon1.text}
\ltUnknown{misc}{vVerse2}
\ltDialog{ps}{psa102.v2.text}
\ltActorSingleLine{actors}{People}
\ltDialog{ho.s07}{hoLI.Antiphon1.text}
\ltUnknown{misc}{vVerse3}
\ltDialog{ps}{psa102.v19.text}
\ltActorSingleLine{actors}{People}
\ltDialog{ho.s07}{hoLI.Antiphon1.text}
\ltDialog{pub.priest.servicebook}{doxapatrikainyn}
\ltSmallTitle{eu.lichrysbasil}{euLI.Key0202.title}
\ltActorSingleLine{actors}{Deacon}
\ltDialog{prayers}{pet14}
\ltActorSingleLine{actors}{People}
\ltDialog{prayers}{res01}
\ltActorSingleLine{actors}{Deacon}
\ltDialog{prayers}{pet12}
\ltActorSingleLine{actors}{People}
\ltDialog{prayers}{res01}
\ltActorSingleLine{actors}{Deacon}
\ltDialog{prayers}{pet13}
\ltActorSingleLine{actors}{People}
\ltDialog{prayers}{res03}
\ltSmallTitle{eu.lichrysbasil}{euLI.Key0301.title}
\ltActorRubric{actors}{Priest}{rubrical}{InALowVoice}
\ltDialogInaudible{eu.lichrysbasil}{euLI.Key0301.text}
\ltActorSingleLine{actors}{Priest}
\ltDialog{prayers}{exc02}
\ltActorSingleLine{actors}{People}
\ltDialog{prayers}{res04}
\ltSmallTitle{variables.info}{Antiphon2.title}
\ltUnknown{pub.priest.servicebook}{li.rubric.notsunday}{me.m10.d28}{alt1.meLI.Antiphon2.text}
\ltUnknown{misc}{vVerse1}
\ltDialog{ps}{psa145.v1.text}{ps}{psa145.v2.text}
\ltActorSingleLine{actors}{People}
\ltDialog{ho.s07}{hoLI.Antiphon21.text}{ho.s07}{hoLI.Antiphon2s.text}{ho.s07}{hoLI.Antiphon22.text}
\ltUnknown{misc}{vVerse2}
\ltDialog{ps}{psa145.v5.text}
\ltActorSingleLine{actors}{People}
\ltDialog{ho.s07}{hoLI.Antiphon21.text}{ho.s07}{hoLI.Antiphon2s.text}{ho.s07}{hoLI.Antiphon22.text}
\ltUnknown{misc}{vVerse3}
\ltDialog{ps}{psa145.v10.text}
\ltActorSingleLine{actors}{People}
\ltDialog{ho.s07}{hoLI.Antiphon21.text}{ho.s07}{hoLI.Antiphon2s.text}{ho.s07}{hoLI.Antiphon22.text}
\ltDialog{prayers}{DoxaPatri}
\ltRubric{pub.priest.servicebook}{li.rubric.alldays}
\ltDialog{prayers}{KaiNynKaiAei.text}
\ltDialog{ho.s07}{hoLI.OnlyBegotten.text}
\ltSmallTitle{eu.lichrysbasil}{euLI.Key0202.title}
\ltActorSingleLine{actors}{Deacon}
\ltDialog{prayers}{pet14}
\ltActorSingleLine{actors}{People}
\ltDialog{prayers}{res01}
\ltActorSingleLine{actors}{Deacon}
\ltDialog{prayers}{pet12}
\ltActorSingleLine{actors}{People}
\ltDialog{prayers}{res01}
\ltActorSingleLine{actors}{Deacon}
\ltDialog{prayers}{pet13}
\ltActorSingleLine{actors}{People}
\ltDialog{prayers}{res03}
\ltSmallTitle{eu.lichrysbasil}{euLI.Key0401.title}
\ltActorRubric{actors}{Priest}{rubrical}{InALowVoice}
\ltDialogInaudible{eu.lichrysbasil}{euLI.Key0401.text}
\ltActorSingleLine{actors}{Priest}
\ltDialog{prayers}{exc03}
\ltActorSingleLine{actors}{People}
\ltDialog{prayers}{res04}
\ltDesignation{eu.lichrysbasil}{euLI.Key0500.title}
\ltRubric{pub.priest.servicebook}{li.rubric.sundayantifon3}
\ltUnknown{misc}{vVerse1}
\ltDialog{ps}{psa117.v1.text}
\ltRubric{pub.priest.servicebook}{li.rubric.resurrectionmode}
\ltUnknown{misc}{vVerse2}
\ltDialog{ps}{psa68.v35.text}
\ltRubric{pub.priest.servicebook}{li.rubric.resurrectionmode}
\ltRubricItalics{pub.priest.servicebook}{li.rubric.smallentrance}
\ltRubricItalics{pub.priest.servicebook}{li.rubric.deaconquietly}
\ltDialogInaudible{prayers}{pet00}
\ltSmallTitle{eu.lichrysbasil}{euLI.Key0501.title}
\ltActorRubric{actors}{Priest}{rubrical}{InALowVoice}
\ltDialogInaudible{eu.lichrysbasil}{euLI.Key0501.text}{prayers}{exc01}
\ltActorRubric{actors}{Deacon}{rubrical}{InALowVoice}
\ltDialogInaudible{eu.lichrysbasil}{euLI.Key0502.text}
\ltActorRubric{actors}{Priest}{rubrical}{InALowVoice}
\ltDialogInaudible{eu.lichrysbasil}{euLI.Key0503.text}{prayers}{res04}
\ltActorSingleLine{actors}{Deacon}
\ltDialog{prayers}{exc17}{prayers}{exc18}
\ltSmallTitle{titles}{Eisodikon}
\ltActorSingleLine{actors}{People}
\ltDialog{ho.s07}{hoLI.EntranceHymn.text}
\ltRubricItalics{pub.priest.servicebook}{li.rubric.kontakion1}
\ltRubricItalics{pub.priest.servicebook}{li.rubric.cuthbert}
\ltDialog{ho.s99}{cuthbert.text}
\ltRubricItalics{pub.priest.servicebook}{li.rubric.bede}
\ltDialog{ho.s99}{bede.text}
\ltRubricItalics{pub.priest.servicebook}{li.rubric.silouan}
\ltDialog{ho.s99}{silouan.text}
\ltActorSingleLine{actors}{Deacon}
\ltDialog{prayers}{pet00}
\ltActorSingleLine{actors}{People}
\ltDialog{prayers}{res01}
\ltSmallTitle{eu.lichrysbasil}{euLI.Key0601.title}
\ltActorRubric{actors}{Priest}{rubrical}{InALowVoice}
\ltDialogInaudible{eu.lichrysbasil}{euLI.Key0601.text}
\ltActorSingleLine{actors}{Priest}
\ltDialog{prayers}{exc05a}
\ltActorSingleLine{actors}{Deacon}
\ltDialog{prayers}{exc05b}
\ltActorSingleLine{actors}{People}
\ltDialog{prayers}{res04}
\ltSmallTitle{variables.info}{Trisagion.title}
\ltDialog{ho.s07}{hoLI.TrisagiosHymn.text}
\ltDialog{ho.s07}{hoLI.TrisagiosHymn.text}
\ltDialog{ho.s07}{hoLI.TrisagiosHymn.text}
\ltDialog{pub.priest.servicebook}{doxapatrikainyn}
\ltDialog{ho.s07}{hoLI.TrisagiosHymn3.text}{ho.s07}{hoLI.TrisagiosHymn4.text}
\ltActorSingleLine{actors}{Deacon}
\ltDialog{eu.lichrysbasil}{euLI.Key0602.text}
\ltActorSingleLine{actors}{People}
\ltDialog{ho.s07}{hoLI.TrisagiosHymn.text}
\ltSmallTitle{pub.priest.servicebook}{li.readings.title.doc}
\ltActorSingleLine{actors}{Deacon}
\ltDialog{prayers}{exc19}
\ltActorSingleLine{actors}{Priest}
\ltDialog{prayers}{pet31}
\ltActorSingleLine{actors}{Reader}
\ltDialog{prayers}{res05}
\ltActorSingleLine{actors}{Deacon}
\ltDialog{prayers}{exc17}
\ltActorSingleLine{actors}{Reader}
\ltDialog{pub.priest.servicebook}{li.prokeimenonmode}
\ltActorSingleLine{actors}{Deacon}
\ltDialog{prayers}{exc17}
\ltActorSingleLine{actors}{Reader}
\ltRubricItalics{rubrical}{cl.eu.lichrysbasil.R009}
\ltActorSingleLine{actors}{Deacon}
\ltDialog{prayers}{exc19}
\ltRubricItalics{rubrical}{cl.eu.lichrysbasil.R010}
\ltDialog{prayers}{epi02}
\ltActorSingleLine{actors}{Reader}
\ltDialog{prayers}{res05}{prayers}{Allilouia3.text}
\ltSmallTitle{eu.lichrysbasil}{euLI.Key0704.title}
\ltActorRubric{actors}{Priest}{rubrical}{InALowVoice}
\ltDialogInaudible{eu.lichrysbasil}{euLI.Key0704.text}
\ltActorSingleLine{actors}{Deacon}{rubrical}{InALowVoice}
\ltDialogInaudible{pub.priest.servicebook}{li.blessreader}
\ltActorRubric{actors}{Priest}{rubrical}{InALowVoice}
\ltDialogInaudible{pub.priest.servicebook}{li.blessreader2}
\ltActorSingleLine{actors}{Deacon}{rubrical}{InALowVoice}
\ltDialogInaudible{prayers}{res04}
\ltActorSingleLine{actors}{Priest}
\ltDialog{prayers}{exc17}{prayers}{exc18}{prayers}{gos02}{prayers}{pet31}
\ltActorSingleLine{actors}{People}
\ltDialog{prayers}{res05}
\ltActorSingleLine{actors}{Deacon}
\ltDialog{prayers}{gos03a}{prayers}{gos03b}
\ltActorSingleLine{actors}{People}
\ltDialog{prayers}{DoxaSoiKyrie}
\ltActorSingleLine{actors}{Priest}
\ltDialog{prayers}{exc19}
\ltActorSingleLine{actors}{Deacon}
\ltRubricItalics{pub.priest.servicebook}{li.rubric.readgospel}
\ltActorSingleLine{actors}{Priest}
\ltDialog{prayers}{gos04}
\ltActorSingleLine{actors}{People}
\ltDialog{prayers}{DoxaSoiKyrie}
\ltSmallTitle{eu.lichrysbasil}{euLI.Key0706.title}
\ltRubricItalics{pub.priest.servicebook}{li.rubric.blesswithgospel}{pub.priest.servicebook}{li.rubric.preach}
\ltSmallTitle{eu.lichrysbasil}{euLI.Key0800.title}
\ltActorSingleLine{actors}{Deacon}
\ltDialog{prayers}{pet15}
\ltActorSingleLine{actors}{People}
\ltDialog{prayers}{res01}
\ltActorSingleLine{actors}{Deacon}
\ltDialog{prayers}{pet16}
\ltActorSingleLine{actors}{People}
\ltDialog{prayers}{res01}
\ltActorSingleLine{actors}{Deacon}
\ltDialog{prayers}{pet17}
\ltActorSingleLine{actors}{People}
\ltDialogItalics{prayers}{res01}{pub.priest.servicebook}{li.rubric.thriceeach}
\ltActorSingleLine{actors}{Deacon}
\ltUnknown{prayers}{pet19Sa}{client}{cl.bishop1.rank}{client}{cl.bishop1.name.p}
\ltDialog{prayers}{pet20}
\ltDialog{prayers}{pet21}
\ltDialog{prayers}{pet22}
\ltDialog{prayers}{pet23}
\ltSmallTitle{eu.lichrysbasil}{euLI.Key0801.title}
\ltActorSingleLine{actors}{Priest}{rubrical}{InALowVoice}
\ltDialogInaudible{eu.lichrysbasil}{euLI.Key0801.text}
\ltActorSingleLine{actors}{Priest}
\ltDialog{prayers}{exc11}
\ltActorSingleLine{actors}{People}
\ltDialog{prayers}{res04}
\ltSmallTitle{eu.lichrysbasil}{euLI.Key0900.title}
\ltRubricItalics{pub.priest.servicebook}{li.rubric.catechumens}
\ltRubricItalics{pub.priest.servicebook}{li.rubric.catechumens2}
\ltDialog{prayers}{res01}
\ltActorSingleLine{actors}{Deacon}
\ltDialog{eu.lichrysbasil}{euLI.Key0901.text}
\ltDialog{eu.lichrysbasil}{euLI.Key0902.text}
\ltDialog{eu.lichrysbasil}{euLI.Key0903.text}
\ltDialog{eu.lichrysbasil}{euLI.Key0904.text}
\ltDialog{eu.lichrysbasil}{euLI.Key0905.text}
\ltDialog{eu.lichrysbasil}{euLI.Key0906.text}
\ltDialog{eu.lichrysbasil}{euLI.Key0907.text}
\ltDialog{eu.lichrysbasil}{euLI.Key0908.text}
\ltActorSingleLine{actors}{People}
\ltDialog{prayers}{res03}
\ltSmallTitle{eu.lichrysbasil}{euLI.Key0909.title}
\ltActorSingleLine{actors}{Priest}{rubrical}{InALowVoice}
\ltDialogInaudible{eu.lichrysbasil}{euLI.Key0909.text}
\ltActorSingleLine{actors}{Priest}
\ltDialog{eu.lichrysbasil}{euLI.Key0910.text}
\ltActorSingleLine{actors}{People}
\ltDialog{prayers}{res04}
\ltActorSingleLine{actors}{Deacon}
\ltDialog{eu.lichrysbasil}{euLI.Key0911.text}
\ltSmallTitle{eu.lichrysbasil}{euLI.Key1000.title}
\ltActorSingleLine{actors}{Deacon}
\ltDialog{eu.lichrysbasil}{euLI.Key0912.text}
\ltActorSingleLine{actors}{People}
\ltDialog{prayers}{res01}
\ltActorSingleLine{actors}{Deacon}
\ltDialog{prayers}{pet12}
\ltDialog{prayers}{res01}
\ltActorSingleLine{actors}{Deacon}
\ltDialog{prayers}{exc17}
\ltSmallTitle{eu.lichrysbasil}{euLI.Key1001.title}
\ltActorSingleLine{actors}{Priest}{rubrical}{InALowVoice}
\ltDialogInaudible{eu.lichrysbasil}{euLI.Key1001.text}
\ltActorSingleLine{actors}{Priest}
\ltDialog{prayers}{exc01}
\ltActorSingleLine{actors}{People}
\ltDialog{prayers}{res04}
\ltActorSingleLine{actors}{Deacon}
\ltDialog{prayers}{pet14}
\ltActorSingleLine{actors}{People}
\ltDialog{prayers}{res01}
\ltActorSingleLine{actors}{Deacon}
\ltDialog{prayers}{pet12}
\ltActorSingleLine{actors}{People}
\ltDialog{prayers}{res01}
\ltActorSingleLine{actors}{Deacon}
\ltDialog{prayers}{exc17}
\ltSmallTitle{eu.lichrysbasil}{euLI.Key1002.title}
\ltActorRubric{actors}{Priest}{rubrical}{InALowVoice}
\ltDialogInaudible{eu.lichrysbasil}{euLI.Key1002.text}
\ltActorSingleLine{actors}{Priest}
\ltDialog{eu.lichrysbasil}{euLI.Key1003.text}
\ltActorSingleLine{actors}{People}
\ltDialog{prayers}{res04}
\ltDesignation{eu.lichrysbasil}{euLI.Key1100.title}
\ltSmallTitle{eu.lichrysbasil}{euLI.Key1102.title}
\ltActorSingleLine{actors}{People}
\ltDialog{eu.lichrysbasil}{euLI.Key1102.text}
\ltSmallTitle{eu.lichrysbasil}{euLI.Key1101.title}
\ltActorRubric{actors}{Priest}{rubrical}{InALowVoice}
\ltDialogInaudible{eu.lichrysbasil}{euLI.Key1101.text}
\ltActorSingleLine{actors}{Deacon}
\ltDialog{eu.lichrysbasil}{euLI.Key1110.text}
\ltActorSingleLine{actors}{People}
\ltDialog{eu.lichrysbasil}{euLI.Key1103.text}
\ltSmallTitle{eu.lichrysbasil}{euLI.Key1200.title}
\ltActorSingleLine{actors}{Deacon}
\ltDialog{prayers}{pet24}
\ltActorSingleLine{actors}{People}
\ltDialogItalics{prayers}{res01}{pub.priest.servicebook}{li.rubric.eachpetition2}
\ltActorSingleLine{actors}{Deacon}
\ltDialog{eu.lichrysbasil}{euLI.Key1201.text}
\ltDialog{prayers}{pet04}
\ltDialog{eu.lichrysbasil}{euLI.Key0708}{prayers}{pet11}
\ltDialog{prayers}{pet12}
\ltDialog{prayers}{pet25m}
\ltActorSingleLine{actors}{People}
\ltDialogItalics{prayers}{res02}{pub.priest.servicebook}{li.rubric.eachpetition2}
\ltActorSingleLine{actors}{Deacon}
\ltDialog{prayers}{pet26}
\ltDialog{prayers}{pet27}
\ltDialog{prayers}{pet28}
\ltDialog{prayers}{pet29}
\ltDialog{prayers}{pet30}{eu.lichrysbasil}{euLI.Key0709}
\ltDialog{prayers}{pet13}
\ltActorSingleLine{actors}{People}
\ltDialog{prayers}{res03}
\ltSmallTitle{eu.lichrysbasil}{euLI.Key1202.title}
\ltActorRubric{actors}{Priest}{rubrical}{InALowVoice}
\ltDialogInaudible{eu.lichrysbasil}{euLI.Key1202.text}
\ltActorSingleLine{actors}{Priest}
\ltDialog{eu.lichrysbasil}{euLI.Key1203.text}
\ltActorSingleLine{actors}{People}
\ltDialog{prayers}{res04}
\ltActorSingleLine{actors}{Priest}
\ltDialog{prayers}{pet31}
\ltActorSingleLine{actors}{People}
\ltDialog{prayers}{res05}
\ltActorSingleLine{actors}{Deacon}
\ltDialog{eu.lichrysbasil}{euLI.Key1204.text}
\ltActorSingleLine{actors}{People}
\ltDialog{eu.lichrysbasil}{euLI.Key1205.text}
\ltSmallTitle{eu.lichrysbasil}{euLI.Key1209.title}
\ltActorSingleLine{actors}{Deacon}
\ltDialog{eu.lichrysbasil}{euLI.Key1208.text}
\ltActorSingleLine{actors}{People}
\ltReading{prayers}{Pistevo.text}
\ltSmallTitle{eu.lichrysbasil}{euLI.Key1300.title}
\ltActorSingleLine{actors}{Deacon}
\ltDialog{eu.lichrysbasil}{euLI.Key1301.text}
\ltActorSingleLine{actors}{People}
\ltDialog{eu.lichrysbasil}{euLI.Key1302.text}
\ltActorSingleLine{actors}{Priest}
\ltDialog{eu.lichrysbasil}{euLI.Key1303.text}
\ltActorSingleLine{actors}{People}
\ltDialog{eu.lichrysbasil}{euLI.Key1304.text}
\ltActorSingleLine{actors}{Priest}
\ltDialog{eu.lichrysbasil}{euLI.Key1305.text}
\ltActorSingleLine{actors}{People}
\ltDialog{eu.lichrysbasil}{euLI.Key1306.text}
\ltActorSingleLine{actors}{Priest}
\ltDialog{eu.lichrysbasil}{euLI.Key1307.text}
\ltActorSingleLine{actors}{People}
\ltDialog{eu.lichrysbasil}{euLI.Key1308.text}
\ltActorRubric{actors}{Priest}{rubrical}{InALowVoice}
\ltDialogInaudible{eu.lichrysbasil}{euLI.Key1309.text}
\ltActorSingleLine{actors}{Priest}
\ltDialog{eu.lichrysbasil}{euLI.Key1310.text}
\ltActorSingleLine{actors}{People}
\ltDialog{eu.lichrysbasil}{euLI.Key1311.text}
\ltActorRubric{actors}{Priest}{rubrical}{InALowVoice}
\ltDialogInaudible{eu.lichrysbasil}{euLI.Key1312.text}
\ltActorSingleLine{actors}{Priest}
\ltDialog{eu.lichrysbasil}{euLI.Key1313.text}
\ltActorSingleLine{actors}{People}
\ltDialog{prayers}{res04}
\ltActorRubric{actors}{Priest}{rubrical}{InALowVoice}
\ltDialogInaudible{eu.lichrysbasil}{euLI.Key1314.text}
\ltActorSingleLine{actors}{Priest}
\ltDialog{eu.lichrysbasil}{euLI.Key1315.text}
\ltActorSingleLine{actors}{People}
\ltDialog{prayers}{res04}
\ltActorRubric{actors}{Priest}{rubrical}{InALowVoice}
\ltDialogInaudible{eu.lichrysbasil}{euLI.Key1316.text}
\ltActorSingleLine{actors}{Priest}
\ltDialog{eu.lichrysbasil}{euLI.Key1317.text}
\ltActorSingleLine{actors}{People}
\ltDialog{eu.lichrysbasil}{euLI.Key1318.text}
\ltActorRubric{actors}{Priest}{rubrical}{InALowVoice}
\ltDialogInaudible{eu.lichrysbasil}{euLI.Key1319.text}
\ltActorRubric{actors}{Deacon}{rubrical}{InALowVoice}
\ltDialogInaudible{pub.priest.servicebook}{li.changebread}
\ltActorRubric{actors}{Priest}{rubrical}{InALowVoice}
\ltDialogInaudible{eu.lichrysbasil}{euLI.Key1321.text}
\ltActorRubric{actors}{Deacon}{rubrical}{InALowVoice}
\ltDialogInaudible{prayers}{res04}
\ltDialogInaudible{pub.priest.servicebook}{li.changewine}
\ltActorRubric{actors}{Priest}{rubrical}{InALowVoice}
\ltDialogInaudible{eu.lichrysbasil}{euLI.Key1323.text}
\ltActorRubric{actors}{Deacon}{rubrical}{InALowVoice}
\ltDialogInaudible{prayers}{res04}
\ltDialogInaudible{pub.priest.servicebook}{li.blessboth}
\ltActorRubric{actors}{Priest}{rubrical}{InALowVoice}
\ltDialogInaudible{eu.lichrysbasil}{euLI.Key1325.text}
\ltActorRubric{actors}{Deacon}{rubrical}{InALowVoice}
\ltDialogInaudible{prayers}{res10}
\ltActorRubric{actors}{Priest}{rubrical}{InALowVoice}
\ltDialogInaudible{eu.lichrysbasil}{euLI.Key1326.text}
\ltActorSingleLine{actors}{Priest}
\ltDialog{eu.lichrysbasil}{euLI.Key1327.text}
\ltSmallTitle{variables.info}{TheotokosHymn.title}
\ltActorSingleLine{actors}{People}
\ltDialog{prayers}{AxionEstinComplete.text}
\ltActorRubric{actors}{Priest}{rubrical}{InALowVoice}
\ltDialogInaudible{eu.lichrysbasil}{euLI.Key1329.text}
\ltActorSingleLine{actors}{Priest}
\ltDialogJumbo{eu.lichrysbasil}{euLI.Key1330a.text}{client}{cl.bishop1.rank}{client}{cl.bishop1.name.p}{eu.lichrysbasil}{euLI.Key1330b.text}
\ltActorSingleLine{actors}{Deacon}
\ltDialog{eu.lichrysbasil}{euLI.Key1331.text}
\ltActorSingleLine{actors}{People}
\ltDialog{eu.lichrysbasil}{euLI.Key1332.text}
\ltActorRubric{actors}{Priest}{rubrical}{InALowVoice}
\ltDialogInaudible{eu.lichrysbasil}{euLI.Key1333.text}
\ltActorSingleLine{actors}{Priest}
\ltDialog{eu.lichrysbasil}{euLI.Key1334.text}
\ltActorSingleLine{actors}{People}
\ltDialog{prayers}{res04}
\ltActorSingleLine{actors}{Priest}
\ltDialog{eu.lichrysbasil}{euLI.Key1335.text}
\ltActorSingleLine{actors}{People}
\ltDialog{eu.lichrysbasil}{euLI.Key1336.text}
\ltSmallTitle{pub.priest.servicebook}{li.litanylordsprayer.title.doc}
\ltActorSingleLine{actors}{Deacon}
\ltDialog{eu.lichrysbasil}{euLI.Key1401.text}
\ltActorSingleLine{actors}{People}
\ltDialogItalics{prayers}{res01}{pub.priest.servicebook}{li.rubric.eachpetition2}
\ltActorSingleLine{actors}{Deacon}
\ltDialog{eu.lichrysbasil}{euLI.Key1402.text}
\ltDialog{eu.lichrysbasil}{euLI.Key1403.text}
\ltDialog{prayers}{pet11}
\ltDialog{prayers}{pet12}
\ltDialog{prayers}{pet25m}
\ltActorSingleLine{actors}{People}
\ltDialogItalics{prayers}{res02}{pub.priest.servicebook}{li.rubric.eachpetition2}
\ltActorSingleLine{actors}{Deacon}
\ltDialog{prayers}{pet26}
\ltDialog{prayers}{pet27}
\ltDialog{prayers}{pet28}
\ltDialog{prayers}{pet29}
\ltDialog{prayers}{pet30}
\ltDialog{eu.lichrysbasil}{euLI.Key1404.text}
\ltActorSingleLine{actors}{People}
\ltDialog{prayers}{res03}
\ltActorRubric{actors}{Priest}{rubrical}{InALowVoice}
\ltDialogInaudible{eu.lichrysbasil}{euLI.Key1405.text}
\ltActorSingleLine{actors}{Priest}
\ltDialog{eu.lichrysbasil}{euLI.Key1406.text}
\ltSmallTitle{titles}{KyriakiProsefchi}
\ltActorSingleLine{actors}{People}
\ltReading{prayers}{PaterImon.text}
\ltActorSingleLine{actors}{Priest}
\ltDialog{prayers}{exc20}
\ltActorSingleLine{actors}{People}
\ltDialog{prayers}{res04}
\ltActorSingleLine{actors}{Priest}
\ltDialog{prayers}{pet31}
\ltActorSingleLine{actors}{People}
\ltDialog{prayers}{res05}
\ltActorSingleLine{actors}{Deacon}
\ltDialog{prayers}{pet32}
\ltActorSingleLine{actors}{People}
\ltDialog{prayers}{res03}
\ltActorRubric{actors}{Priest}{rubrical}{InALowVoice}
\ltDialogInaudible{eu.lichrysbasil}{euLI.Key1407.text}
\ltActorSingleLine{actors}{Priest}
\ltDialog{prayers}{exc07a}
\ltActorSingleLine{actors}{People}
\ltDialog{prayers}{res04}
\ltActorRubric{actors}{Priest}{rubrical}{InALowVoice}
\ltDialogInaudible{eu.lichrysbasil}{euLI.Key1409.text}
\ltRubricItalics{pub.priest.servicebook}{li.rubric.bowcommunion}
\ltDialogInaudible{pub.priest.servicebook}{li.preparation.mercy}
\ltActorSingleLine{actors}{Deacon}
\ltDialog{prayers}{exc19}
\ltActorSingleLine{actors}{Priest}
\ltDialog{eu.lichrysbasil}{euLI.Key1410.text}
\ltActorSingleLine{actors}{People}
\ltDialog{eu.lichrysbasil}{euLI.Key1411.text}
\ltMixedDesignation{eu.lichrysbasil}{euLI.Key1409.title}
\ltSmallTitle{ho.s21}{hoPrayer.title}
\ltActorSingleLine{actors}{People}
\ltReading{ho.s21}{hoPrayer.Key101.text}
\ltReading{ho.s21}{hoPrayer.Key110.text}
\ltReading{ho.s21}{hoPrayer.Key121.text}
\ltReading{ho.s21}{hoPrayer.Key161.text}
\ltActorSingleLine{actors}{Deacon}
\ltDialog{eu.lichrysbasil}{euLI.Key1526.text}
\ltActorSingleLine{actors}{People}
\ltDialog{pub.priest.servicebook}{li.godisthelord}
\ltRubricItalics{eu.lichrysbasil}{euLI.Key1528.rubric}
\ltDialogInaudible{eu.lichrysbasil}{euLI.Key1527.text}
\ltDesignation{eu.lichrysbasil}{euLI.MM.HymnsDuringCommunion.title}
\ltActorSingleLine{actors}{Priest}
\ltDialog{eu.lichrysbasil}{euLI.Key1529.text}
\ltActorSingleLine{actors}{People}
\ltDialog{eu.lichrysbasil}{euLI.Key1530.text}
\ltActorSingleLine{actors}{Priest}
\ltDialog{prayers}{PantoteNyn.text}
\ltActorSingleLine{actors}{People}
\ltDialog{prayers}{res04}
\ltDialog{eu.lichrysbasil}{euLI.Key1603.text}
\ltMixedDesignation{pub.priest.servicebook}{li.thanksdismissal.title.doc}
\ltActorSingleLine{actors}{Deacon}
\ltDialog{eu.lichrysbasil}{euLI.Key1604.text}
\ltActorSingleLine{actors}{People}
\ltUnknown{prayers}{DoxaSoiKyrie}{rubrical}{Or}{prayers}{res01}
\ltActorSingleLine{actors}{Deacon}
\ltDialog{prayers}{pet12}
\ltActorSingleLine{actors}{People}
\ltDialog{prayers}{res01}
\ltActorSingleLine{actors}{Deacon}
\ltDialog{eu.lichrysbasil}{euLI.Key1605.text}
\ltActorSingleLine{actors}{People}
\ltDialog{prayers}{res03}
\ltSmallTitle{eu.lichrysbasil}{euLI.Key1606.title}
\ltActorRubric{actors}{Priest}{rubrical}{InALowVoice}
\ltDialogInaudible{eu.lichrysbasil}{euLI.Key1606.text}
\ltActorSingleLine{actors}{Priest}
\ltDialog{prayers}{exc24}
\ltActorSingleLine{actors}{People}
\ltDialog{prayers}{res04}
\ltSmallTitle{eu.lichrysbasil}{euLI.Key1700.title}
\ltActorSingleLine{actors}{Priest}
\ltDialog{eu.lichrysbasil}{euLI.Key1701.text}
\ltActorSingleLine{actors}{People}
\ltDialog{pub.priest.servicebook}{li.lordsname}
\ltActorSingleLine{actors}{Deacon}
\ltDialog{prayers}{pet00}
\ltActorSingleLine{actors}{People}
\ltDialog{prayers}{res01}
\ltSmallTitle{eu.lichrysbasil}{euLI.Key1702.title}
\ltActorSingleLine{actors}{Priest}
\ltDialog{eu.lichrysbasil}{euLI.Key1702.text}
\ltActorSingleLine{actors}{People}
\ltDialogJumbo{prayers}{res04}{liturgical.verses}{psLI.aftercommunion.v1.text}{rubrical}{Thrice}
\ltActorRubric{actors}{Priest}{rubrical}{InALowVoice}
\ltDialogInaudible{eu.lichrysbasil}{euLI.Key1704.text}
\ltActorSingleLine{actors}{Deacon}
\ltDialog{prayers}{pet00}
\ltActorSingleLine{actors}{People}
\ltDialog{prayers}{res01}
\ltActorSingleLine{actors}{Priest}
\ltDialog{prayers}{pet37}
\ltActorSingleLine{actors}{People}
\ltDialog{prayers}{res04}
\ltActorSingleLine{actors}{Priest}
\ltDialog{prayers}{DoxaSoiOTheosImon.text}
\ltActorSingleLine{actors}{Reader}
\ltDialog{pub.priest.servicebook}{doxapatrikainyn}{prayers}{res06}{prayers}{res13}
\ltActorSingleLine{actors}{Priest}
\itId{en}{uk}{durlash}{redirect}{r10}{
\itRid{pub.priest.servicebook}{li.dis.oanastas}
}%
\itId{en}{uk}{durlash}{redirect}{r11}{
\itRid{pub.priest.servicebook}{li.rubric.sundaydismissal}
}%
\itId{en}{uk}{durlash}{redirect}{r12}{
\itRid{dismissals}{dis01}
}%
\itId{en}{uk}{durlash}{redirect}{r13}{
\itRid{dismissals}{dis02} \itRid{dismissals}{dis03} \itRid{dismissals}{dis04} \itRid{dismissals}{dis05} \itRid{dismissals}{dis06} \itRid{dismissals}{dis07} \itRid{dismissals}{dis08} \itRid{dismissals}{li.dis.chrysostom} \itRid{dismissals}{dis09} \itRid{dismissals}{dis10} \itRid{dismissals}{dis89} \itRid{prayers}{DiEfchonPateron.text}
}%
\itId{ro}{uk}{dur}{redirect}{r10}{
\itRid{pub.priest.servicebook}{li.dis.oanastas}
}%
\itId{ro}{uk}{dur}{redirect}{r11}{
\itRid{pub.priest.servicebook}{li.rubric.sundaydismissal}
}%
\itId{ro}{uk}{dur}{redirect}{r12}{
\itRid{dismissals}{dis01}
}%
\itId{ro}{uk}{dur}{redirect}{r13}{
\itRid{dismissals}{dis02} \itRid{dismissals}{dis03} \itRid{dismissals}{dis04} \itRid{dismissals}{dis05} \itRid{dismissals}{dis06} \itRid{dismissals}{dis07} \itRid{dismissals}{dis08} \itRid{dismissals}{li.dis.chrysostom} \itRid{dismissals}{dis09} \itRid{dismissals}{dis10} \itRid{dismissals}{dis89} \itRid{prayers}{DiEfchonPateron.text}
}%
\ltUnknown{redirect}{r10}{redirect}{r11}{redirect}{r12}{redirect}{r13}
\ltActorSingleLine{actors}{People}
\ltDialog{prayers}{res04}
\ltRubricItalics{pub.priest.servicebook}{li.rubric.giveantidoron}
\ltDialog{pub.priest.servicebook}{li.blessingmercy}
\ltParaRedBold{pub.priest.servicebook}{li.end.title.doc}
\ltColumnsOff%
\tiny\textit{Generated 2023-08-15T16:26:02.631Z (Universal Time)  using OCMC liturgical software and a template from GOARCH DCS, Inc.}%
\vfill%
\pagebreak%
\cleardoublepage%
\mybackcover%
\end{document}%
