\itId{sys}{technology.codes}{en}{github}{name}{%
GitHub
}%
\itId{sys}{technology.codes}{en}{github}{description}{%
The project coordinator assigned to you will store copies of your work on the Github website to keep them safe.  It also stores all the prior versions you have made in case you need to get them back.
}%
\itId{sys}{technology.codes}{en}{ocmc.i18n}{name}{%
i18n-topic-key.sty
}%
\itId{sys}{technology.codes}{en}{ocmc.i18n}{description}{%
A \LaTeX\ style created by OCMC for retrieving text by language, country, realm, topic, and key.
}%
\itId{sys}{technology.codes}{en}{ocmc.liturgical.text}{name}{%
ocmc-liturgical-text.sty
}%
\itId{sys}{technology.codes}{en}{ocmc.liturgical.text}{description}{%
A \LaTeX\ style created by OCMC for formatting liturgical texts of the Eastern Orthodox Christian Church.
}%
\itId{sys}{technology.codes}{en}{latex}{name}{%
\LaTeX
}%
\itId{sys}{technology.codes}{en}{latex}{description}{%
For typesetting your document and creating a PDF file.
}%
\itId{sys}{technology.codes}{en}{skype}{name}{%
Skype
}%
\itId{sys}{technology.codes}{en}{skype}{description}{%
If you have Skype installed on your computer, then if you wish, you can talk with the project coordinator assigned to work with you using Skype.
}%
\itId{sys}{technology.codes}{en}{sharelatex}{name}{%
ShareLatex
}%
\itId{sys}{technology.codes}{en}{sharelatex}{description}{%
An Internet website that provides you with an environment to work on your translation(s) and to produce PDF documents.
}%
\itId{sys}{technology.codes}{en}{browser}{name}{%
Web Browser
}%
\itId{sys}{technology.codes}{en}{browser}{description}{%
The only software you need on your computer is a web browser.
}%
